---
title: "Large-scale simulation for the cash paper, Part 4: Smaller, faster exploratory simulations -- Average pFDP"
author: "Lei Sun"
date: 2017-11-11
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

## Using smaller, faster, exploratory simulations

Instead of doing a simulation with $1K$ runs, each run with $10K$ samples, we are downsizing it so that simulations can be done faster while still show a pattern. Right now, $100$ runs, each run with $5K$ samples seem adequate.

We don't want the sample size to be too small. Small sample sizes appear to work less well with Gaussian derivatives fitting.

## Frequentist pFDR accuracy with all data sets

```{r code, message = FALSE, warning = FALSE}
source("../code/gdash_lik.R")
```

```{r effect sampling function, echo = FALSE}
## produce simulated true signals beta
sample.g = function (g, n) {
  UseMethod("sample.g")
}

sample.g.normalmix = function (g, n) {
  K = length(g$pi)
  beta = list()
  for (i in 1 : K) {
    beta[[i]] = rnorm(ceiling(n * g$pi[i]), g$mean[i], g$sd[i])
  }
  return(list(beta = sample(unlist(beta)), mixcompdist = "normal"))
}
```

```{r pFDR calibration function, echo = FALSE}
pFDP = function (FDR, response, predictor) {
  return(1 - mean(response[predictor <= FDR]))
}

pFDR.calib = function (beta, qvalue, pFDR.nominal) {
  pFDP.list = list()
  for (i in 1 : length(beta))
  pFDP.list[[i]] = sapply(pFDR.nominal, pFDP,
                         response = (beta[[i]] != 0),
                         predictor = qvalue[[i]])
  pFDP.mat = matrix(unlist(pFDP.list), nrow = length(pFDP.list), byrow = TRUE)
  pFDP.samplesize = colSums(!is.na(pFDP.mat))
  pFDP.mean = colMeans(pFDP.mat, na.rm = TRUE)
  pFDP.mean.sd = apply(pFDP.mat, 2, sd, na.rm = TRUE) / sqrt(pFDP.samplesize)
  return(list(pFDR.nominal = pFDR.nominal, pFDP.mean = pFDP.mean, pFDP.mean.sd = pFDP.mean.sd))
}

FDR.calib = function (beta, qvalue, pFDR.nominal) {
  pFDP.list = list()
  for (i in 1 : length(beta))
  pFDP.list[[i]] = sapply(pFDR.nominal, pFDP,
                         response = (beta[[i]] != 0),
                         predictor = qvalue[[i]])
  pFDP.mat = matrix(unlist(pFDP.list), nrow = length(pFDP.list), byrow = TRUE)
  pFDP.mat[is.na(pFDP.mat)] <- 0
  pFDP.samplesize = colSums(!is.na(pFDP.mat))
  pFDP.mean = colMeans(pFDP.mat, na.rm = TRUE)
  pFDP.mean.sd = apply(pFDP.mat, 2, sd, na.rm = TRUE) / sqrt(pFDP.samplesize)
  return(list(pFDR.nominal = pFDR.nominal, pFDP.mean = pFDP.mean, pFDP.mean.sd = pFDP.mean.sd))
}

pFDP.polygon.plot = function (beta, qvalue, pFDR.nominal, col) {
  summary = pFDR.calib(beta, qvalue, pFDR.nominal)
  mean = summary$pFDP.mean
  sd = summary$pFDP.mean.sd
  lines(pFDR.nominal, mean, col = col, cex = 2)
  polygon.color.rgb = as.vector(grDevices::col2rgb(col))
  polygon(x = c(0, pFDR.nominal, rev(pFDR.nominal), 0),
          y = c(0, mean - 2 * sd, rev(mean + 2 * sd), 0),
          col = grDevices::rgb(polygon.color.rgb[1], polygon.color.rgb[2], polygon.color.rgb[3], alpha = 100, max = 255),
          border = col,
          lty = 2)
}
```

```{r read data}
z.mat = readRDS("../output/z_null_liver_777.rds")
se.mat = readRDS("../output/sebetahat_null_liver_777.rds")
```

```{r fitting_plotting function, echo = FALSE}

cashSim <- function(z.mat, se.mat, nsim, ngene,
                    g.pi = c(0.9, 0.1), g.sd = c(0, 1),
                    relative_to_noise = TRUE) {
  ## generate intermediary variables to store results
  betahat.list = beta.list = list()
  pihat0.ash = pihat0.gdash = pihat0.qvalue = c()
  qvalue.BH = qvalue.qvalue = qvalue.ash = qvalue.gdash = list()
  
  ## select correlated null and standard error for simulation
  row.select <- sample(nrow(z.mat), nsim)
  z.mat <- z.mat[row.select, ]
  se.mat <- se.mat[row.select, ]
  
  ## simulation
  for (i in 1 : nsim) {
    gene.select <- sample(ncol(z.mat), ngene)
    ## standard error
    sebetahat <- se.mat[i, gene.select]
    ## correlated null
    z <- z.mat[i, gene.select]
    sigma_n <- 1
    if (relative_to_noise) {
      sigma_n <- sqrt(mean(sebetahat^2))
    }
    g <- ashr::normalmix(pi = g.pi, mean = 0, sd = g.sd * sigma_n)
    ## true signal
    beta = sample.g(g, ngene)$beta
    beta.list[[i]] = beta
    response = (beta != 0)
    ## betahat
    betahat = beta + sebetahat * z
    ## p value
    pvalue = (1 - pnorm(abs(betahat / sebetahat))) * 2

    ## different methods
    fit.ash = ashr::ash(betahat, sebetahat, mixcompdist = "normal", method = "fdr")
    fit.gdash = gdash(betahat, sebetahat)
    fit.qvalue = qvalue::qvalue(pvalue)
    fit.BH = p.adjust(pvalue, method = "BH")
    
    ## pihat0
    pihat0.ash[i] = ashr::get_pi0(fit.ash)
    pihat0.gdash[i] = ashr::get_pi0(fit.gdash)
    pihat0.qvalue[i] = fit.qvalue$pi0
    
    ## q value
    qvalue.BH[[i]] = fit.BH
    qvalue.qvalue[[i]] = fit.qvalue$qvalues
    qvalue.ash[[i]] = ashr::get_qvalue(fit.ash)
    qvalue.gdash[[i]] = fit.gdash$qvalue
  }
  
  ## plot & compare pihat0
  boxplot(pihat0.qvalue,
          pihat0.ash,
          pihat0.gdash,
          ylim = c(0, 1),
          names = c("qvalue",
                    "ASH",
                    "CASH"),
          ylab = expression(hat(pi)[0]),
          main = expression(hat(pi)[0]),
          las = 2
          )
  abline(h = g.pi[1], lty = 2, col = "red")
  
  ## plot & compare qvalue / positive FDR
  pFDR.nominal = seq(0, 0.2, 0.005)
  pFDR.methods = c("BH", "qvalue", "ASH", "CASH")
  col.vec = grDevices::rainbow(length(pFDR.methods))
  plot(pFDR.nominal, pFDR.nominal, type = "n", xlab = "Nominal Positive False Discovery Rate", ylab = "Average Positive False Discovery Proportion", main = "Calibration of Positive FDR")
  pFDP.polygon.plot(beta.list, qvalue.BH, pFDR.nominal, col.vec[1])
  pFDP.polygon.plot(beta.list, qvalue.qvalue, pFDR.nominal, col.vec[2])
  pFDP.polygon.plot(beta.list, qvalue.ash, pFDR.nominal, col.vec[3])
  pFDP.polygon.plot(beta.list, qvalue.gdash, pFDR.nominal, col.vec[4])
  lines(c(0, pFDR.nominal), c(0, pFDR.nominal), cex = 3, lty = 6)
  legend("topleft", ncol = 2, lty = 1, col = col.vec, legend = pFDR.methods, bty = "n")
}
```

## Simulation

```{r cache = TRUE}
cashSim(z.mat, se.mat,
        nsim = 100, ngene = 1000,
        g.pi = c(0.8, 0.2), g.sd = c(0, 1), relative_to_noise = TRUE)
```

## Simulation

```{r cache = TRUE}
cashSim(z.mat, se.mat,
        nsim = 100, ngene = 1000,
        g.pi = c(0.8, 0.2), g.sd = c(0, 2), relative_to_noise = TRUE)
```

## Simulation

```{r cache = TRUE}
cashSim(z.mat, se.mat,
        nsim = 100, ngene = 1000,
        g.pi = c(0.8, 0.2), g.sd = c(0, 1), relative_to_noise = FALSE)
```

## Simulation

```{r cache = TRUE}
cashSim(z.mat, se.mat,
        nsim = 100, ngene = 1000,
        g.pi = c(0.8, 0.1, 0.1), g.sd = c(0, 1, 2), relative_to_noise = TRUE)
```

## Simulation

```{r cache = TRUE}
cashSim(z.mat, se.mat,
        nsim = 100, ngene = 1000,
        g.pi = c(0.8, 0.1, 0.1), g.sd = c(0, 1, 2), relative_to_noise = FALSE)
```

## Simulation

```{r cache = TRUE}
cashSim(z.mat, se.mat,
        nsim = 100, ngene = 1000,
        g.pi = c(0.9, 0.1), g.sd = c(0, 1), relative_to_noise = TRUE)
```

## Simulation

```{r cache = TRUE}
cashSim(z.mat, se.mat,
        nsim = 100, ngene = 1000,
        g.pi = c(0.9, 0.1), g.sd = c(0, 2), relative_to_noise = TRUE)
```

## Simulation

```{r cache = TRUE}
cashSim(z.mat, se.mat,
        nsim = 100, ngene = 1000,
        g.pi = c(0.9, 0.1), g.sd = c(0, 1), relative_to_noise = FALSE)
```

## Simulation

```{r cache = TRUE}
cashSim(z.mat, se.mat,
        nsim = 100, ngene = 1000,
        g.pi = c(0.9, 0.05, 0.05), g.sd = c(0, 1, 2), relative_to_noise = TRUE)
```

## Simulation

```{r cache = TRUE}
cashSim(z.mat, se.mat,
        nsim = 100, ngene = 1000,
        g.pi = c(0.9, 0.05, 0.05), g.sd = c(0, 1, 2), relative_to_noise = FALSE)
```

## Simulation

```{r cache = TRUE}
cashSim(z.mat, se.mat,
        nsim = 100, ngene = 1000,
        g.pi = c(0.85, 0.10, 0.05), g.sd = c(0, 1, 2), relative_to_noise = TRUE)
```

## Simulation

```{r cache = TRUE}
cashSim(z.mat, se.mat,
        nsim = 100, ngene = 1000,
        g.pi = c(0.85, 0.10, 0.05), g.sd = c(0, 1, 2), relative_to_noise = FALSE)
```

## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
