---
title: "Histogram of correlated $z$ scores, Part 2"
author: "Lei Sun"
date: 2017-03-06
output: workflowr::wflow_html
---


**Last updated:** `r Sys.Date()`

**Code version:** `r workflowr::extract_commit(".", 1)$sha1`


## Introduction

Following [previous simulation](correlated_z.html) on randomly selected data sets, this time we first apply `ash` on $z$ scores for every data set, and take a second look at those data sets on which `ash` makes most mistakes, or in other words, produces smallest $\hat\pi_0$.

## Simulation and `ash`

```{r, cache = TRUE}
z = read.table("../output/z_null_liver_777.txt")
```

```{r, cache = TRUE}
library(ashr)
n = dim(z)[1]
pihat0 = c()
for (i in 1:n) {
  ash.fit = ash(as.numeric(z[i, ]), 1, method = "fdr")
  pihat0[i] = get_pi0(ash.fit)
}
```

## Histograms of $z$ scores in 100 most "`ash`-hostile" data sets

```{r, cache = TRUE}
I = order(pihat0)[1:100]
x = seq(-10, 10, 0.01)
y = dnorm(x)
k = 1
for (j in I) {
  cat("N0.", k, ": Data Set", j, "pihat0 =", pihat0[j])
  hist(as.numeric(z[j, ]), xlab = "z scores", freq = FALSE, ylim = c(0, 0.45), main = "10000 z scores, default")
  lines(x, y, col = "red")
  hist(as.numeric(z[j, ]), xlab = "z scores", freq = FALSE, ylim = c(0, 0.45), nclass = 100, main = "10000 z scores, 100 bins")
  lines(x, y, col = "red")
  k = k + 1
}
```

## Take a closer look at the $p$ values in 100 most "`ash`-hostile" data sets

We take a closer look at the behavior of $p$ values in these most "`ash`-hostile" data sets, and also apply Benjamini-Hochberg's FDR procedure on them, to see if BH is robust enough against the foes that make `ash` fail badly.  False discoveries produced by BH are indicated as green points.

```{r, cache = TRUE}
p = read.table("../output/p_null_liver_777.txt")
```


```{r, cache = TRUE}
fd.bh = c()

for (i in 1 : n[1]) {
  p_BH = p.adjust(p[i, ], method = "BH")
  fd.bh[i] = sum(p_BH <= 0.05)
}
```


```{r, cache = TRUE}
I = order(pihat0)[1:100]
x = seq(-10, 10, 0.01)
y = dnorm(x)
k = 1
m = dim(p)[2]
for (j in I) {
  cat("N0.", k, ": Data Set", j, "; pihat0 =", pihat0[j], "; Number of False Discoveries:", fd.bh[j])
  hist(as.numeric(z[j, ]), xlab = "z scores", freq = FALSE, ylim = c(0, 0.45), nclass = 100, main = "10000 z scores, 100 bins")
  lines(x, y, col = "red")
  qqnorm(as.numeric(z[j, ]), main = "Normal Q-Q plot for z scores")
  abline(0, 1)
  plot(sort(as.numeric(p[j, ])), xlab = "Order", ylab = "Ordered p value", main = "All p values")
  abline(0, 1 / m, col = "blue")
  abline(0, 0.05 / m, col = "red")
  legend("top", lty = 1, col = c("blue", "red"), c("Uniform", "BH, FDR = 0.05"))
  
  pj = sort(as.numeric(p[j, ]))

  plot(pj[1:max(100, fd.bh[j])], xlab = "Order", ylab = "Ordered p value", main = "Zoom-in to 100 smallest p values", ylim = c(0, pj[max(100, fd.bh[j])]))
  abline(0, 1 / m, col = "blue")
  points(pj[1:fd.bh[j]], col = "green", pch = 19)
  abline(0, 0.05 / m, col = "red")
  legend("top", lty = 1, col = c("blue", "red"), c("Uniform", "BH, FDR = 0.05"))
  
  plot(pj[pj <= 0.01], xlab = "Order", ylab = "Ordered p value", main = "Zoom-in to p values <= 0.01", ylim = c(0, 0.01))
  abline(0, 1 / m, col = "blue")
  points(pj[1:fd.bh[j]], col = "green", pch = 19)
  abline(0, 0.05 / m, col = "red")
  legend("top", lty = 1, col = c("blue", "red"), c("Uniform", "BH, FDR = 0.05"))
  
  plot(pj[pj <= 0.05], xlab = "Order", ylab = "Ordered p value", main = "Zoom-in to p values <= 0.05", ylim = c(0, 0.05))
  abline(0, 1 / m, col = "blue")
  points(pj[1:fd.bh[j]], col = "green", pch = 19)
  abline(0, 0.05 / m, col = "red")
  legend("top", lty = 1, col = c("blue", "red"), c("Uniform", "BH, FDR = 0.05"))
  
  k = k + 1
}
```

```{r, cache = TRUE}
write.table(pihat0, file = "../output/pihat0_z_null_liver_777.txt", quote = FALSE, col.names = FALSE, row.names = FALSE)
```

## Session Information

