---
title: "Histograms of correlated $z$ scores"
author: "Lei Sun"
date: 2017-03-06
output: html_document
---

```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

```{r knitr-opts-chunk, include=FALSE}
```

**Last updated:** `r Sys.Date()`

**Code version:** `r workflowr::extract_commit(".", 1)$sha1`

## Introduction

[Efron 2010] and [Schwartzman's comment] brings to the center the question "what's the behavior of $z$ scores under correlation?"  Schwartzman pointed out in theory that "the observed histogram is more likely to be narrow than wide, and that it cannot be too wide before it becomes bimodal."  Let's take a look if this result holds true under our simulation scheme with GTex/Liver data.

## Simulation and results

```{r, cache = TRUE}
z = read.table("../output/z_null_liver_777.txt")
```

We randomly selected 20 data sets, each with $10000$ z scores, generated by the [null simulation pipeline](nullpipeline.html).  Based on each data set we plot two histograms, one using default number of bins and the other $100$ bins.  The red line indicates the density of $N(0, 1)$.

```{r}
set.seed(777)
sample_z = sort(sample(dim(z)[1], 20))
x = seq(- 10, 10, 0.01)
y = dnorm(x)
for (i in sample_z) {
  cat("Data Set", i)
  hist(as.numeric(z[i, ]), xlab = "z scores", freq = FALSE, ylim = c(0, 0.45), main = "10000 z scores, default")
  lines(x, y, col = "red")
  hist(as.numeric(z[i, ]), xlab = "z scores", freq = FALSE, ylim = c(0, 0.45), nclass = 100, main = "10000 z scores, 100 bins")
  lines(x, y, col = "red")
}
```


[Efron 2010]: http://amstat.tandfonline.com/doi/abs/10.1198/jasa.2010.tm09129
[Schwartzman's comment]: http://amstat.tandfonline.com/doi/abs/10.1198/jasa.2010.tm10237

## Session Information

```{r session-info}
```
