---
title: "Histogram of correlated $z$ scores, Part 3"
author: "Lei Sun"
date: 2017-03-10
output: html_document
---

```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

```{r knitr-opts-chunk, include=FALSE}
```

**Last updated:** `r Sys.Date()`

**Code version:** `r workflowr::extract_commit(".", 1)$sha1`

## Introduction

From previous simulation on [FDR on correlated null](FDR_Null.html) we get a sense that Benjamini-Hochberg is surprisingly robust under correlation.  At the same time, there are cases when BH erroneously produces a large number of false discoveries.  Therefore, we take a close look at those data sets BH fails on.

## Simulation

```{r, cache = TRUE}
z = read.table("../output/z_null_liver_777.txt")
p = read.table("../output/p_null_liver_777.txt")
n = dim(z)
```

```{r, cache = TRUE}
pihat0 = read.table("../output/pihat0_z_null_liver_777.txt")
pihat0 = as.numeric(t(pihat0))
```


```{r, cache = TRUE}
fd.bh = c()

for (i in 1 : n[1]) {
  p_BH = p.adjust(p[i, ], method = "BH")
  fd.bh[i] = sum(p_BH <= 0.05)
}
```


## Result

We take a look that all data sets where BH erroneously produces at least one false discovery (green), compared with $\hat\pi_0$ produced by `ash` on these same data sets.

```{r, cache = TRUE}
fdn = sum(fd.bh >= 1)
I = order(fd.bh, decreasing = TRUE)[1:fdn]
x = seq(-10, 10, 0.01)
y = dnorm(x)
k = 1
m = n[2]
for (j in I) {
  cat("N0.", k, ": Data Set", j, "; Number of False Discoveries:", fd.bh[j], "; pihat0 =", pihat0[j])
  hist(as.numeric(z[j, ]), xlab = "z scores", freq = FALSE, ylim = c(0, 0.45), nclass = 100, main = "10000 z scores, 100 bins")
  lines(x, y, col = "red")
  qqnorm(as.numeric(z[j, ]), main = "Normal Q-Q plot for z scores")
  abline(0, 1)
  plot(sort(as.numeric(p[j, ])), xlab = "Order", ylab = "Ordered p value", main = "All p values")
  abline(0, 1 / m, col = "blue")
  abline(0, 0.05 / m, col = "red")
  legend("top", lty = 1, col = c("blue", "red"), c("Uniform", "BH, FDR = 0.05"))
  
  pj = sort(as.numeric(p[j, ]))

  plot(pj[1:max(100, fd.bh[j])], xlab = "Order", ylab = "Ordered p value", main = "Zoom-in to 100 smallest p values", ylim = c(0, pj[max(100, fd.bh[j])]))
  abline(0, 1 / m, col = "blue")
  points(pj[1:fd.bh[j]], col = "green", pch = 19)
  abline(0, 0.05 / m, col = "red")
  legend("top", lty = 1, col = c("blue", "red"), c("Uniform", "BH, FDR = 0.05"))
  
  plot(pj[pj <= 0.01], xlab = "Order", ylab = "Ordered p value", main = "Zoom-in to p values <= 0.01", ylim = c(0, 0.01))
  abline(0, 1 / m, col = "blue")
  points(pj[1:fd.bh[j]], col = "green", pch = 19)
  abline(0, 0.05 / m, col = "red")
  legend("top", lty = 1, col = c("blue", "red"), c("Uniform", "BH, FDR = 0.05"))
  
  plot(pj[pj <= 0.05], xlab = "Order", ylab = "Ordered p value", main = "Zoom-in to p values <= 0.05", ylim = c(0, 0.05))
  abline(0, 1 / m, col = "blue")
  points(pj[1:fd.bh[j]], col = "green", pch = 19)
  abline(0, 0.05 / m, col = "red")
  legend("top", lty = 1, col = c("blue", "red"), c("Uniform", "BH, FDR = 0.05"))
  
  k = k + 1
}
```


## Session Information

```{r session-info}
```
