---
title: "Simulating Design Matrix $X$: Correlation patterns"
author: "Lei Sun"
date: 2018-02-05
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

## Introduction

For a fixed design matrix $X$, $\hat\beta \sim N(\beta, \sigma_e^2(X^TX)^{-1})$, and the empirical distribution of $\hat z_j = \hat\beta_j / \hat{\text{SE}}(\hat\beta_j)$ under the null will depend on the average correlation in $(X^TX)^{-1}$.

Actually the most important quantity to determine the shape of the empirical distribution of $\hat z_j$ is the square root of the mean squared correlation among $\hat\beta_j$'s, that is, $\sqrt{\overline{\rho_{\hat\beta_i, \hat\beta_j}^2}}$.

Now we are taking a look at this quantity for some commonly used design matrix in linear regression simulations.

In all three settings, each row of $X_{n \times p}$ is independently drawn from a $N(0, \Sigma)$ distribution, where the diagonal elements of $\Sigma$ are all one. Then the columns of $X$ are normalized such that $\|X_j\|_2^2 = 1$.

```{r, echo = FALSE}
n <- 3000
p <- 1000
```

## Independent and normalized columns

- $\Sigma = I$.

```{r, echo = FALSE, cache = TRUE}
set.seed(777)
## independent X columns
X <- matrix(rnorm(n * p), n, p)
## column normalization
X <- t(t(X) / sqrt(colSums(X^2)))
Sigma.betahat <- solve(crossprod(X))
Rho.betahat <- cov2cor(Sigma.betahat)
sqroot.avg.sq.rho.betahat.indep <- (sum(Rho.betahat^2) - p) / (p * (p - 1))
sebetahat <- sqrt(diag(Sigma.betahat))
hist(sebetahat, xlab = expression(SE(hat(beta))))
```

## Toeplitz column correlation

- $\Sigma_{ij} = \rho^{|i - j|}$

### $\text{SE}\left(\hat\beta_j\right)$

```{r, echo = FALSE, cache = TRUE}
sqroot.avg.sq.rho.betahat <- sqroot.avg.sq.rho.X <- c()
mean.sebetahat <- sd.sebetahat <- c()
i <- 1
set.seed(777)
for (rho in seq(0.01, 0.99, by = 0.01)) {
  ## generate correlation matrix of X columns
  Sigma.X <- toeplitz(rho^(0 : (p - 1)))
  Rho.X <- cov2cor(Sigma.X)
  sqroot.avg.sq.rho.X[i] <- (sum(Rho.X^2) - p) / (p * (p - 1))
  ## generate correlated X columns
  X <- matrix(rnorm(n * p), n, p) %*% chol(Rho.X)
  ## column normalization
  X <- t(t(X) / sqrt(colSums(X^2)))
  Sigma.betahat <- solve(crossprod(X))
  Rho.betahat <- cov2cor(Sigma.betahat)
  sqroot.avg.sq.rho.betahat[i] <- (sum(Rho.betahat^2) - p) / (p * (p - 1))
  sebetahat <- sqrt(diag(Sigma.betahat))
  mean.sebetahat[i] <- mean(sebetahat)
  sd.sebetahat[i] <- sd(sebetahat)
  i <- i + 1
}
```

```{r, echo = FALSE}
sqroot.avg.sq.rho.betahat.toeplitz <- sqroot.avg.sq.rho.betahat
par(mar = c(4.5, 5, 2, 0.5))
plot(seq(0.01, 0.99, by = 0.01), mean.sebetahat, xlab = expression(rho), ylab = expression(bar(SE(hat(beta[j])))))
plot(seq(0.01, 0.99, by = 0.01), sd.sebetahat, xlab = expression(rho), ylab = expression(SD(SE(hat(beta[j])))))
```

### Average orrelation among $X_j$ and $\hat\beta_j$

```{r, echo = FALSE}
par(mar = c(4.5, 5, 2, 0.5))
plot(seq(0.01, 0.99, by = 0.01), sqroot.avg.sq.rho.X, xlab = expression(rho), ylab = expression(sqrt(bar(rho[ij]^2))), type = "o", pch = 17, main = expression(Cor(X)), cex = 0.2)
plot(seq(0.01, 0.99, by = 0.01), sqroot.avg.sq.rho.betahat, xlab = expression(rho), ylab = expression(sqrt(bar(rho[ij]^2))), type = "o", pch = 2, main = expression(Cor(hat(beta))), cex = 0.2)
abline(h = sqroot.avg.sq.rho.betahat.indep, lty = 2, col = "green")
sqroot.avg.sq.rho.betahat.toeplitz <- sqroot.avg.sq.rho.betahat
```

## Factor model column correlation

- $\Sigma = \texttt{cov2cor}(B_{p \times d}B_{d\times p}^T + I)$

### $\text{SE}\left(\hat\beta_j\right)$

```{r, echo = FALSE, cache = TRUE}
sqroot.avg.sq.rho.betahat <- sqroot.avg.sq.rho.X <- c()
mean.sebetahat <- sd.sebetahat <- c()
i <- 1
set.seed(777)
for (d in 1 : 1000) {
  ## generate correlation matrix of X columns
  B <- matrix(rnorm(p * d, 0, 1), p, d)
  Sigma.X <- tcrossprod(B) + diag(p)
  Rho.X <- cov2cor(Sigma.X)
  sqroot.avg.sq.rho.X[i] <- (sum(Rho.X^2) - p) / (p * (p - 1))
  ## generate correlated X columns
  X <- matrix(rnorm(n * p), n, p) %*% chol(Rho.X)
  X <- t(t(X) / sqrt(colSums(X^2)))
  Sigma.betahat <- solve(crossprod(X))
  Rho.betahat <- cov2cor(Sigma.betahat)
  sqroot.avg.sq.rho.betahat[i] <- (sum(Rho.betahat^2) - p) / (p * (p - 1))
  sebetahat <- sqrt(diag(Sigma.betahat))
  mean.sebetahat[i] <- mean(sebetahat)
  sd.sebetahat[i] <- sd(sebetahat)
  i <- i + 1
}
```

```{r, echo = FALSE}
par(mar = c(4.5, 5, 2, 0.5))
plot(1 : 1000, mean.sebetahat, xlab = expression(d), ylab = expression(bar(SE(hat(beta[j])))))
plot(1 : 1000, sd.sebetahat, xlab = expression(d), ylab = expression(SD(SE(hat(beta[j])))))
```

### Average correlation among $X_j$ and $\hat\beta_j$.

```{r, echo = FALSE}
par(mar = c(4.5, 5, 2, 0.5))
plot(1 : 1000, sqroot.avg.sq.rho.X, xlab = expression(d), ylab = expression(sqrt(bar(rho[ij]^2))), type = "o", pch = 17, main = expression(Cor(X)), cex = 0.2)
plot(1 : 1000, sqroot.avg.sq.rho.betahat, xlab = expression(d), ylab = expression(sqrt(bar(rho[ij]^2))), type = "o", pch = 2, main = expression(Cor(hat(beta))), cex = 0.2, ylim = range(sqroot.avg.sq.rho.betahat, sqroot.avg.sq.rho.betahat.toeplitz, sqroot.avg.sq.rho.betahat.indep))
lines(seq(1, 1000, length = 99), sqroot.avg.sq.rho.betahat.toeplitz, lty = 2, col = "blue")
abline(h = sqroot.avg.sq.rho.betahat.indep, lty = 2, col = "green")
```

## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
