---
title: "Diagnostic Plot for `ASH`"
author: "Lei Sun"
date: 2017-05-05
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

## Introduction

Based on discussion with Matthew on several ideas to improve the diagnostic plot for `ASH`, this file documents the latest version of `plot_diagnostic` function in `ashr`.

```{r, cache = TRUE, cache = TRUE, message = FALSE}
library(ashr)
```

## $\alpha = 0.01$ rather than $0.05$.

The idea is to "reduce the number of crossings some, but still give a good idea of what is expected without being too conservative."

```{r 0.01, cache = TRUE, echo = FALSE}
set.seed(777)
n = 1e4
upper = qbeta(0.995, 1:n, n + 1 - (1:n)) - (1:n) / (n + 1)
lower = qbeta(0.005, 1:n, n + 1 - (1:n)) - (1:n) / (n + 1)
for (i in 1:10) {
  n = 1e4
  z.normal = rnorm(n)
  fit.normal = ash.workhorse(z.normal, 1, method = "fdr", mixcompdist = "normal")
  cdfhat.normal = plot_diagnostic(fit.normal, plot.it = FALSE)
  diff = sort(cdfhat.normal) - (1:n) / (n + 1)
  ylim = range(diff, upper, lower, 0)
  plot(diff, cex = 0.1, pch = 19, ylim = ylim, ylab = expression(X[(k)] - E(X[(k)])), main = "De-trended Diagnostic Plot for ASH")
  abline(h = 0, col = "red", lty = 2)
  lines(upper, col = "red")
  lines(lower, col = "red")
}
```

## Other ideas

All have been put into the `ashr::plot_diagnostic` function.

## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
