---
title: "Diagnostic Plots for `BH`-friendly, `lfsr`-hostile Correlated $N(0, 1)$ Scores"
author: "Lei Sun"
date: 2017-04-23
output: workflowr::wflow_html
---





## Introduction

We take a look at those data sets where `BH` produces few (false) discoveries, and at the same time, `ASH`'s `lfsr` produces many (false) discoveries.  For each data set, $z$ scores, $p$ values, and diagnostic $\hat F_j$ are plotted.

```{r, cache = TRUE, message = FALSE}
library(ashr)
z = read.table("../output/z_null_liver_777.txt")
p = read.table("../output/p_null_liver_777.txt")
pihat0 = as.numeric(unlist(read.table("../output/pihat0_z_null_liver_777.txt")))
fd.bh = as.numeric(unlist(read.table("../output/fd.bh.0.05_null_liver_777.txt")))
fd.lfsr = as.numeric(unlist(read.table("../output/fd.lfsr.0.05.z.normal_null_liver_777.txt")))
```

```{r, cache = TRUE, echo = FALSE}
n = nrow(z)
m = ncol(p)
```

```{r, cache = TRUE, echo = FALSE}
ind.lfsr = intersect(
  intersect(order(fd.lfsr, decreasing = TRUE),
            which(fd.lfsr != 0)),
  which(fd.bh == 0))
ind.bh = intersect(
  intersect(order(fd.bh, decreasing = TRUE),
            which(fd.bh != 0)),
  which(fd.lfsr == 0))
```

## The 118 data sets where `BH` didn't produce false discoveries but `lfsr` does.

In this simulation, `BH` used the FDR level $\alpha = 0.05$, whereas `ASH` declared a discovery when `lfsr` $\leq 0.05$.

```{r, cache = TRUE, echo = FALSE}
x = seq(-10, 10, 0.01)
y = dnorm(x)
k = 1
for (j in ind.lfsr) {
  fit.ash.n.n = ash.workhorse(as.numeric(z[j, ]), 1, mixcompdist = "normal", method = "fdr")
  fit.ash.n.u = ash.workhorse(as.numeric(z[j, ]), 1, mixcompdist = "uniform", method = "fdr")
  fit.ash.n.hu = ash.workhorse(as.numeric(z[j, ]), 1, mixcompdist = "halfuniform", method = "fdr")
  cat("N0.", k, ": Data Set", j, "; Number of False Discoveries by BH:", fd.bh[j], "; Number of False Discoveries by ASH's lfsr:", fd.lfsr[j], "; pihat0 =", get_pi0(fit.ash.n.n))
  hist(as.numeric(z[j, ]), xlab = "z scores", freq = FALSE, ylim = c(0, 0.45), nclass = 100, main = "10000 z scores, 100 bins")
  lines(x, y, col = "red")
  qqnorm(as.numeric(z[j, ]), main = "Normal Q-Q plot for z scores")
  ind.z = order(abs(as.numeric(z[j, ])), decreasing = TRUE)[1 : fd.lfsr[j]]
  points(qnorm(ppoints(m)[order(order(as.numeric(z[j, ])))][ind.z]), as.numeric(z[j, ])[ind.z], col = "green", pch = 19)
  abline(0, 1, lty = 2, col = "red")
  legend("bottomright", pch = 19, col = "green", legend = expression("lfsr "<= 0.05))
  pj = sort(as.numeric(p[j, ]))
  plot(pj[1:max(50, fd.lfsr[j])], xlab = "Order", ylab = "Ordered p value", main = c("All false discoveries by lfsr", "or 50 smallest p values"), pch = 21)
  abline(0, 1 / m, col = "blue")
  points(pj[min(1, fd.lfsr[j]) : fd.lfsr[j]], col = "green", pch = 19)
  abline(0, 0.05 / m, col = "red")
  legend("top", lty = 1, col = c("blue", "red"), c("Uniform", "BH, FDR = 0.05"), bty = "n")
  ashr::plot_diagnostic(fit.ash.n.n, main = c("Diagnostic Plot for ASH", "Normal Mixture Prior"))
  ashr::plot_diagnostic(fit.ash.n.u, main = c("Diagnostic Plot for ASH", "Uniform Mixture Prior"))
  ashr::plot_diagnostic(fit.ash.n.hu, main = c("Diagnostic Plot for ASH", "Half-Uniform Mixture Prior"))
  k = k + 1
}
```

## The 7 data sets where `lfsr` is more conservative than `BH`.

```{r, cache = TRUE, echo = FALSE}
x = seq(-10, 10, 0.01)
y = dnorm(x)
k = 1
for (j in ind.bh) {
  fit.ash.n.n = ash.workhorse(as.numeric(z[j, ]), 1, mixcompdist = "normal", method = "fdr")
  fit.ash.n.u = ash.workhorse(as.numeric(z[j, ]), 1, mixcompdist = "uniform", method = "fdr")
  fit.ash.n.hu = ash.workhorse(as.numeric(z[j, ]), 1, mixcompdist = "halfuniform", method = "fdr")
  cat("N0.", k, ": Data Set", j, "; Number of False Discoveries by BH:", fd.bh[j], "; Number of False Discoveries by ASH's lfsr:", fd.lfsr[j], "; pihat0 =", get_pi0(fit.ash.n.n))
  hist(as.numeric(z[j, ]), xlab = "z scores", freq = FALSE, ylim = c(0, 0.45), nclass = 100, main = "10000 z scores, 100 bins")
  lines(x, y, col = "red")
  qqnorm(as.numeric(z[j, ]), main = "Normal Q-Q plot for z scores")
  ind.z = order(abs(as.numeric(z[j, ])), decreasing = TRUE)[1 : fd.bh[j]]
  points(qnorm(ppoints(m)[order(order(as.numeric(z[j, ])))][ind.z]), as.numeric(z[j, ])[ind.z], col = "green", pch = 19)
  abline(0, 1, lty = 2, col = "red")
  legend("bottomright", pch = 19, col = "green", legend = expression(paste("BH at ", alpha == 0.05)))
  pj = sort(as.numeric(p[j, ]))
  plot(pj[1:max(10, fd.bh[j])], xlab = "Order", ylab = "Ordered p value", main = c("All false discoveries by BH", "or 10 smallest p values"), pch = 21)
  abline(0, 1 / m, col = "blue")
  points(pj[min(1, fd.bh[j]) : fd.bh[j]], col = "green", pch = 19)
  abline(0, 0.05 / m, col = "red")
  legend("top", lty = 1, col = c("blue", "red"), c("Uniform", "BH, FDR = 0.05"), bty = "n")
  ashr::plot_diagnostic(fit.ash.n.n, main = c("Diagnostic Plot for ASH", "Normal Mixture Prior"))
  ashr::plot_diagnostic(fit.ash.n.u, main = c("Diagnostic Plot for ASH", "Uniform Mixture Prior"))
  ashr::plot_diagnostic(fit.ash.n.hu, main = c("Diagnostic Plot for ASH", "Half-Uniform Mixture Prior"))
  k = k + 1
}
```

## Comparison of false discoveries by `BH` and `lfsr`

To get a more comprehensive picture, we plot as follows the numbers of false discoveries by `BH` and `lfsr` for each data set.  These data sets were selected out of $1000$ of them, because they produced at least one false discoveries by either method.  Note that for every data set there are $10K$ correlated null statistics.

```{r, echo = FALSE, cache = TRUE}
ind.bh.lfsr = intersect(
  order(fd.lfsr, decreasing = TRUE),
  union(
    which(fd.lfsr != 0), which(fd.bh != 0)
  )
)
plot(fd.lfsr[ind.bh.lfsr], pch = 19, cex = 0.5, ylab = "Number of False Discoveries", main = "False Discoveries by lfsr and BH")
points(fd.bh[ind.bh.lfsr], pch = 19, cex = 0.5, col = "red")
legend("topright", pch = 19, pt.cex = 0.5, col = c("black", "red"), c("lfsr", "BH"))
```


