---
title: "Diagnostic Plot for `ASH`"
author: "Lei Sun"
date: 2017-05-05
output: workflowr::wflow_html
---





## Introduction

Based on discussion with Matthew on several ideas to improve the diagnostic plot for `ASH`, this file documents the latest version of `plot_diagnostic` function in `ashr`.

```{r, cache = TRUE, cache = TRUE, message = FALSE}
library(ashr)
```

## $\alpha = 0.01$ rather than $0.05$.

The idea is to "reduce the number of crossings some, but still give a good idea of what is expected without being too conservative."

```{r 0.01, cache = TRUE, echo = FALSE}
set.seed(777)
n = 1e4
upper = qbeta(0.995, 1:n, n + 1 - (1:n)) - (1:n) / (n + 1)
lower = qbeta(0.005, 1:n, n + 1 - (1:n)) - (1:n) / (n + 1)
for (i in 1:10) {
  n = 1e4
  z.normal = rnorm(n)
  fit.normal = ash.workhorse(z.normal, 1, method = "fdr", mixcompdist = "normal")
  cdfhat.normal = plot_diagnostic(fit.normal, plot.it = FALSE)
  diff = sort(cdfhat.normal) - (1:n) / (n + 1)
  ylim = range(diff, upper, lower, 0)
  plot(diff, cex = 0.1, pch = 19, ylim = ylim, ylab = expression(X[(k)] - E(X[(k)])), main = "De-trended Diagnostic Plot for ASH")
  abline(h = 0, col = "red", lty = 2)
  lines(upper, col = "red")
  lines(lower, col = "red")
}
```

## Other ideas

All have been put into the `ashr::plot_diagnostic` function.

## Illustration

```{r, cache = TRUE, echo = FALSE}
z = read.table("../output/z_null_liver_777.txt")
```

```{r, cache = TRUE, echo = FALSE}
betahat = as.numeric(z[327, ])
hist(betahat, breaks = 100, prob = TRUE, ylim = c(0, dnorm(0)), xlab = "Correlated Z Scores", main = "Histogram of Correlated Z Scores")
lines(seq(-6, 6, 0.01), dnorm(seq(-6, 6, 0.01)), col = "red")
legend("topleft", lty = 1, col = "red", legend = "N(0, 1)")
fit = ashr::ash(betahat, 1, mixcompdist = "normal", method = "fdr")
plot_diagnostic(fit)
```


