---
title: "FDR / s-value on Correlated Null: Use $z$ scores only"
author: "Lei Sun"
date: 2017-02-10
output: html_document
---

```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

```{r knitr-opts-chunk, include=FALSE}
```

**Last updated:** `r Sys.Date()`

**Code version:** `r workflowr::extract_commit(".", 1)$sha1`

## Introduction

We apply Benjamini–Hochberg's FDR-controlling procedure, `ash`, and `truncash` (with the threshold $T = 1.96$) to the simulated, correlated null data, obtained from 5 vs 5 GTEx/Liver samples and 10K top expressed genes, and $1000$ independent simulation trials.  We compare the numbers of false discoveries (by definition, all discoveries should be false) obtained by these three methods, under FDR $\leq 0.05$ and $s$-value $\leq 0.05$ as cutoffs.

## Simulation: Using $p$ values for [BH] and [BY] procedures; using $z$ scores, converted from $p$ values, for `ash` and `truncash`.

For `ash` and `truncash`, $\hat\beta = \hat z$, $\hat s \equiv 1$.

```{r}
library(ashr)
source("../code/truncash.R")
```

```{r}
t = proc.time()
```

```{r, cache = TRUE}
p = read.table("../output/p_null_liver_777.txt")
t = read.table("../output/t_null_liver_777.txt")
z = read.table("../output/z_null_liver_777.txt")

m = dim(p)[1]
n = dim(p)[2]
fd.bh = fd.by = fd.ash = fd.truncash = c()

for (i in 1:m) {
  p_BH = p.adjust(p[i, ], method = "BH")
  fd.bh[i] = sum(p_BH <= 0.05)
  p_BY = p.adjust(p[i, ], method = "BY")
  fd.by[i] = sum(p_BY <= 0.05)
  betahat = -as.numeric(z[i, ])
  sebetahat = rep(1, n)
  fit.ash = ashr::ash(betahat, sebetahat, method = "fdr", mixcompdist = "normal")
  fd.ash[i] = sum(ashr::get_svalue(fit.ash) <= 0.05)
  fit.truncash = truncash(betahat, sebetahat, t = qnorm(0.975))
  fd.truncash[i] = sum(get_svalue(fit.truncash) <= 0.05)
}
```

```{r}
proc.time() - t
```

[BH]: https://www.jstor.org/stable/2346101
[BY]: https://projecteuclid.org/euclid.aos/1013699998

## Session Information

```{r session-info}
```
