---
title: "FDR / $s$ value on Correlated Null: `betahat = zscore`, `sebetahat = 1`"
author: "Lei Sun"
date: 2017-02-10
output: workflowr::wflow_html
---


**Last updated:** `r Sys.Date()`

**Code version:** `r workflowr::extract_commit(".", 1)$sha1`

## Introduction

Apply two FDR-controlling procedures, Benjamini–Hochberg 1995 ("[BH]") and Benjamini-Yekutieli 2001 ("[BY]"), and two $s$ value models, `ash` and `truncash` (with the threshold $T = 1.96$) to the simulated, correlated null data.  The data are obtained from 5 vs 5 GTEx/Liver samples and 10K top expressed genes, and $1000$ independent simulation trials.

Compare the numbers of false discoveries (by definition, all discoveries should be false) obtained by these four methods, using FDR $\leq 0.05$ and $s$-value $\leq 0.05$ as cutoffs.

## Simulation: $p$ values for [BH] and [BY] procedures; $\hat\beta = \hat z$, $\hat s \equiv 1$, for `ash` and `truncash`.

**$\hat z$ obtained from [the last step of the pipeline](nullpipeline.html).**

```{r}
library(ashr)
source("../code/truncash.R")
```

```{r, cache = TRUE}
p = read.table("../output/p_null_liver_777.txt")
t = read.table("../output/t_null_liver_777.txt")
z = read.table("../output/z_null_liver_777.txt")

m = dim(p)[1]
n = dim(p)[2]
fd.bh = fd.by = fd.ash = fd.truncash = c()

for (i in 1:m) {
  p_BH = p.adjust(p[i, ], method = "BH")
  fd.bh[i] = sum(p_BH <= 0.05)
  p_BY = p.adjust(p[i, ], method = "BY")
  fd.by[i] = sum(p_BY <= 0.05)
  betahat = -as.numeric(z[i, ])
  sebetahat = rep(1, n)
  fit.ash = ashr::ash(betahat, sebetahat, method = "fdr", mixcompdist = "normal")
  fd.ash[i] = sum(ashr::get_svalue(fit.ash) <= 0.05)
  fit.truncash = truncash(betahat, sebetahat, t = qnorm(0.975))
  fd.truncash[i] = sum(get_svalue(fit.truncash) <= 0.05)
}
```

## Result

Simulated under the global null, FWER $=$ FDR.

### Estimated FWER or FDR by BH

```{r}
fdr.bh = mean(fd.bh >= 1)
fdr.bh
```

Estimated FWER or FDR by BY
```{r}
fdr.by = mean(fd.by >= 1)
fdr.by
```

Estimated FWER or FDR by `ash`
```{r}
fdr.ash = mean(fd.ash >= 1)
fdr.ash
```

Estimated FWER or FDR by `truncash`
```{r}
fdr.truncash = mean(fd.truncash >= 1)
fdr.truncash
```

### Happenstance of false discoveries by four approaches

```{r}
maxcount = max(c(fd.bh, fd.by, fd.ash, fd.truncash))
xlim = c(0, maxcount)
maxfreq = max(c(max(table(fd.bh)), max(table(fd.by)), max(table(fd.ash)), max(table(fd.truncash))))
ylim = c(0, maxfreq)
plot(table(fd.bh), xlab = "Number of False Discoveries / 10K", ylab = "Frequency", main = "Benjamini - Hochberg 1995", xlim = xlim, ylim = ylim)
plot(table(fd.by), xlab = "Number of False Discoveries / 10K", ylab = "Frequency", main = "Benjamini - Yekutieli 2001", xlim = xlim, ylim = ylim)
plot(table(fd.ash), xlab = "Number of False Discoveries / 10K", ylab = "Frequency", main = "ash", xlim = xlim, ylim = ylim)
plot(table(fd.truncash), xlab = "Number of False Discoveries / 10K", ylab = "Frequency", main = "truncash", xlim = xlim, ylim = ylim)
```

### Comparison of the numbers of false discoveries by four approaches

```{r}
m = length(fd.bh)
fd.ind = (1:m)[!((fd.bh == 0) & (fd.by == 0) & (fd.ash == 0) & (fd.truncash == 0))]
plot(1:length(fd.ind), fd.bh[fd.ind], pch = 4, ylim = xlim, xlab = "Trials with False Discoveries", ylab = "Number of False Discoveries / 10K")
points(1:length(fd.ind), fd.by[fd.ind], pch = 4, col = 2)
points(1:length(fd.ind), fd.ash[fd.ind], pch = 4, col = 3)
points(1:length(fd.ind), fd.truncash[fd.ind], pch = 4, col = 4)
legend("topright", c("BH", "BY", "ash", "truncash"), col = 1:4, pch = 4)
```

[BH]: https://www.jstor.org/stable/2346101
[BY]: https://projecteuclid.org/euclid.aos/1013699998

## Session Information

