---
title: "Empirical Null with Gaussian Derivatives: Large Correlation"
author: "Lei Sun"
date: 2017-03-26
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

## Can $K$ be too small?

[Another assumption](gaussian_derivatives.rmd) to make the problem tractable is that the pairwise correlation $\rho_{ij}$ is moderate enough so $W_k\varphi^{(k)}$ vanishes as the order $k$ increases.  With this assumption we can stop at a sufficiently large $K$ without consideration higher order Gaussian derivatives.  But what if $\rho_{ij}$ is large?

## Extreme case: $\rho_{ij} \equiv 1$

When we have perfect correlation among all $z$ scores, the approximate limit observed density $f_0(x)\to\delta_z(x) = \delta(x-z)$.  That is, with probability one, we observe $z_1 = \cdots = z_n = z$, as $n\to\infty$, $f_0(x)$ goes to a Dirac delta function peak at the observed $z$, and zero elsewhere.  Now the question is, can this Dirac delta function be decomposed with the Gaussian $\varphi$ and its derivatives $\varphi^{(k)}$, so that we still have

$$
f_0(x) = \delta(x - z) = \varphi(x)\sum\limits_{k = 0}^\infty W_kh_k(x)
$$
with appropriate $W_k$'s?

Using the orthogonality of Hermite functions, [we have](gaussian_derivatives.html#gaussian_derivatives_and_hermite_polynomials)

$$
W_k = \frac{1}{k!}\int_{-\infty}^{\infty}h_k(x)f_0(x)dx = \frac{1}{k!}\int_{-\infty}^{\infty}h_k(x)\delta(x-z)dx = \frac{1}{k!}h_k(z)
$$
Now the decomposition $\varphi(x)\sum\limits_{k = 0}^\infty W_kh_k(x)$ becomes

$$
\varphi(x)\sum\limits_{k = 0}^\infty \frac{1}{k!}h_k(z)h_k(x)
$$
It turns out this equation is connected to [Mehler's formula](https://en.wikipedia.org/wiki/Mehler_kernel) which can be [shown](https://en.wikipedia.org/wiki/Hermite_polynomials#Completeness_relation) to give the identity

$$
\sum\limits_{k = 0}^\infty \psi_k(x)\psi_k(z) = \delta(x - z)
$$
where $\psi_k$'s are the [Hermite functions](https://en.wikipedia.org/wiki/Hermite_polynomials#Hermite_functions) defined as

$$
\begin{array}{rrcl}
& \psi_k(x) &=& (k!)^{-1/2}(\sqrt{\pi})^{-1/2}e^{-x^2/2}h_k(\sqrt{2}x)\\
\Rightarrow & h_k(x) &=& (k!)^{1/2}(\sqrt{\pi})^{1/2}e^{x^2/4}\psi_k\left(\frac x{\sqrt{2}}\right)\\
\Rightarrow & \varphi(x)\sum\limits_{k = 0}^\infty \frac{1}{k!}h_k(z)h_k(x) & =&
\frac1{\sqrt{2}}e^{-\frac{x^2}4+\frac{z^2}4}\sum\limits_{k = 0}^\infty
\psi_k\left(\frac x{\sqrt{2}}\right)\psi_k\left(\frac z{\sqrt{2}}\right)\\
& &=&
\frac1{\sqrt{2}}e^{-\frac{x^2}4+\frac{z^2}4}
\delta\left(\frac{x - z}{\sqrt{2}}\right)
\end{array}
$$
Note that the Dirac delta function has a property that $\delta(\alpha x) = \delta(x) / |\alpha| \Rightarrow \frac1{\sqrt{2}}\delta\left(\frac{x - z}{\sqrt{2}}\right) = \delta(x - z)$.  Therefore,

$$
\varphi(x)\sum\limits_{k = 0}^\infty \frac{1}{k!}h_k(z)h_k(x)
=
\delta(x-z)\exp\left(-\frac{x^2}4+\frac{z^2}4\right)
$$
Note that $\exp\left(-\frac{x^2}4+\frac{z^2}4\right)$ is bounded for any $z\in\mathbb{R}$, so $\delta(x-z)\exp\left(-\frac{x^2}4+\frac{z^2}4\right)$ vanishes to $0$ for any $x\neq z$, and

$$
\int_{-\infty}^\infty \delta(x-z)\exp\left(-\frac{x^2}4+\frac{z^2}4\right)dx = 
\exp\left(-\frac{z^2}4+\frac{z^2}4\right) = 1
$$
Hence, in essence, $\delta(x-z)\exp\left(-\frac{x^2}4+\frac{z^2}4\right) = \delta(x-z)$.  Therefore we have
$$
f_0(x) = \varphi(x)\sum\limits_{k = 0}^\infty W_kh_k(x)
=
\varphi(x)\sum\limits_{k = 0}^\infty \frac{1}{k!}h_k(z)h_k(x)
=\delta(x -z)
$$
when 
$$
W_k = \frac{1}{k!}h_k(z)
$$
Thus we show that the Dirac delta function can be decomposed by Gaussian density and its derivatives.

### Visualization with finite $K$

With Gaussian and its infinite orders of derivatives, we can compose a Dirac delta function at any position, yet what happens if we stop at a finite $K$?  Let $f_0^K$ be the approximation of $f_0 = \delta_z$ with first $K$ Gaussian derivatives.  That is,

$$
f_0^K(x) = \varphi(x)\sum\limits_{k = 0}^K \frac{1}{k!}h_k(z)h_k(x) \ .
$$
Meanwhile, let $F_0^K(x) = \int_{-\infty}^x f_0^K(u)du$.  It's easy to shown that

$$
F_0^K(x) = \Phi(x) - \varphi(x)\sum\limits_{k = 1}^K W_k h_{k - 1}(x) = \Phi(x) - \varphi(x) \sum\limits_{k = 1}^K \frac{1}{k!}h_k(z) h_{k - 1}(x) \ .
$$

Theoretically, $f_0^K$ is an approximation to empirical density of perfectly correlated $z$ scores; hence, as $K\to\infty$, $f_0^K\to\delta_z$.  Similarly, $F_0^K$ is an approximation to empirical cdf of perfectly correlated $z$ scores; hence, as $K\to\infty$, $f_0^K$ should converge to the $0$-$1$ step function, and the location of the step is the observed $z$.

In practice, the convergence is not fast.  As we can see from the following visualization, the difference between $f_0^K$ and $\delta_z$, as well as that between $F_0^K$ and the step function, is still conspicuous even if $K = 20$, which is about the highest order `R` can reasonbly handle in the current implementation.  Therefore, at least in theory it's possible that $K$ can be too small.

**Note that the oscillation near the presumptive step may be connected with [Gibbs phenomenon](https://en.wikipedia.org/wiki/Gibbs_phenomenon).**


```{r, cache = TRUE, echo = FALSE}
z = c(-1, 0, 2)
x = seq(-max(abs(min(z) - 3), abs(max(z) + 3)), max(abs(min(z) - 3), abs(max(z) + 3)), 0.01)
K = c(1, 10, 20)
H = sapply(1:max(K), EQL::hermite, x = x)
```

```{r, cache = TRUE, echo = FALSE}
K = c(1, 2, 3, 4, 10, 20)
col.0 = "red"
col.inf = "black"
col = colorRampPalette(c(col.inf, col.0))(length(K) + 2)[-c(1, length(K) + 2)]
# col = gray(0 : (length(K) - 1) / length(K))
for (zscore in z) {
  cat("Under perfect correlation, observed z scores =", zscore, "\n")
  if (is.element(zscore, x)) {
    w = H[which(x == zscore), ]
  } else {
    w = hermite(x = zscore, n = 1:max(K))
  }
  w = w / factorial(1:max(K))
  plot(x, (H %*% w + 1) * dnorm(x), type = "n", xlab = "x", ylab = expression(f[0]^K~(x)), main = bquote(f[0]^K~"when observed z scores ="~.(zscore)))
  lines(x, dnorm(x), col = col.0)
  i = 1
  for (k in sort(K, decreasing = TRUE)) {
    lines(x, (cbind(H[, 1:k]) %*% w[1:k] + 1) * dnorm(x), col = col[i])
    i = i + 1
  }
  segments(zscore, 0, zscore, par('usr')[4] + 1, col = col.inf)
  segments(min(x), 0, max(x), 0, col = col.inf)
  legend("topright", lty = 1, col = c(col.0, rev(col), col.inf), legend = c(expression(paste("K = 0, ", varphi)), paste("K =", K), expression(paste("K = ", infinity, ", ", delta[z]))))
  plot(x, x, type = "n", xlab = "x", ylab = expression(F[0]^K~(x)), main = bquote(F[0]^K~"when observed z scores ="~.(zscore)), ylim = c(-0.4, 1.1))
  lines(x, pnorm(x), col = col.0)
  i = 1
  for (k in sort(K, decreasing = TRUE)) {
    lines(x, pnorm(x) - cbind(cbind(1, H)[, 1:k]) %*% w[1:k] * dnorm(x), col = col[i])
    i = i + 1
  }
  abline(h = 0, lty = 3, col = col.inf)
  abline(h = 1, lty = 3, col = col.inf)
  segments(min(x), 0, zscore, 0, col = col.inf)
  segments(zscore, 0, zscore, 1, col = col.inf)
  segments(zscore, 1, max(x), 1, col = col.inf)
  legend("right", y = 0.9, lty = 1, col = c(col.0, rev(col), col.inf), legend = c(expression(paste("K = 0, ", Phi)), paste("K =", K), expression(paste("K = ", infinity))))
}
```

## Fitting experiments when $\rho_{ij}$ is large

As previous theoretical result indicates, when $\rho$ is large, a large $K$ is probably needed.  However, on the other hand, when $\rho$ is large, the effective sample size is small.  Indeed when $\rho\equiv1$, the sample size is essentially $1$.

Let's take a look at some examples with pairwise correlations of $z$ scores $\rho_{ij}\equiv\rho$, $\rho$ moderate to high.  Such $z$ scores can be simulated as $z_i = \epsilon\sqrt{\rho} + e_i\sqrt{1-\rho}$, where $\epsilon, e_i$ are iid $N(0, 1)$.

```{r, cache = TRUE}
n = 1e4
rho = 0.5
set.seed(777)
z = rnorm(1) * sqrt(rho) + rnorm(n) * sqrt(1 - rho)
```

```{r, cache = TRUE, results = "hide", message = FALSE}
source("../code/ecdfz.R")
fit.ecdfz = ecdfz.optimal(z)
```

```{r, cache = TRUE, include = FALSE}
x = seq(-3, 3, 0.01)
H = sapply(1:6, EQL::hermite, x = x)
```

When $\rho = 0.5$, current implementation with $K = 5$ fits positively correlationed z scores reasonably well.

```{r, cache = TRUE, echo = FALSE}
cat(n, "z scores with pairwise correlation =", rho)
hist(z, prob = TRUE, xlim = range(x), breaks = 100)
lines(x, dnorm(x), col = "red")
lines(x, (H[, 1:5] %*% fit.ecdfz$res[[5]]$primal_values[[1]] + 1) * dnorm(x), col = "blue")
legend("topleft", lty = 1, col = c('red', 'blue'), c('K = 0', 'K = 5'))
```

However, as $\rho$ gets larger, current implementation usually fails to find a good $K$ before the algorithm goes unstable, as illustrated in the following $\rho = 0.7$ plot.  $K = 3$ is obviously not enough, yet $K = 4$ has already gone wildly unstable.

```{r, cache = TRUE, result = "hide"}
n = 1e4
rho = 0.7
set.seed(777)
z = rnorm(1) * sqrt(rho) + rnorm(n) * sqrt(1 - rho)
```

```{r, cache = TRUE, result = "hide", message = FALSE}
source("../code/ecdfz.R")
fit.ecdfz = ecdfz.optimal(z)
```

```{r, cache = TRUE, echo = FALSE}
cat(n, "z scores with pairwise correlation =", rho)
hist(z, prob = TRUE, xlim = range(x), breaks = 100)
lines(x, dnorm(x), col = "red")
col = c("yellow", "green", "blue")
for (i in 2:4) {
  lines(x, (H[, 1:i] %*% fit.ecdfz$res[[i]]$primal_values[[1]] + 1) * dnorm(x), col = col[i - 1])
}
legend("topleft", lty = 1, col = c('red', col), paste("K =", c(0, 2:4)))
```

When $\rho = 0.9$, the observed $z$ scores are so concentrated in a small range, even if we have $10,000$ of them, making the effective sample size hopelessly small.  Current implementation can't even handle this data set; it goes crazy when $K = 2$.

```{r, cache = TRUE, result = "hide"}
n = 1e4
rho = 0.9
set.seed(777)
z = rnorm(1) * sqrt(rho) + rnorm(n) * sqrt(1 - rho)
```

```{r, cache = TRUE, result = "hide", message = FALSE}
source("../code/ecdfz.R")
fit.ecdfz = ecdfz(z, 2)
```

```{r, cache = TRUE, echo = FALSE}
cat(n, "z scores with pairwise correlation =", rho)
hist(z, prob = TRUE, xlim = range(x), breaks = 100)
lines(x, dnorm(x), col = "red")
lines(x, (H[, 1:2] %*% fit.ecdfz$res[[1]]$primal_values[[1]] + 1) * dnorm(x), col = "blue")
legend("topleft", lty = 1, col = c('red', "blue"), paste("K =", c(0, 2)))
```


## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
