---
title: "Approximating the Delta function by Gaussian Derivatives"
author: "Lei Sun"
date: 2017-05-10
output: workflowr::wflow_html
---





## Introduction

[Theoretically](gaussian_derivatives_4.html), the Dirac delta function $\delta_z$ can be approximated by infinite orders of Gaussian derivatives as follows,

$$
\delta_z = \sum\limits_{l = 0}^\infty \frac{1}{\sqrt{l!}}h_l\left(z\right) 
\left(\frac{1}{\sqrt{l!}}h_l\left(x\right)\varphi(x)\right) \ .
$$
Previously with the `EQL::hermite` function, it takes a very long time to evaluate an Hermite polynomial of a high degree, yet the `PolynomF` package provides a computationally efficient way to check if higher order Gaussian derivatives indeed approximate $\delta_z$ at any $z$.

With finite $L$, we are looking at

$$
f_L\left(x\right) := 
\sum\limits_{l = 0}^L
\frac{1}{\sqrt{l!}}h_l\left(z\right)
\left(
\frac{1}{\sqrt{l!}}h_l\left(x\right)
\varphi\left(x\right)
\right)
$$
and

$$
F_L\left(x\right) := \Phi\left(x\right) - 
\sum\limits_{l = 1}^L
\frac{1}{\sqrt{l}}
\frac{1}{\sqrt{l!}}h_l\left(z\right) 
\left(
\frac{1}{\sqrt{\left(l - 1\right)!}}h_{l - 1}\left(x\right)\varphi\left(x\right)\right) \ .
$$
Given any $z$, $f_L$ should get closer to $\delta_z$ and $F_L$ to the $0$-$1$ step function, as $L\to\infty$.

```{r, message = FALSE, cache = TRUE, echo = FALSE}
source("../code/gdash.R")
```

```{r, cache = TRUE, echo = FALSE}
## Give a n \times {L + 1} matrix of normalized gaussian derivatives evaluated at the n-vector z
F.mat = function (z, L) {
  hermite = Hermite(L)
  gd.norm = function (z, l) {
  return(dnorm(z) * hermite[[l]](z) / sqrt(factorial(l)))
}
  F.mat = matrix(0, nrow = length(z), ncol = L)
  for (i in 1 : L) {
    F.mat[, i] = gd.norm(z, i)
  }
  F.mat = cbind(dnorm(z), F.mat)
  return(F.mat)
}

hz = function (z, L) {
  hermite = Hermite(L)
  hz = c()
  for (l in 1 : L) {
    hz[l] = hermite[[l]](z) / sqrt(factorial(l))
  }
  hz = c(1, hz)
}

fL = function(z, x, L) {
  F.mat.x = F.mat(x, L)
  w = hz(z, L)
  return(F.mat.x %*% w)
}

FL = function(z, x, L) {
  F.mat.x = F.mat(x, L - 1)
  w = hz(z, L)[-1] / sqrt(1 : L)
  return(pnorm(x) - F.mat.x %*% w)
}

L.plot = function(z, fun, x.seq, L.seq, col.0 = "red", col.Inf = "black") {
  Fun = match.fun(fun)
  y.seq = list()
  for (l in 1 : length(L.seq)) {
    y.seq[[l]] = Fun(z, x.seq, L.seq[l])
  }
  ymax = max(unlist(y.seq))
  ymin = min(unlist(y.seq))
  plot(x.seq, x.seq, type = "n", xlab = "x", ylim = c(ymin, ymax), main = "", ylab = "")
  col = grDevices::colorRampPalette(c(col.0, col.inf))(length(L.seq) + 2)[-c(1, length(L.seq) + 2)]
  for (l in 1 : length(L.seq)) {
    lines(x.seq, y.seq[[l]], col = col[l])
  }
  if (fun == "fL") {
    title(main = bquote(paste("Approximating ", delta[.(z)], " with L Gaussian Derivatives")), ylab = expression(f[L](x)))
    segments(min(x.seq), 0, max(x.seq), 0, col = col.inf, lty = 2)
    segments(z, 0, z, ymax * 10, col = col.inf, lty = 2)
    lines(x.seq, dnorm(x.seq), col = col.0, lty = 2)
  } else if (fun == "FL") {
    title(main = bquote(paste("Approximating ", F[delta[.(z)]], " with L Gaussian Derivatives")), ylab = expression(F[L](x)))
    segments(min(x.seq), 0, z, 0, col = col.inf, lty = 2)
    segments(z, 0, z, 1, col = col.inf, lty = 2)
    segments(z, 1, max(x.seq), 1, col = col.inf, lty = 2)
    lines(x.seq, pnorm(x.seq), col = col.0, lty = 2)
  }
  legend("topleft",
         lty = c(2, rep(1, length(L.seq)), 2),
         col = c(col.0, col, col.inf),
         legend = paste("L =", c(0, L.seq, Inf)),
         ncol = 2, cex = 0.75
         )
}
```

```{r, cache = TRUE, echo = FALSE}
x.seq = seq(-6, 6, 0.01)
L.seq = seq(0, 100, by = 20)[-1]
col.0 = "red"
col.inf = "black"
```

## $z = -2$

```{r, cache = TRUE, echo = FALSE}
z = -2
L.plot(z, fun = "fL", x.seq, L.seq)
L.plot(z, fun = "FL", x.seq, L.seq)
```

## $z = 0$

```{r, cache = TRUE, echo = FALSE}
z = 0
L.plot(z, fun = "fL", x.seq, L.seq)
L.plot(z, fun = "FL", x.seq, L.seq)
```

## $z = 4$

```{r, cache = TRUE, echo = FALSE}
z = 4
L.plot(z, fun = "fL", x.seq, L.seq)
L.plot(z, fun = "FL", x.seq, L.seq)
```

## $z = 6$

Numerical instability.

```{r, cache = TRUE, echo = FALSE}
z = 6
L.plot(z, fun = "fL", x.seq = seq(-2, 10, 0.01), L.seq)
L.plot(z, fun = "FL", x.seq = seq(-2, 10, 0.01), L.seq)
```


