---
title: "Comparison with `Knockoff`: Start from $\\Sigma_{\\hat\\beta}$"
author: "Lei Sun"
date: 2018-01-27
output: workflowr::wflow_html
---





## Introduction

Similar to [previous simulations](knockoff.html), only that the design matrix $X$ is [simulated](design_matrix.html#start_from_(sigma_{hatbeta})) such that $\Sigma_{\hat\beta} = \sigma_e^2(X^TX)^{-1}$ has non negligible off-diagnoal correlations.

```{r, echo = FALSE, message = FALSE}
source("~/GitHub/truncash/code/gdash_lik.R")
library(ashr)
library(qvalue)
library(knockoff)
library(reshape2)
library(ggplot2)
fdp <- function(selected) sum(beta[selected] == 0) / max(length(selected), 1)
tdn <- function(selected) sum(beta[selected] != 0)
mean_sdp <- function(x) {
   m <- mean(x)
   ymax <- m + sd(x)
   return(c(y = m, ymax = ymax, ymin = m))
}
method.name <- c("BH", "qvalue", "Knockoff", "ASH", "CASH", "CASH+")
method.col <- c("blue", "green", "orange", "burlywood4", "red", "maroon")
```

```{r, echo = FALSE, cache = TRUE, warning = FALSE}
n <- 2000
p <- 1000
k.vec <- 5 : 1 * 100
q <- 0.1
m <- 100
d.max <- 50
sigma.e <- 1
sigma.beta <- 3

fdp.list <- tdn.list <- time.list <- list()

fdp.mat <- tdn.mat <- matrix(0, nrow = m, ncol = 6)
colnames(fdp.mat) <- colnames(tdn.mat) <- c("BH", "qvalue", "Knockoff", "ASH", "CASH", "CASH+")

time.mat <- matrix(0, nrow = m, ncol = 6)
colnames(time.mat) <- c("BH", "qvalue", "Knockoff", "ASH", "CASH", "LS")

for (j in seq(length(k.vec))) {
k <- k.vec[j]
for (i in 1 : m) {
d <- sample(d.max, 1)
B <- matrix(rnorm(p * d, 0, 1), p, d)
Sigma.betahat <- tcrossprod(B) + diag(p)
Sigma.betahat <- Sigma.betahat / mean(diag(Sigma.betahat))
X <- svd(matrix(rnorm(n * p), n, p))$u %*% chol(solve(Sigma.betahat))
beta <- rep(0, p)
nonzero <- sample(p, k)
beta[nonzero] <- rnorm(k, 0, sigma.beta * sigma.e)
y <- X %*% beta + rnorm(n, 0, sigma.e)

## Knockoff
knockoff.time <- system.time(knockoff.fit <- knockoff::knockoff.filter(X, y, knockoffs = create.fixed, statistic = stat.glmnet_lambdasmax, fdr = q))[3]
knockoff.selected <- knockoff.fit$selected

## Least squares
ls.time <- system.time(lm.fit <- lm(y ~ X - 1))[3]
betahat <- coef(lm.fit)
sebetahat <- summary(lm.fit)$coefficients[, 2]
pvalue <- summary(lm.fit)$coefficients[, 4]

## Cash
cash.time <- system.time(cash.fit <- gdash(betahat, sebetahat))[3]
cash.selected <- (1 : p)[cash.fit$qvalue <= q]

## Cash selection with oracle knowledge
betahat.Sigma <- solve(crossprod(X)) * sigma.e^2
betahat.Cor <- cov2cor(betahat.Sigma)
rho.moment <- sapply(c(2, 4, 6, 8, 10), function(x) (sum(betahat.Cor^x) - p) / (p * (p - 1)))
w.pen = rep(0, 10)
w.pen[c(2, 4, 6, 8, 10)] = 1 / sqrt(rho.moment) * 20 / (1 / sqrt(rho.moment))[1]
sebetahat.perfect <- sqrt(diag(betahat.Sigma))
cash.oracle <- gdash(betahat, sebetahat.perfect, w.pen = w.pen)
cash.oracle.selected <- (1 : p)[cash.oracle$qvalue <= q]

## Ash
ash.time <- system.time(ash.fit <- ashr::ash(betahat, sebetahat, method = "fdr", mixcompdist = "normal"))[3]
ash.selected <- (1 : p)[get_qvalue(ash.fit) <= q]

## BH
BH.time <- system.time(BH.fit <- p.adjust(pvalue, method = "BH"))[3]
BH.selected <- (1 : p)[BH.fit <= q]

## qvalue
qvalue.time <- system.time(qvalue.fit <- qvalue::qvalue(pvalue))[3]
qvalue.selected <- (1 : p)[qvalue.fit$qvalues <= q]

fdp.mat[i, ] <- c(
  fdp(BH.selected),
  fdp(qvalue.selected),
  fdp(knockoff.selected),
  fdp(ash.selected),
  fdp(cash.selected),
  fdp(cash.oracle.selected)
)
tdn.mat[i, ] <- c(
  tdn(BH.selected),
  tdn(qvalue.selected),
  tdn(knockoff.selected),
  tdn(ash.selected),
  tdn(cash.selected),
  tdn(cash.oracle.selected)
)
time.mat[i, ] <- c(
  ls.time + BH.time,
  ls.time + qvalue.time,
  knockoff.time,
  ls.time + ash.time,
  ls.time + cash.time,
  ls.time
)
}
fdp.list[[j]] <- fdp.mat
tdn.list[[j]] <- tdn.mat
time.list[[j]] <- time.mat
}
```

## $d$ and $\Sigma_{\hat\beta}$

Let $\Sigma_{\hat\beta} / \sigma_e^2 = B_{p \times d} \cdot B_{p \times d}^T + I$, where $B_{i, j} \stackrel{\text{iid}}{\sim} N(0, 1)$. Then rescale the matrix such that the mean of its diagnal $= 1$. Generate $X_{n \times p}$ such that $(X^TX)^{-1} = \Sigma_{\hat\beta} / \sigma_e^2$.

Recall that the random coefficient of the second order of Gaussian deviative with the empirical distribution of correlated null $W_2$ has the property
$$
Var(W_2) = \bar{\rho_{ij}^2}
$$
We take a look at how $d$ is related to this quantity.

```{r, echo = FALSE, cache = TRUE}
w2.sd <- c()

for (d in 1 : 100) {
B <- matrix(rnorm(p * d, 0, 1), p, d)
Sigma.betahat <- B %*% t(B) + diag(p)
Sigma.betahat <- Sigma.betahat / mean(diag(Sigma.betahat))

Rho.betahat <- cov2cor(Sigma.betahat)
w2.sd[d] <- sqrt((sum(Rho.betahat^2) - p) / (p * (p - 1)))
}
```

```{r, echo = FALSE}
par(mar = c(4.5, 5, 2.5, 0.5))
plot(1 : 100, w2.sd, xlab = "d", ylab = expression(sigma(W[2]) == sqrt(bar(rho[ij]^2))), main = expression(paste("Square root of the average squared correlation among ", hat(beta)[i], " and ", hat(beta)[j])))
abline(v = c(20, 50), col = c(2, 4), lty = 2, lwd = 2)
```

## $\eta \in \{0.5, 0.6, 0.7, 0.8, 0.9\}$, $\sigma_\beta / \sigma_e = 3$, $d \sim Unif\{1, 2, \cdots, 50\}$

### Overall FDR and Power comparison

```{r avg, echo = FALSE, message = FALSE, warning = FALSE}
fdp.avg <- sapply(fdp.list, colMeans)
tdn.avg <- sapply(tdn.list, colMeans)

plot(1 - k.vec / p, k.vec, type = "n", ylim = range(fdp.avg, q, 0), ylab = "FDR", xlab = "Sparsity")
for (l in seq(nrow(fdp.avg))) {
  lines(1 - k.vec / p, fdp.avg[l, ], col = method.col[l], type = "o", pch = l)
}
legend("bottomright", lty = 1, pch = seq(nrow(fdp.avg)), col = method.col, legend = method.name, bty = "n")
abline(h = 0.1, lty = 2, lwd = 2)

plot(1 - k.vec / p, k.vec, type = "n", ylim = range(tdn.avg), ylab = "Number of True Discoveries", xlab = "Sparsity")
for (l in seq(nrow(tdn.avg))) {
  lines(1 - k.vec / p, tdn.avg[l, ], col = method.col[l], type = "o", pch = l)
}
legend("topright", lty = 1, pch = seq(nrow(fdp.avg)), col = method.col, legend = method.name)

plot(1 - k.vec / p, k.vec, type = "n", ylim = range(t(tdn.avg) / k.vec), ylab = "Power", xlab = "Sparsity")
for (l in seq(nrow(tdn.avg))) {
  lines(1 - k.vec / p, tdn.avg[l, ] / k.vec, col = method.col[l], type = "o", pch = l)
}
legend("topright", lty = 1, pch = seq(nrow(fdp.avg)), col = method.col, legend = method.name)
```

### FDR and Power at low sparsity: $50\%$ true signal

```{r 500, echo = FALSE, message = FALSE, warning = FALSE}
ggplot(data = melt(as.data.frame(fdp.list[[1]])),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  geom_hline(yintercept = q, col = "maroon", linetype = "dashed", size = 1) +
  labs(title = bquote(paste("False Discovery Proportions at ", FDR == .(q), " Cutoff")), x = "", y = "Actual False Discovery Proportion (FDP)") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

ggplot(data = melt(as.data.frame(tdn.list[[1]])),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Number of True Discoveries at ", FDR == .(q), " Cutoff")), x = "", y = "Number of True Discoveries") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

boxplot(log(time.list[[1]]), main = "Time Elapsed in Logarithm", ylab = "Log (Time in Seconds)", col = c(method.col[1 : 5], 1))
```

### FDR and Power at high sparsity: $10\%$ true signal

```{r 100, echo = FALSE, message = FALSE, warning = FALSE}
ggplot(data = melt(as.data.frame(fdp.list[[5]])),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  geom_hline(yintercept = q, col = "maroon", linetype = "dashed", size = 1) +
  labs(title = bquote(paste("False Discovery Proportions at ", FDR == .(q), " Cutoff")), x = "", y = "Actual False Discovery Proportion (FDP)") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

ggplot(data = melt(as.data.frame(tdn.list[[5]])),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Number of True Discoveries at ", FDR == .(q), " Cutoff")), x = "", y = "Number of True Discoveries") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

boxplot(log(time.list[[5]]), main = "Time Elapsed in Logarithm", ylab = "Log (Time in Seconds)", col = c(method.col[1 : 5], 1))
```

## $\eta \in \{0.75, 0.80, 0.85, 0.90, 0.95\}$, $\sigma_\beta / \sigma_e = 3$, $d \sim Unif\{1, 2, \cdots, 20\}$

```{r sparse_cor, echo = FALSE, cache = TRUE, warning = FALSE}
n <- 2000
p <- 1000
k.vec <- 5 : 1 * 50
q <- 0.1
m <- 100
d.max <- 20
sigma.e <- 1
sigma.beta <- 3

fdp.list <- tdn.list <- time.list <- list()

fdp.mat <- tdn.mat <- matrix(0, nrow = m, ncol = 6)
colnames(fdp.mat) <- colnames(tdn.mat) <- c("BH", "qvalue", "Knockoff", "ASH", "CASH", "CASH+")

time.mat <- matrix(0, nrow = m, ncol = 6)
colnames(time.mat) <- c("BH", "qvalue", "Knockoff", "ASH", "CASH", "LS")

for (j in seq(length(k.vec))) {
k <- k.vec[j]
for (i in 1 : m) {
d <- sample(d.max, 1)
B <- matrix(rnorm(p * d, 0, 1), p, d)
Sigma.betahat <- tcrossprod(B) + diag(p)
Sigma.betahat <- Sigma.betahat / mean(diag(Sigma.betahat))
X <- svd(matrix(rnorm(n * p), n, p))$u %*% chol(solve(Sigma.betahat))
beta <- rep(0, p)
nonzero <- sample(p, k)
beta[nonzero] <- rnorm(k, 0, sigma.beta * sigma.e)
y <- X %*% beta + rnorm(n, 0, sigma.e)

## Knockoff
knockoff.time <- system.time(knockoff.fit <- knockoff::knockoff.filter(X, y, knockoffs = create.fixed, statistic = stat.glmnet_lambdasmax, fdr = q))[3]
knockoff.selected <- knockoff.fit$selected

## Least squares
ls.time <- system.time(lm.fit <- lm(y ~ X - 1))[3]
betahat <- coef(lm.fit)
sebetahat <- summary(lm.fit)$coefficients[, 2]
pvalue <- summary(lm.fit)$coefficients[, 4]

## Cash
cash.time <- system.time(cash.fit <- gdash(betahat, sebetahat))[3]
cash.selected <- (1 : p)[cash.fit$qvalue <= q]

## Cash selection with oracle knowledge
betahat.Sigma <- solve(crossprod(X)) * sigma.e^2
betahat.Cor <- cov2cor(betahat.Sigma)
rho.moment <- sapply(c(2, 4, 6, 8, 10), function(x) (sum(betahat.Cor^x) - p) / (p * (p - 1)))
w.pen = rep(0, 10)
w.pen[c(2, 4, 6, 8, 10)] = 1 / sqrt(rho.moment) * 20 / (1 / sqrt(rho.moment))[1]
sebetahat.perfect <- sqrt(diag(betahat.Sigma))
cash.oracle <- gdash(betahat, sebetahat.perfect, w.pen = w.pen)
cash.oracle.selected <- (1 : p)[cash.oracle$qvalue <= q]

## Ash
ash.time <- system.time(ash.fit <- ashr::ash(betahat, sebetahat, method = "fdr", mixcompdist = "normal"))[3]
ash.selected <- (1 : p)[get_qvalue(ash.fit) <= q]

## BH
BH.time <- system.time(BH.fit <- p.adjust(pvalue, method = "BH"))[3]
BH.selected <- (1 : p)[BH.fit <= q]

## qvalue
qvalue.time <- system.time(qvalue.fit <- qvalue::qvalue(pvalue))[3]
qvalue.selected <- (1 : p)[qvalue.fit$qvalues <= q]

fdp.mat[i, ] <- c(
  fdp(BH.selected),
  fdp(qvalue.selected),
  fdp(knockoff.selected),
  fdp(ash.selected),
  fdp(cash.selected),
  fdp(cash.oracle.selected)
)
tdn.mat[i, ] <- c(
  tdn(BH.selected),
  tdn(qvalue.selected),
  tdn(knockoff.selected),
  tdn(ash.selected),
  tdn(cash.selected),
  tdn(cash.oracle.selected)
)
time.mat[i, ] <- c(
  ls.time + BH.time,
  ls.time + qvalue.time,
  knockoff.time,
  ls.time + ash.time,
  ls.time + cash.time,
  ls.time
)
}
fdp.list[[j]] <- fdp.mat
tdn.list[[j]] <- tdn.mat
time.list[[j]] <- time.mat
}
```

### Overall FDR and Power comparison

```{r sparse_cor avg, echo = FALSE, message = FALSE, warning = FALSE}
fdp.avg <- sapply(fdp.list, colMeans)
tdn.avg <- sapply(tdn.list, colMeans)

plot(1 - k.vec / p, k.vec, type = "n", ylim = range(fdp.avg, q, 0), ylab = "FDR", xlab = "Sparsity")
for (l in seq(nrow(fdp.avg))) {
  lines(1 - k.vec / p, fdp.avg[l, ], col = method.col[l], type = "o", pch = l)
}
legend("bottomright", lty = 1, pch = seq(nrow(fdp.avg)), col = method.col, legend = method.name, bty = "n")
abline(h = 0.1, lty = 2, lwd = 2)

plot(1 - k.vec / p, k.vec, type = "n", ylim = range(tdn.avg), ylab = "Number of True Discoveries", xlab = "Sparsity")
for (l in seq(nrow(tdn.avg))) {
  lines(1 - k.vec / p, tdn.avg[l, ], col = method.col[l], type = "o", pch = l)
}
legend("topright", lty = 1, pch = seq(nrow(fdp.avg)), col = method.col, legend = method.name)

plot(1 - k.vec / p, k.vec, type = "n", ylim = range(t(tdn.avg) / k.vec), ylab = "Power", xlab = "Sparsity")
for (l in seq(nrow(tdn.avg))) {
  lines(1 - k.vec / p, tdn.avg[l, ] / k.vec, col = method.col[l], type = "o", pch = l)
}
legend("topright", lty = 1, pch = seq(nrow(fdp.avg)), col = method.col, legend = method.name)
```

### FDR and Power at low sparsity: $20\%$ true signal

```{r sparse_cor 250, echo = FALSE, message = FALSE, warning = FALSE}
ggplot(data = melt(as.data.frame(fdp.list[[2]])),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  geom_hline(yintercept = q, col = "maroon", linetype = "dashed", size = 1) +
  labs(title = bquote(paste("False Discovery Proportions at ", FDR == .(q), " Cutoff")), x = "", y = "False Discovery Proportion (FDP)") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

ggplot(data = melt(as.data.frame(tdn.list[[2]] / k.vec[2])),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Number of True Discoveries at ", FDR == .(q), " Cutoff")), x = "", y = "Power") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

boxplot(log(time.list[[2]]), main = "Time Elapsed in Logarithm", ylab = "Log (Time in Seconds)", col = c(method.col[1 : 5], 1))
```

### FDR and Power at high sparsity: $10\%$ true signal

```{r sparse_cor 100, echo = FALSE, message = FALSE, warning = FALSE}
ggplot(data = melt(as.data.frame(fdp.list[[4]])),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  geom_hline(yintercept = q, col = "maroon", linetype = "dashed", size = 1) +
  labs(title = bquote(paste("False Discovery Proportions at ", FDR == .(q), " Cutoff")), x = "", y = "False Discovery Proportion (FDP)") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

ggplot(data = melt(as.data.frame(tdn.list[[4]] / k.vec[4])),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Number of True Discoveries at ", FDR == .(q), " Cutoff")), x = "", y = "Power") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

boxplot(log(time.list[[4]]), main = "Time Elapsed in Logarithm", ylab = "Log (Time in Seconds)", col = c(method.col[1 : 5], 1))
```


