---
title: "Comparison with `Knockoff`: Collinearity in $X$"
author: "Lei Sun"
date: 2018-01-25
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

## Introduction

Similar to [previous simulation](knockoff.html), only that the design matrix $X$ is [simulated](design_matrix.html#(sigma):_high_collinearity) such that the columns in $X$ have high collinearity.

Each row of $X$ is independently drawn from a $N(0, \Sigma_X)$ distribution, where $\Sigma_X = B_{p \times d} \cdot B_{p \times d}^T + I$, where $B_{i, j} \stackrel{\text{iid}}{\sim} N(0, 1)$. Then transform $\Sigma_X$ to a correlation matrix.

## $d = 5$, the sparsity $\eta \in \{0.5, 0.6, 0.7, 0.8, 0.9\}$

```{r, echo = FALSE, message = FALSE}
set.seed(777)

library(knockoff)
source("../code/gdash_lik.R")
library(ashr)

fdp = function(selected) sum(beta[selected] == 0) / max(1, length(selected))
tdn = function(selected) sum(beta[selected] != 0)

library(reshape2)
library(ggplot2)
mean_sdp <- function(x) {
   m <- mean(x)
   ymax <- m + sd(x)
   return(c(y = m, ymax = ymax, ymin = m))
}
method.name <- c("BH", "qvalue", "Knockoff", "ASH", "Cash", "Cash+")
method.col <- c("blue", "green", "orange", "burlywood4", "red", "maroon")
```

```{r, echo = FALSE, cache = TRUE}
m <- 100

fdp.mat <- matrix(0, ncol = 6, nrow = m)
tdn.mat <- matrix(0, ncol = 6, nrow = m)
time.mat <- matrix(0, ncol = 3, nrow = m)

fdp.list <- list()
tdn.list <- list()
time.list <- list()

colnames(fdp.mat) <- c("BH", "qvalue", "Knockoff", "ASH", "Cash", "Cash+")
colnames(tdn.mat) <- c("BH", "qvalue", "Knockoff", "ASH", "Cash", "Cash+")
colnames(time.mat) <- c("BH", "Knockoff", "Cash")

# Problem parameters
n = 2000          # number of observations
p = 1000           # number of variables
k.vec = 5 : 1 * 100            # number of variables with nonzero coefficients
amplitude = 3.5   # signal amplitude (for noise level = 1)
q = 0.1          # nominal fdr to control for
d = 5            # level of collinearity in X

for (j in seq(length(k.vec))) {
for (i in 1 : m) {
# Generate the variables from a multivariate normal distribution
B = matrix(rnorm(p * d, 0, 1), ncol = d, nrow = p)
V = B %*% t(B) + diag(p)
Sigma <- cov2cor(V)
X = matrix(rnorm(n * p), n) %*% chol(Sigma)

# Generate the response from a linear model
k = k.vec[j]
nonzero = sample(p, k)
beta = rep(0, p)
beta[nonzero] = rnorm(k, 0, amplitude) / sqrt(n)
y.sample = function(X) X %*% beta + rnorm(n)
y = y.sample(X)

# Knockoff selection
knockoff.time <- system.time(knockoff.result <- knockoff::knockoff.filter(X, y, knockoffs = create.fixed, statistic = stat.glmnet_lambdasmax, fdr = q))[3]
knockoff.selected <- knockoff.result$selected

# CASH selection
cash.time <- proc.time()
lm.fit <- lm(y ~ X - 1)
betahat <- coef(lm.fit)
sebetahat <- summary(lm.fit)$coefficients[, 2]
cash <- gdash(betahat, sebetahat)
cash.time <- (proc.time() - cash.time)[3]
cash.selected <- (1 : p)[cash$qvalue <= q]

# CASH selection with better penalization
betahat.sigma <- cov2cor(solve(crossprod(X)))
rho.m <- sapply(c(2, 4, 6, 8, 10), function(x) (sum(betahat.sigma^x) - p) / (p * (p - 1)))
w.pen = rep(0, 10)
w.pen[c(2, 4, 6, 8, 10)] = 1 / sqrt(rho.m) * 20 / (1 / sqrt(rho.m))[1]
cash.penalization <- gdash(betahat, sebetahat, w.pen = w.pen)
cash.penalization.selected <- (1 : p)[cash.penalization$qvalue <= q]

# CASH selection with perfect knowledge
sebetahat.perfect <- sqrt(diag(solve(crossprod(X))))
cash.perfect <- gdash(betahat, sebetahat.perfect, w.pen = w.pen)
cash.perfect.selected <- (1 : p)[cash.perfect$qvalue <= q]

# ASH selection
ash <- ashr::ash(betahat, sebetahat, method = "fdr", mixcompdist = "normal")
ash.selected <- (1 : p)[get_qvalue(ash) <= q]

# BH selection
pvalue <- summary(lm.fit)$coefficients[, 4]
BH.time <- system.time(BH <- p.adjust(pvalue, method = "BH"))[3]
BH.selected <- (1 : p)[BH <= q]

# qvalue selection
qvalue <- qvalue::qvalue(pvalue)
qvalue.selected <- (1 : p)[qvalue$qvalues <= q]

fdp.mat[i, ] <- c(
  fdp(BH.selected),
  fdp(qvalue.selected),
  fdp(knockoff.selected),
  fdp(ash.selected),
  fdp(cash.selected),
  fdp(cash.perfect.selected)
)
tdn.mat[i, ] <- c(
  tdn(BH.selected),
  tdn(qvalue.selected),
  tdn(knockoff.selected),
  tdn(ash.selected),
  tdn(cash.selected),
  tdn(cash.perfect.selected)
)
time.mat[i, ] <- c(
  BH.time,
  knockoff.time,
  cash.time
)
}
fdp.list[[j]] <- fdp.mat
tdn.list[[j]] <- tdn.mat
time.list[[j]] <- time.mat
}
```

### Overall across all sparsity

```{r avg, echo = 500}
fdp.avg <- sapply(fdp.list, colMeans)
tdn.avg <- sapply(tdn.list, colMeans)

plot(1 - k.vec / p, k.vec, type = "n", ylim = range(fdp.avg, q, 0), ylab = "FDR", xlab = "Sparsity")
for (l in seq(nrow(fdp.avg))) {
  lines(1 - k.vec / p, fdp.avg[l, ], col = method.col[l], type = "o", pch = l)
}
legend("bottomright", lty = 1, pch = seq(nrow(fdp.avg)), col = method.col, legend = method.name, bty = "n")
abline(h = 0.1, lty = 2, lwd = 2)

plot(1 - k.vec / p, k.vec, type = "n", ylim = range(tdn.avg), ylab = "Power", xlab = "Sparsity")
for (l in seq(ncol(tdn.avg))) {
  lines(1 - k.vec / p, tdn.avg[l, ], col = method.col[l], type = "o", pch = l)
}
legend("topright", lty = 1, pch = seq(nrow(fdp.avg)), col = method.col, legend = method.name)
```

### Low sparsity: $50\%$ true signal

```{r 500, echo = FALSE}
ggplot(data = melt(as.data.frame(fdp.list[[1]])),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  geom_hline(yintercept = q, col = "maroon", linetype = "dashed", size = 1) +
  labs(title = bquote(paste("False Discovery Proportions at ", FDR == .(q), " Cutoff")), x = "", y = "Actual False Discovery Proportion (FDP)") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

ggplot(data = melt(as.data.frame(tdn.list[[1]])),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Number of True Discoveries at ", FDR == .(q), " Cutoff")), x = "", y = "Number of True Discoveries") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

boxplot(log(time.list[[1]]), main = "Time Elapsed in Logarithm", ylab = "Log (Time in Seconds)", col = method.col[c(1, 3, 5)])
```

### High sparsity: $10\%$ true signal

```{r 100, echo = FALSE}
ggplot(data = melt(as.data.frame(fdp.list[[5]])),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  geom_hline(yintercept = q, col = "maroon", linetype = "dashed", size = 1) +
  labs(title = bquote(paste("False Discovery Proportions at ", FDR == .(q), " Cutoff")), x = "", y = "Actual False Discovery Proportion (FDP)") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

ggplot(data = melt(as.data.frame(tdn.list[[5]])),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Number of True Discoveries at ", FDR == .(q), " Cutoff")), x = "", y = "Number of True Discoveries") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

boxplot(log(time.list[[5]]), main = "Time Elapsed in Logarithm", ylab = "Log (Time in Seconds)", col = method.col[c(1, 3, 5)])
```

## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
