---
title: "Comparison with `Knockoff`: $\\Sigma_X$ is Toeplitz"
author: "Lei Sun"
date: 2017-01-18
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

## Introduction

Applying CASH to linear regression variable selection, compared with other popular methods including BH, Knockoff.

## Simulation Setting

The simulation setting is very similar to what's used in Knockoff's [vignette](https://cran.r-project.org/web/packages/knockoff/vignettes/fixed.html). The only notable difference is that the non-zero signals are normally distributed centered at zero, rather than constant.

Data are simulated by

$$
y_n = X_{n \times p}\beta_p + e_n
$$
where
$$
\begin{array}{c}
n = 2000 \\
p = 1000 \\
e_n \sim N(0, 1) \\
\beta \sim \eta\delta_0 + (1 - \eta)N(0, \sigma /\sqrt{n})
\end{array}
$$
Each row of $X$ is generated independently from a $N(0, \Sigma_\rho)$ distribution, where $\left(\Sigma_\rho\right)_{j, k} = \rho^{|j - k|}$, a Toplitz matrix.

Every method selects the variables with respect to a nominal false discovery rate $q = 0.1$.

In simulations, we are changing the values of the sparsity level $\eta$, the signal strength $\sigma$, the feature correlation $\rho$.

## Methods

- BH: First run multiple linear regression, then apply BH to obtained $p$-values.

- qvalue: First run multiple linear regression, then apply `qvalue::qvalue` to obtained $p$-values.

- Knockoff: Directly apply `knockoff::knockoff` on $X$, $y$.

- ASH: First run multiple linear regression, then apply `ashr::ash` on obtained $\hat\beta$ and $\hat{\text{se}}\left(\hat \beta\right)$, using normal mixture and normal likelihood.

- CASH: First run multiple linear regression, then apply `cash` on obtained $\hat\beta$ and $\hat{\text{se}}\left(\hat \beta\right)$, using normal mixture and normal likelihood, with default penalty on Gaussian derivative coefficients.

- CASH+: CASH with perfect knowledge, using real noise level $\text{se}\left(\hat{\beta}\right)$.

## Observations

- BH is very robust, very fast.

- Knockoff is way too slow and way too conservative with signals being unimodal at zero. Perhaps it needs strong signals distinctly different from the "bulk." Unimodal setting is really adversary to this method.

- `CASH` works fine, but not better than the basic `ASH`.

## $\eta = 0.9$, $\sigma = 5$, $\rho = 0.5$

```{r, echo = FALSE, cache = TRUE}
set.seed(777)

library(knockoff)
source("../code/gdash_lik.R")

fdp = function(selected) sum(beta[selected] == 0) / max(1, length(selected))
tdn = function(selected) sum(beta[selected] != 0)

m <- 100

fdp.mat <- matrix(0, ncol = 3, nrow = m)
tdn.mat <- matrix(0, ncol = 3, nrow = m)
time.mat <- matrix(0, ncol = 3, nrow = m)

colnames(fdp.mat) <- c("Knockoff", "Cash", "BH")
colnames(tdn.mat) <- c("Knockoff", "Cash", "BH")
colnames(time.mat) <- c("Knockoff", "Cash", "BH")

# Problem parameters
n = 2000          # number of observations
p = 1000           # number of variables
k = 100            # number of variables with nonzero coefficients
amplitude = 5   # signal amplitude (for noise level = 1)
q = 0.1          # nominal fdr to control for

# Generate the variables from a multivariate normal distribution
rho = 0.5
Sigma = toeplitz(rho^(0 : (p - 1)))

for (i in 1 : m) {
X = matrix(rnorm(n * p), n) %*% chol(Sigma)

# Generate the response from a linear model
nonzero = sample(p, k)
beta = rep(0, p)
beta[nonzero] = rnorm(k, 0, amplitude) / sqrt(n)
y.sample = function(X) X %*% beta + rnorm(n)
y = y.sample(X)

# Knockoff selection
knockoff.time <- system.time(knockoff.result <- knockoff::knockoff.filter(X, y, knockoffs = create.fixed, statistic = stat.glmnet_lambdasmax, fdr = q))[3]
knockoff.selected <- knockoff.result$selected

# CASH selection
cash.time <- proc.time()
lm.fit <- lm(y ~ X - 1)
betahat <- coef(lm.fit)
sebetahat <- summary(lm.fit)$coefficients[, 2]
cash <- gdash(betahat, sebetahat)
cash.time <- (proc.time() - cash.time)[3]
cash.selected <- (1 : p)[cash$qvalue <= q]

# # CASH selection with perfect knowledge
# sebetahat.perfect <- sqrt(diag(solve(crossprod(X))))
# betahat.sigma <- cov2cor(solve(crossprod(X)))
# rho.m <- sapply(c(2, 4, 6, 8, 10), function(x) (sum(betahat.sigma^x) - p) / (p * (p - 1)))
# w.pen = rep(0, 10)
# w.pen[c(2, 4, 6, 8, 10)] = 1 / sqrt(rho.m) * 20 / (1 / sqrt(rho.m))[1]
# cash.perfect <- gdash(betahat, sebetahat, w.pen = w.pen, sebetahat.perfect)
# cash.perfect.selected <- (1 : p)[cash.perfect$qvalue <= q]

# BH selection
pvalue <- summary(lm.fit)$coefficients[, 4]
BH.time <- system.time(BH <- p.adjust(pvalue, method = "BH"))[3]
BH.selected <- (1 : p)[BH <= q]

fdp.mat[i, ] <- c(
  fdp(knockoff.selected),
  fdp(cash.selected),
  fdp(BH.selected)
)
tdn.mat[i, ] <- c(
  tdn(knockoff.selected),
  tdn(cash.selected),
  tdn(BH.selected)
)
time.mat[i, ] <- c(
  knockoff.time,
  cash.time,
  BH.time
)
}
```

```{r, echo = FALSE}
library(reshape2)
library(ggplot2)
mean_sdp <- function(x) {
   m <- mean(x)
   ymax <- m + sd(x)
   return(c(y = m, ymax = ymax, ymin = m))
}
method.name <- c("Knockoff", "Cash", "BH")
method.col <- c("blue", "red", "green")

ggplot(data = melt(as.data.frame(fdp.mat)),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  geom_hline(yintercept = q, col = "maroon", linetype = "dashed", size = 1) +
  labs(title = bquote(paste("False Discovery Proportions at ", FDR == .(q), " Cutoff")), x = "", y = "Actual False Discovery Proportion (FDP)") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

ggplot(data = melt(as.data.frame(tdn.mat)),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Number of True Discoveries at ", FDR == .(q), " Cutoff")), x = "", y = "Number of True Discoveries") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

boxplot(log(time.mat), main = "Time Elapsed in Logarithm", ylab = "Log (Time in Seconds)")
```


## $\eta = 0.8$, $\sigma = 4$, $\rho = 0.5$


```{r, echo = FALSE, cache = TRUE}
set.seed(777)

library(knockoff)
source("../code/gdash_lik.R")

fdp = function(selected) sum(beta[selected] == 0) / max(1, length(selected))
tdn = function(selected) sum(beta[selected] != 0)

m <- 100

fdp.mat <- matrix(0, ncol = 5, nrow = m)
tdn.mat <- matrix(0, ncol = 5, nrow = m)
time.mat <- matrix(0, ncol = 3, nrow = m)

colnames(fdp.mat) <- c("Knockoff", "BH", "Cash", "Cash+", "Cash++")
colnames(tdn.mat) <- c("Knockoff", "BH", "Cash", "Cash+", "Cash++")
colnames(time.mat) <- c("Knockoff", "BH", "Cash")

# Problem parameters
n = 2000          # number of observations
p = 1000           # number of variables
k = 200            # number of variables with nonzero coefficients
amplitude = 4   # signal amplitude (for noise level = 1)
q = 0.1          # nominal fdr to control for

# Generate the variables from a multivariate normal distribution
rho = 0.5
Sigma = toeplitz(rho^(0 : (p - 1)))

for (i in 1 : m) {
X = matrix(rnorm(n * p), n) %*% chol(Sigma)

# Generate the response from a linear model
nonzero = sample(p, k)
beta = rep(0, p)
beta[nonzero] = rnorm(k, 0, amplitude) / sqrt(n)
y.sample = function(X) X %*% beta + rnorm(n)
y = y.sample(X)

# Knockoff selection
knockoff.time <- system.time(knockoff.result <- knockoff::knockoff.filter(X, y, knockoffs = create.fixed, statistic = stat.glmnet_lambdasmax, fdr = q))[3]
knockoff.selected <- knockoff.result$selected

# CASH selection
cash.time <- proc.time()
lm.fit <- lm(y ~ X - 1)
betahat <- coef(lm.fit)
sebetahat <- summary(lm.fit)$coefficients[, 2]
cash <- gdash(betahat, sebetahat)
cash.time <- (proc.time() - cash.time)[3]
cash.selected <- (1 : p)[cash$qvalue <= q]

# CASH selection with better penalization
betahat.sigma <- cov2cor(solve(crossprod(X)))
rho.m <- sapply(c(2, 4, 6, 8, 10), function(x) (sum(betahat.sigma^x) - p) / (p * (p - 1)))
w.pen = rep(0, 10)
w.pen[c(2, 4, 6, 8, 10)] = 1 / sqrt(rho.m) * 20 / (1 / sqrt(rho.m))[1]
cash.penalization <- gdash(betahat, sebetahat, w.pen = w.pen)
cash.penalization.selected <- (1 : p)[cash.penalization$qvalue <= q]

# CASH selection with perfect knowledge
sebetahat.perfect <- sqrt(diag(solve(crossprod(X))))
cash.perfect <- gdash(betahat, sebetahat.perfect, w.pen = w.pen)
cash.perfect.selected <- (1 : p)[cash.perfect$qvalue <= q]

# BH selection
pvalue <- summary(lm.fit)$coefficients[, 4]
BH.time <- system.time(BH <- p.adjust(pvalue, method = "BH"))[3]
BH.selected <- (1 : p)[BH <= q]

fdp.mat[i, ] <- c(
  fdp(knockoff.selected),
  fdp(BH.selected),
  fdp(cash.selected),
  fdp(cash.penalization.selected),
  fdp(cash.perfect.selected)
)
tdn.mat[i, ] <- c(
  tdn(knockoff.selected),
  tdn(BH.selected),
  tdn(cash.selected),
  tdn(cash.penalization.selected),
  tdn(cash.perfect.selected)
)
time.mat[i, ] <- c(
  knockoff.time,
  BH.time,
  cash.time
)
}
```

```{r, echo = FALSE}
library(reshape2)
library(ggplot2)
mean_sdp <- function(x) {
   m <- mean(x)
   ymax <- m + sd(x)
   return(c(y = m, ymax = ymax, ymin = m))
}
method.name <- c("Knockoff", "BH", "Cash", "Cash+", "Cash++")
method.col <- c("blue", "green", "orange", "red", "maroon")

ggplot(data = melt(as.data.frame(fdp.mat)),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  geom_hline(yintercept = q, col = "maroon", linetype = "dashed", size = 1) +
  labs(title = bquote(paste("False Discovery Proportions at ", FDR == .(q), " Cutoff")), x = "", y = "Actual False Discovery Proportion (FDP)") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

ggplot(data = melt(as.data.frame(tdn.mat)),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Number of True Discoveries at ", FDR == .(q), " Cutoff")), x = "", y = "Number of True Discoveries") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

boxplot(log(time.mat), main = "Time Elapsed in Logarithm", ylab = "Log (Time in Seconds)")
```


## $\eta = 0.5$, $\sigma = 4$, $\rho = 0.5$

```{r, echo = FALSE, cache = TRUE}
set.seed(777)

library(knockoff)
source("../code/gdash_lik.R")

fdp = function(selected) sum(beta[selected] == 0) / max(1, length(selected))
tdn = function(selected) sum(beta[selected] != 0)

m <- 100

fdp.mat <- matrix(0, ncol = 5, nrow = m)
tdn.mat <- matrix(0, ncol = 5, nrow = m)
time.mat <- matrix(0, ncol = 3, nrow = m)

colnames(fdp.mat) <- c("Knockoff", "BH", "Cash", "Cash+", "Cash++")
colnames(tdn.mat) <- c("Knockoff", "BH", "Cash", "Cash+", "Cash++")
colnames(time.mat) <- c("Knockoff", "BH", "Cash")

# Problem parameters
n = 2000          # number of observations
p = 1000           # number of variables
k = 500            # number of variables with nonzero coefficients
amplitude = 4   # signal amplitude (for noise level = 1)
q = 0.1          # nominal fdr to control for

# Generate the variables from a multivariate normal distribution
rho = 0.5
Sigma = toeplitz(rho^(0 : (p - 1)))

for (i in 1 : m) {
X = matrix(rnorm(n * p), n) %*% chol(Sigma)

# Generate the response from a linear model
nonzero = sample(p, k)
beta = rep(0, p)
beta[nonzero] = rnorm(k, 0, amplitude) / sqrt(n)
y.sample = function(X) X %*% beta + rnorm(n)
y = y.sample(X)

# Knockoff selection
knockoff.time <- system.time(knockoff.result <- knockoff::knockoff.filter(X, y, knockoffs = create.fixed, statistic = stat.glmnet_lambdasmax, fdr = q))[3]
knockoff.selected <- knockoff.result$selected

# CASH selection
cash.time <- proc.time()
lm.fit <- lm(y ~ X - 1)
betahat <- coef(lm.fit)
sebetahat <- summary(lm.fit)$coefficients[, 2]
cash <- gdash(betahat, sebetahat)
cash.time <- (proc.time() - cash.time)[3]
cash.selected <- (1 : p)[cash$qvalue <= q]

# CASH selection with better penalization
betahat.sigma <- cov2cor(solve(crossprod(X)))
rho.m <- sapply(c(2, 4, 6, 8, 10), function(x) (sum(betahat.sigma^x) - p) / (p * (p - 1)))
w.pen = rep(0, 10)
w.pen[c(2, 4, 6, 8, 10)] = 1 / sqrt(rho.m) * 20 / (1 / sqrt(rho.m))[1]
cash.penalization <- gdash(betahat, sebetahat, w.pen = w.pen)
cash.penalization.selected <- (1 : p)[cash.penalization$qvalue <= q]

# CASH selection with perfect knowledge
sebetahat.perfect <- sqrt(diag(solve(crossprod(X))))
cash.perfect <- gdash(betahat, sebetahat.perfect, w.pen = w.pen)
cash.perfect.selected <- (1 : p)[cash.perfect$qvalue <= q]

# BH selection
pvalue <- summary(lm.fit)$coefficients[, 4]
BH.time <- system.time(BH <- p.adjust(pvalue, method = "BH"))[3]
BH.selected <- (1 : p)[BH <= q]

fdp.mat[i, ] <- c(
  fdp(knockoff.selected),
  fdp(BH.selected),
  fdp(cash.selected),
  fdp(cash.penalization.selected),
  fdp(cash.perfect.selected)
)
tdn.mat[i, ] <- c(
  tdn(knockoff.selected),
  tdn(BH.selected),
  tdn(cash.selected),
  tdn(cash.penalization.selected),
  tdn(cash.perfect.selected)
)
time.mat[i, ] <- c(
  knockoff.time,
  BH.time,
  cash.time
)
}
```

```{r, echo = FALSE}
library(reshape2)
library(ggplot2)
mean_sdp <- function(x) {
   m <- mean(x)
   ymax <- m + sd(x)
   return(c(y = m, ymax = ymax, ymin = m))
}
method.name <- c("Knockoff", "BH", "Cash", "Cash+", "Cash++")
method.col <- c("blue", "green", "orange", "red", "maroon")

ggplot(data = melt(as.data.frame(fdp.mat)),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  geom_hline(yintercept = q, col = "maroon", linetype = "dashed", size = 1) +
  labs(title = bquote(paste("False Discovery Proportions at ", FDR == .(q), " Cutoff")), x = "", y = "Actual False Discovery Proportion (FDP)") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

ggplot(data = melt(as.data.frame(tdn.mat)),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Number of True Discoveries at ", FDR == .(q), " Cutoff")), x = "", y = "Number of True Discoveries") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

boxplot(log(time.mat), main = "Time Elapsed in Logarithm", ylab = "Log (Time in Seconds)")
```


## $\eta \in \left\{0.5, 0.6, 0.7, 0.8, 0.9\right\}$, $\sigma = 4$, $\rho = 0.5$

```{r sparsity, echo = FALSE, cache = TRUE}
set.seed(777)

library(knockoff)
source("../code/gdash_lik.R")
library(ashr)

fdp = function(selected) sum(beta[selected] == 0) / max(1, length(selected))
tdn = function(selected) sum(beta[selected] != 0)

m <- 100

fdp.mat <- matrix(0, ncol = 6, nrow = m)
tdn.mat <- matrix(0, ncol = 6, nrow = m)
time.mat <- matrix(0, ncol = 3, nrow = m)

fdp.list <- list()
tdn.list <- list()
time.list <- list()

colnames(fdp.mat) <- c("BH", "qvalue", "Knockoff", "ASH", "Cash", "Cash+")
colnames(tdn.mat) <- c("BH", "qvalue", "Knockoff", "ASH", "Cash", "Cash+")
colnames(time.mat) <- c("BH", "Knockoff", "Cash")

# Problem parameters
n = 2000          # number of observations
p = 1000           # number of variables
k.vec = 5 : 1 * 100            # number of variables with nonzero coefficients
amplitude = 4   # signal amplitude (for noise level = 1)
q = 0.1          # nominal fdr to control for

# Generate the variables from a multivariate normal distribution
rho = 0.5
Sigma = toeplitz(rho^(0 : (p - 1)))

for (j in seq(length(k.vec))) {
for (i in 1 : m) {
X = matrix(rnorm(n * p), n) %*% chol(Sigma)

# Generate the response from a linear model
k = k.vec[j]
nonzero = sample(p, k)
beta = rep(0, p)
beta[nonzero] = rnorm(k, 0, amplitude) / sqrt(n)
y.sample = function(X) X %*% beta + rnorm(n)
y = y.sample(X)

# Knockoff selection
knockoff.time <- system.time(knockoff.result <- knockoff::knockoff.filter(X, y, knockoffs = create.fixed, statistic = stat.glmnet_lambdasmax, fdr = q))[3]
knockoff.selected <- knockoff.result$selected

# CASH selection
cash.time <- proc.time()
lm.fit <- lm(y ~ X - 1)
betahat <- coef(lm.fit)
sebetahat <- summary(lm.fit)$coefficients[, 2]
cash <- gdash(betahat, sebetahat)
cash.time <- (proc.time() - cash.time)[3]
cash.selected <- (1 : p)[cash$qvalue <= q]

# CASH selection with better penalization
betahat.sigma <- cov2cor(solve(crossprod(X)))
rho.m <- sapply(c(2, 4, 6, 8, 10), function(x) (sum(betahat.sigma^x) - p) / (p * (p - 1)))
w.pen = rep(0, 10)
w.pen[c(2, 4, 6, 8, 10)] = 1 / sqrt(rho.m) * 20 / (1 / sqrt(rho.m))[1]
cash.penalization <- gdash(betahat, sebetahat, w.pen = w.pen)
cash.penalization.selected <- (1 : p)[cash.penalization$qvalue <= q]

# CASH selection with perfect knowledge
sebetahat.perfect <- sqrt(diag(solve(crossprod(X))))
cash.perfect <- gdash(betahat, sebetahat.perfect, w.pen = w.pen)
cash.perfect.selected <- (1 : p)[cash.perfect$qvalue <= q]

# ASH selection
ash <- ashr::ash(betahat, sebetahat, method = "fdr", mixcompdist = "normal")
ash.selected <- (1 : p)[get_qvalue(ash) <= q]


# BH selection
pvalue <- summary(lm.fit)$coefficients[, 4]
BH.time <- system.time(BH <- p.adjust(pvalue, method = "BH"))[3]
BH.selected <- (1 : p)[BH <= q]

# qvalue selection
qvalue <- qvalue::qvalue(pvalue)
qvalue.selected <- (1 : p)[qvalue$qvalues <= q]

fdp.mat[i, ] <- c(
  fdp(BH.selected),
  fdp(qvalue.selected),
  fdp(knockoff.selected),
  fdp(ash.selected),
  fdp(cash.selected),
  fdp(cash.perfect.selected)
)
tdn.mat[i, ] <- c(
  tdn(BH.selected),
  tdn(qvalue.selected),
  tdn(knockoff.selected),
  tdn(ash.selected),
  tdn(cash.selected),
  tdn(cash.perfect.selected)
)
time.mat[i, ] <- c(
  BH.time,
  knockoff.time,
  cash.time
)
}
fdp.list[[j]] <- fdp.mat
tdn.list[[j]] <- tdn.mat
time.list[[j]] <- time.mat
}
```

```{r plot func, echo = FALSE}
library(reshape2)
library(ggplot2)
mean_sdp <- function(x) {
   m <- mean(x)
   ymax <- m + sd(x)
   return(c(y = m, ymax = ymax, ymin = m))
}
method.name <- c("BH", "qvalue", "Knockoff", "ASH", "Cash", "Cash+")
method.col <- c("blue", "green", "orange", "burlywood4", "red", "maroon")
```

### Overall across all sparsity

```{r avg, echo = 500}
fdp.avg <- sapply(fdp.list, colMeans)
tdn.avg <- sapply(tdn.list, colMeans)

plot(1 - k.vec / p, k.vec, type = "n", ylim = range(fdp.avg, q, 0), ylab = "FDR", xlab = "Sparsity")
for (l in seq(nrow(fdp.avg))) {
  lines(1 - k.vec / p, fdp.avg[l, ], col = method.col[l], type = "o", pch = l)
}
legend("bottomright", lty = 1, pch = seq(nrow(fdp.avg)), col = method.col, legend = method.name, bty = "n")
abline(h = 0.1, lty = 2, lwd = 2)

plot(1 - k.vec / p, k.vec, type = "n", ylim = range(tdn.avg), ylab = "Power", xlab = "Sparsity")
for (l in seq(ncol(tdn.avg))) {
  lines(1 - k.vec / p, tdn.avg[l, ], col = method.col[l], type = "o", pch = l)
}
legend("topright", lty = 1, pch = seq(nrow(fdp.avg)), col = method.col, legend = method.name)
```

### $\eta = 0.5$, $\sigma = 4$, $\rho = 0.5$

```{r 500, echo = FALSE}
ggplot(data = melt(as.data.frame(fdp.list[[1]])),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  geom_hline(yintercept = q, col = "maroon", linetype = "dashed", size = 1) +
  labs(title = bquote(paste("False Discovery Proportions at ", FDR == .(q), " Cutoff")), x = "", y = "Actual False Discovery Proportion (FDP)") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

ggplot(data = melt(as.data.frame(tdn.list[[1]])),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Number of True Discoveries at ", FDR == .(q), " Cutoff")), x = "", y = "Number of True Discoveries") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

boxplot(log(time.list[[1]]), main = "Time Elapsed in Logarithm", ylab = "Log (Time in Seconds)", col = method.col[c(1, 3, 5)])
```

### $\eta = 0.9$, $\sigma = 4$, $\rho = 0.5$


```{r 100, echo = FALSE}
ggplot(data = melt(as.data.frame(fdp.list[[5]])),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  geom_hline(yintercept = q, col = "maroon", linetype = "dashed", size = 1) +
  labs(title = bquote(paste("False Discovery Proportions at ", FDR == .(q), " Cutoff")), x = "", y = "Actual False Discovery Proportion (FDP)") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

ggplot(data = melt(as.data.frame(tdn.list[[5]])),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Number of True Discoveries at ", FDR == .(q), " Cutoff")), x = "", y = "Number of True Discoveries") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

boxplot(log(time.list[[5]]), main = "Time Elapsed in Logarithm", ylab = "Log (Time in Seconds)", col = method.col[c(1, 3, 5)])
```

## $\eta \in \left\{0.5, 0.6, 0.7, 0.8, 0.9\right\}$, $\sigma = 3$, $\rho = 0.7$

```{r sparsity weak, echo = FALSE, cache = TRUE}
set.seed(777)

library(knockoff)
source("../code/gdash_lik.R")
library(ashr)

fdp = function(selected) sum(beta[selected] == 0) / max(1, length(selected))
tdn = function(selected) sum(beta[selected] != 0)

m <- 100

fdp.mat <- matrix(0, ncol = 6, nrow = m)
tdn.mat <- matrix(0, ncol = 6, nrow = m)
time.mat <- matrix(0, ncol = 3, nrow = m)

fdp.list <- list()
tdn.list <- list()
time.list <- list()

colnames(fdp.mat) <- c("BH", "qvalue", "Knockoff", "ASH", "Cash", "Cash+")
colnames(tdn.mat) <- c("BH", "qvalue", "Knockoff", "ASH", "Cash", "Cash+")
colnames(time.mat) <- c("BH", "Knockoff", "Cash")

# Problem parameters
n = 2000          # number of observations
p = 1000           # number of variables
k.vec = 5 : 1 * 100            # number of variables with nonzero coefficients
amplitude = 3   # signal amplitude (for noise level = 1)
q = 0.1          # nominal fdr to control for

# Generate the variables from a multivariate normal distribution
rho = 0.7
Sigma = toeplitz(rho^(0 : (p - 1)))

for (j in seq(length(k.vec))) {
for (i in 1 : m) {
X = matrix(rnorm(n * p), n) %*% chol(Sigma)

# Generate the response from a linear model
k = k.vec[j]
nonzero = sample(p, k)
beta = rep(0, p)
beta[nonzero] = rnorm(k, 0, amplitude) / sqrt(n)
y.sample = function(X) X %*% beta + rnorm(n)
y = y.sample(X)

# Knockoff selection
knockoff.time <- system.time(knockoff.result <- knockoff::knockoff.filter(X, y, knockoffs = create.fixed, statistic = stat.glmnet_lambdasmax, fdr = q))[3]
knockoff.selected <- knockoff.result$selected

# CASH selection
cash.time <- proc.time()
lm.fit <- lm(y ~ X - 1)
betahat <- coef(lm.fit)
sebetahat <- summary(lm.fit)$coefficients[, 2]
cash <- gdash(betahat, sebetahat)
cash.time <- (proc.time() - cash.time)[3]
cash.selected <- (1 : p)[cash$qvalue <= q]

# CASH selection with better penalization
betahat.sigma <- cov2cor(solve(crossprod(X)))
rho.m <- sapply(c(2, 4, 6, 8, 10), function(x) (sum(betahat.sigma^x) - p) / (p * (p - 1)))
w.pen = rep(0, 10)
w.pen[c(2, 4, 6, 8, 10)] = 1 / sqrt(rho.m) * 20 / (1 / sqrt(rho.m))[1]
cash.penalization <- gdash(betahat, sebetahat, w.pen = w.pen)
cash.penalization.selected <- (1 : p)[cash.penalization$qvalue <= q]

# CASH selection with perfect knowledge
sebetahat.perfect <- sqrt(diag(solve(crossprod(X))))
cash.perfect <- gdash(betahat, sebetahat.perfect, w.pen = w.pen)
cash.perfect.selected <- (1 : p)[cash.perfect$qvalue <= q]

# ASH selection
ash <- ashr::ash(betahat, sebetahat, method = "fdr", mixcompdist = "normal")
ash.selected <- (1 : p)[get_qvalue(ash) <= q]


# BH selection
pvalue <- summary(lm.fit)$coefficients[, 4]
BH.time <- system.time(BH <- p.adjust(pvalue, method = "BH"))[3]
BH.selected <- (1 : p)[BH <= q]

# qvalue selection
qvalue <- qvalue::qvalue(pvalue)
qvalue.selected <- (1 : p)[qvalue$qvalues <= q]

fdp.mat[i, ] <- c(
  fdp(BH.selected),
  fdp(qvalue.selected),
  fdp(knockoff.selected),
  fdp(ash.selected),
  fdp(cash.selected),
  fdp(cash.perfect.selected)
)
tdn.mat[i, ] <- c(
  tdn(BH.selected),
  tdn(qvalue.selected),
  tdn(knockoff.selected),
  tdn(ash.selected),
  tdn(cash.selected),
  tdn(cash.perfect.selected)
)
time.mat[i, ] <- c(
  BH.time,
  knockoff.time,
  cash.time
)
}
fdp.list[[j]] <- fdp.mat
tdn.list[[j]] <- tdn.mat
time.list[[j]] <- time.mat
}
```

### Overall across all sparsity

```{r avg weak, echo = 500}
fdp.avg <- sapply(fdp.list, colMeans)
tdn.avg <- sapply(tdn.list, colMeans)

plot(1 - k.vec / p, k.vec, type = "n", ylim = range(fdp.avg, q, 0), ylab = "FDR", xlab = "Sparsity")
for (l in seq(nrow(fdp.avg))) {
  lines(1 - k.vec / p, fdp.avg[l, ], col = method.col[l], type = "o", pch = l)
}
legend("bottomright", lty = 1, pch = seq(nrow(fdp.avg)), col = method.col, legend = method.name, bty = "n")
abline(h = 0.1, lty = 2, lwd = 2)

plot(1 - k.vec / p, k.vec, type = "n", ylim = range(tdn.avg), ylab = "Power", xlab = "Sparsity")
for (l in seq(ncol(tdn.avg))) {
  lines(1 - k.vec / p, tdn.avg[l, ], col = method.col[l], type = "o", pch = l)
}
legend("topright", lty = 1, pch = seq(nrow(fdp.avg)), col = method.col, legend = method.name)
```

### $\eta = 0.5$, $\sigma = 3$, $\rho = 0.7$

```{r 500 weak, echo = FALSE}
ggplot(data = melt(as.data.frame(fdp.list[[1]])),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  geom_hline(yintercept = q, col = "maroon", linetype = "dashed", size = 1) +
  labs(title = bquote(paste("False Discovery Proportions at ", FDR == .(q), " Cutoff")), x = "", y = "Actual False Discovery Proportion (FDP)") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

ggplot(data = melt(as.data.frame(tdn.list[[1]])),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Number of True Discoveries at ", FDR == .(q), " Cutoff")), x = "", y = "Number of True Discoveries") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

boxplot(log(time.list[[1]]), main = "Time Elapsed in Logarithm", ylab = "Log (Time in Seconds)", col = method.col[c(1, 3, 5)])
```

### $\eta = 0.9$, $\sigma = 3$, $\rho = 0.7$

```{r 100 weak, echo = FALSE}
ggplot(data = melt(as.data.frame(fdp.list[[5]])),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  geom_hline(yintercept = q, col = "maroon", linetype = "dashed", size = 1) +
  labs(title = bquote(paste("False Discovery Proportions at ", FDR == .(q), " Cutoff")), x = "", y = "Actual False Discovery Proportion (FDP)") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

ggplot(data = melt(as.data.frame(tdn.list[[5]])),
        aes(x = variable, y = value, col = variable)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Number of True Discoveries at ", FDR == .(q), " Cutoff")), x = "", y = "Number of True Discoveries") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 20), axis.title.y = element_text(size = 20), axis.text.x = element_text(size = 20), axis.text.y = element_text(size = 15))

boxplot(log(time.list[[5]]), main = "Time Elapsed in Logarithm", ylab = "Log (Time in Seconds)", col = method.col[c(1, 3, 5)])
```


## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
