---
title: "`Knockoff` on Correlated Design Matrix"
author: "Lei Sun"
date: 2018-02-01
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

## Introduction

In the `Knockoff` paper simulations, the columns of $X$ are either independent or simulated from a Toeplitz correlation where $Cor(X_i, X_j) = \rho^{|i - j|}$. Here we are replicating the independent results, and investigating how well `Knockoff` deal with other correlation structures.

In the following simulations, we always have $n = 3000$, $p = 1000$. Out of $p = 1000$ $\beta_j$'s, $950$ of them are zeroes, and the rest $k = 50$ signals all have $\beta_j = A$. For a certain $X$, $Y_n \sim N(X_{n\times p}\beta_p, I_n)$. Here are three scenarios to generate the columns of $X_{n \times p}$. All simulations use $q = 0.1$ cutoff.

```{r}
n <- 3000
p <- 1000
k <- 50
q <- 0.1
```

- Scenario 1: Each row of $X$ are independently drawn from $N(0, I_p)$. All columns of $X$ are normalized such that $\|X_j\|_2^2 = 1$. The signal magnitude $A = 3.5$.
- Scenario 2: Each row of $X$ are independently drawn from $N(0, \Sigma_X)$, where $\Sigma_X = \texttt{cov2cor}(B_{p \times d}B_{d\times p}^T + I)$, $d = 5$. All columns of $X$ are normalized such that $\|X_j\|_2^2 = 1$. The signal magnitude $A = 9$ to make sure that the signal is significantly stronger than the noise level $\text{SE}(\hat\beta) = \sqrt{\text{diag}[(X^TX)^{-1}]}$ . [In this case the columns of $X$ will have substantial average correlation, but not necessarily so for $\hat\beta$](design_matrix_2.html).
- Scenario 3: Each row of $X$ (with normalization) are independently drawn from $N(0, \Sigma_{\hat\beta}^{-1})$, where $\Sigma_{\hat\beta} = \texttt{cov2cor}(B_{p \times d}B_{d\times p}^T + I)$, $d = 5$. We'll have $(X^TX)^{-1}\approx\Sigma_{\hat\beta}$. In this case $\hat\beta_j$'s will have substantial average correlation. The signal magnitude $A = 3.5$.

```{r, echo = FALSE}
fdp <- function(selected) sum(beta[selected] == 0) / max(length(selected), 1)
power <- function(selected, k = k) sum(beta[selected] != 0) / max(k, 1)
library(knockoff)
```

## Scenario 1: Independent $X$ columns

```{r, cache = TRUE}
set.seed(777)
## Independent columns
X <- matrix(rnorm(n * p), n , p)
## Normalization
X <- t(t(X) / sqrt(colSums(X^2)))
## Generate knockoffs
Xk <- knockoff::create.fixed(X)
Xk <- Xk$Xk
## Average sebetahat
sqrt(mean(diag(solve(crossprod(X)))))
## Signal strength
A <- 3.5
## Set beta
beta <- rep(0, p)
nonzero <- sample(p, k)
beta[nonzero] <- A
```

```{r, echo = FALSE, cache = TRUE}
m <- 500

result <- list()

for (i in 1 : m) {
y <- X %*% beta + rnorm(n)

## Least squares
lm.fit <- lm(y ~ X - 1)
pvalue <- summary(lm.fit)$coefficients[, 4]

## BH
BH.fit <- p.adjust(pvalue, method = "BH")
BH.selected <- (1 : p)[BH.fit <= q]

## Knockoff
W = stat.glmnet_lambdasmax(X, Xk, y)
thres.knockoff = knockoff.threshold(W, fdr = q, offset = 0) # less conservative
thres.knockoff.plus = knockoff.threshold(W, fdr = q, offset = 1) # more conservative
knockoff.selected <- which(W >= thres.knockoff)
knockoff.plus.selected <- which(W >= thres.knockoff.plus)

result[[i]] <- c(
  fdp.BH = fdp(BH.selected),
  fdp.knockoff = fdp(knockoff.selected),
  fdp.knockoff.plus = fdp(knockoff.plus.selected),
  power.BH = power(BH.selected, k),
  power.knockoff = power(knockoff.selected, k),
  power.knockoff.plus = power(knockoff.plus.selected, k)
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 6, byrow = TRUE)
colnames(result.summary) <- c("fdp.BH", "fdp.Knockoff", "fdp.Knockoff.plus", "power.BH", "power.Knockoff", "power.Knockoff.plus")
result.indep <- result.summary
```

## Scenario 2: $X$ from a factor model

```{r, cache = TRUE}
set.seed(777)
## Generate correlation matrix of X
d <- 5
B <- matrix(rnorm(p * d, 0, 1), p, d)
Sigma.X <- tcrossprod(B) + diag(p)
Rho.X <- cov2cor(Sigma.X)
## Simulate X
X <- matrix(rnorm(n * p), n, p) %*% chol(Rho.X)
## Normalization
X <- t(t(X) / sqrt(colSums(X^2)))
## Generate knockoffs
Xk <- knockoff::create.fixed(X)
Xk <- Xk$Xk
## Average sebetahat
sqrt(mean(diag(solve(crossprod(X)))))
## Signal strength
A <- 9
## Set beta
beta <- rep(0, p)
nonzero <- sample(p, k)
beta[nonzero] <- A
```

```{r, echo = FALSE, cache = TRUE}
m <- 500

result <- list()

for (i in 1 : m) {
y <- X %*% beta + rnorm(n)

## Least squares
lm.fit <- lm(y ~ X - 1)
pvalue <- summary(lm.fit)$coefficients[, 4]

## BH
BH.fit <- p.adjust(pvalue, method = "BH")
BH.selected <- (1 : p)[BH.fit <= q]

## Knockoff
W = stat.glmnet_lambdasmax(X, Xk, y)
thres.knockoff = knockoff.threshold(W, fdr = q, offset = 0) # less conservative
thres.knockoff.plus = knockoff.threshold(W, fdr = q, offset = 1) # more conservative
knockoff.selected <- which(W >= thres.knockoff)
knockoff.plus.selected <- which(W >= thres.knockoff.plus)

result[[i]] <- c(
  fdp.BH = fdp(BH.selected),
  fdp.knockoff = fdp(knockoff.selected),
  fdp.knockoff.plus = fdp(knockoff.plus.selected),
  power.BH = power(BH.selected, k),
  power.knockoff = power(knockoff.selected, k),
  power.knockoff.plus = power(knockoff.plus.selected, k)
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 6, byrow = TRUE)
colnames(result.summary) <- c("fdp.BH", "fdp.Knockoff", "fdp.Knockoff.plus", "power.BH", "power.Knockoff", "power.Knockoff.plus")
result.SigmaX <- result.summary
```

## Scenario 3: $\hat\beta$ from a factor model

```{r, cache = TRUE}
set.seed(777)
## Generate correlation matrix of betahat
d <- 5
B <- matrix(rnorm(p * d, 0, 1), p, d)
Sigma.betahat <- tcrossprod(B) + diag(p)
Cor.betahat <- cov2cor(Sigma.betahat)
## Simulate X with independent columns
X <- matrix(rnorm(n * p), n, p)
## Normalize X
X <- t(t(X) / sqrt(colSums(X^2)))
## Transform independent columns to have Sigma_betahat^{-1} correlation structure
X <- X %*% chol(solve(Cor.betahat))
## Generate knockoffs
Xk <- knockoff::create.fixed(X)
Xk <- Xk$Xk
## Average sebetahat
sqrt(mean(diag(solve(crossprod(X)))))
## Signal strength
A <- 3.5
## Set beta
beta <- rep(0, p)
nonzero <- sample(p, k)
beta[nonzero] <- A
```

```{r, echo = FALSE, cache = TRUE}
m <- 500

result <- list()

for (i in 1 : m) {
y <- X %*% beta + rnorm(n)

## Least squares
lm.fit <- lm(y ~ X - 1)
pvalue <- summary(lm.fit)$coefficients[, 4]

## BH
BH.fit <- p.adjust(pvalue, method = "BH")
BH.selected <- (1 : p)[BH.fit <= q]

## Knockoff
W = stat.glmnet_lambdasmax(X, Xk, y)
thres.knockoff = knockoff.threshold(W, fdr = q, offset = 0) # less conservative
thres.knockoff.plus = knockoff.threshold(W, fdr = q, offset = 1) # more conservative
knockoff.selected <- which(W >= thres.knockoff)
knockoff.plus.selected <- which(W >= thres.knockoff.plus)

result[[i]] <- c(
  fdp.BH = fdp(BH.selected),
  fdp.knockoff = fdp(knockoff.selected),
  fdp.knockoff.plus = fdp(knockoff.plus.selected),
  power.BH = power(BH.selected, k),
  power.knockoff = power(knockoff.selected, k),
  power.knockoff.plus = power(knockoff.plus.selected, k)
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 6, byrow = TRUE)
colnames(result.summary) <- c("fdp.BH", "fdp.Knockoff", "fdp.Knockoff.plus", "power.BH", "power.Knockoff", "power.Knockoff.plus")
result.Sigmabetahat <- result.summary
```

```{r, echo = FALSE}
summary <- rbind.data.frame(colMeans(result.indep), colMeans(result.SigmaX), colMeans(result.Sigmabetahat))
colnames(summary) <- c("FDP.BH", "FDP.Knockoff", "FDP.Knockoff.Plus", "Power.BH", "Power.Knockoff", "Power.Knockoff.Plus")
rownames(summary) <- c("Independent Columns", "Factor Model for X", "Factor Model for betahat")
library(knitr)
kable(summary, digits = 4)
```

```{r, echo = FALSE}
library(ggplot2)
mean_sdp <- function(x) {
   m <- mean(x)
   ymax <- m + sd(x)
   return(c(y = m, ymax = ymax, ymin = m))
}
method.name <- c("BH", "Knockoff", "Knockoff+")
method.col <- c("blue", "red", "maroon")
```

```{r, echo = FALSE}
FDP.summary <- rbind.data.frame(
   cbind.data.frame(FDP = result.indep[, 1], Method = rep("BH", length(result.indep[, 1])), Scenario = rep("Independent Columns", length(result.indep[, 1]))),
   cbind.data.frame(FDP = result.indep[, 2], Method = rep("Knockoff", length(result.indep[, 2])), Scenario = rep("Independent Columns", length(result.indep[, 2]))),
   cbind.data.frame(FDP = result.indep[, 3], Method = rep("Knockoff+", length(result.indep[, 3])), Scenario = rep("Independent Columns", length(result.indep[, 3]))),
   cbind.data.frame(FDP = result.SigmaX[, 1], Method = rep("BH", length(result.SigmaX[, 1])), Scenario = rep("Factor Model for X", length(result.SigmaX[, 1]))),
   cbind.data.frame(FDP = result.SigmaX[, 2], Method = rep("Knockoff", length(result.SigmaX[, 2])), Scenario = rep("Factor Model for X", length(result.SigmaX[, 2]))),
   cbind.data.frame(FDP = result.SigmaX[, 3], Method = rep("Knockoff+", length(result.SigmaX[, 3])), Scenario = rep("Factor Model for X", length(result.SigmaX[, 3]))),
   cbind.data.frame(FDP = result.Sigmabetahat[, 1], Method = rep("BH", length(result.Sigmabetahat[, 1])), Scenario = rep("Factor Model for betahat", length(result.Sigmabetahat[, 1]))),
   cbind.data.frame(FDP = result.Sigmabetahat[, 2], Method = rep("Knockoff", length(result.Sigmabetahat[, 2])), Scenario = rep("Factor Model for betahat", length(result.Sigmabetahat[, 2]))),
   cbind.data.frame(FDP = result.Sigmabetahat[, 3], Method = rep("Knockoff+", length(result.Sigmabetahat[, 3])), Scenario = rep("Factor Model for betahat", length(result.Sigmabetahat[, 3])))
 )

ggplot(data = FDP.summary,
        aes(x = Method, y = FDP, col = Method)) +
  geom_violin(trim = TRUE) +
  facet_wrap(~Scenario) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  geom_hline(yintercept = q, col = "maroon", linetype = "dashed", size = 1) +
  labs(title = bquote(paste("False Discovery Proportions at Nominal ", FDR == .(q), " Cutoff")), x = "", y = "FDP") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 15), axis.title.y = element_text(size = 15), axis.text.x = element_text(size = 9), axis.text.y = element_text(size = 15))
```

```{r, echo = FALSE}
Power.summary <- rbind.data.frame(
   cbind.data.frame(Power = result.indep[, 4], Method = rep("BH", length(result.indep[, 4])), Scenario = rep("Independent Columns", length(result.indep[, 4]))),
   cbind.data.frame(Power = result.indep[, 5], Method = rep("Knockoff", length(result.indep[, 5])), Scenario = rep("Independent Columns", length(result.indep[, 5]))),
   cbind.data.frame(Power = result.indep[, 6], Method = rep("Knockoff+", length(result.indep[, 6])), Scenario = rep("Independent Columns", length(result.indep[, 6]))),
   cbind.data.frame(Power = result.SigmaX[, 4], Method = rep("BH", length(result.SigmaX[, 4])), Scenario = rep("Factor Model for X", length(result.SigmaX[, 4]))),
   cbind.data.frame(Power = result.SigmaX[, 5], Method = rep("Knockoff", length(result.SigmaX[, 5])), Scenario = rep("Factor Model for X", length(result.SigmaX[, 5]))),
   cbind.data.frame(Power = result.SigmaX[, 6], Method = rep("Knockoff+", length(result.SigmaX[, 6])), Scenario = rep("Factor Model for X", length(result.SigmaX[, 6]))),
   cbind.data.frame(Power = result.Sigmabetahat[, 4], Method = rep("BH", length(result.Sigmabetahat[, 4])), Scenario = rep("Factor Model for betahat", length(result.Sigmabetahat[, 4]))),
   cbind.data.frame(Power = result.Sigmabetahat[, 5], Method = rep("Knockoff", length(result.Sigmabetahat[, 5])), Scenario = rep("Factor Model for betahat", length(result.Sigmabetahat[, 5]))),
   cbind.data.frame(Power = result.Sigmabetahat[, 6], Method = rep("Knockoff+", length(result.Sigmabetahat[, 6])), Scenario = rep("Factor Model for betahat", length(result.Sigmabetahat[, 6])))
 )

ggplot(data = Power.summary,
        aes(x = Method, y = Power, col = Method)) +
  geom_violin(trim = TRUE) +
  facet_wrap(~Scenario) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Power at Nominal ", FDR == .(q), " Cutoff")), x = "", y = "Power") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 15), axis.title.y = element_text(size = 15), axis.text.x = element_text(size = 9), axis.text.y = element_text(size = 15))
```

## Comparison across correlation levels (various $d$)

### Scenario 2: $X$ from a factor model

```{r factor_X_overall, echo = FALSE, cache = TRUE}
d.vec <- c(1, 5, 10, 50, 100, 500, 1000)
set.seed(777)
result.SigmaX <- matrix(0, length(d.vec), 6)
colnames(result.SigmaX) <- c("fdp.BH", "fdp.Knockoff", "fdp.Knockoff.plus", "power.BH", "power.Knockoff", "power.Knockoff.plus")
rownames(result.SigmaX) <- paste("d =", d.vec)
for (j in seq(length(d.vec))) {
## Generate correlation matrix of betahat
d <- d.vec[j]
B <- matrix(rnorm(p * d, 0, 1), p, d)
Sigma.X <- tcrossprod(B) + diag(p)
Rho.X <- cov2cor(Sigma.X)
## Simulate X
X <- matrix(rnorm(n * p), n, p) %*% chol(Rho.X)
## Normalization
X <- t(t(X) / sqrt(colSums(X^2)))
## Generate knockoffs
Xk <- knockoff::create.fixed(X)
Xk <- Xk$Xk
## Signal strength
A <- ceiling(3 * sqrt(mean(diag(solve(crossprod(X))))))
## Set beta
beta <- rep(0, p)
nonzero <- sample(p, k)
beta[nonzero] <- A
m <- 100
result <- list()
for (i in 1 : m) {
y <- X %*% beta + rnorm(n)

## Least squares
lm.fit <- lm(y ~ X - 1)
pvalue <- summary(lm.fit)$coefficients[, 4]

## BH
BH.fit <- p.adjust(pvalue, method = "BH")
BH.selected <- (1 : p)[BH.fit <= q]

## Knockoff
W = stat.glmnet_lambdasmax(X, Xk, y)
thres.knockoff = knockoff.threshold(W, fdr = q, offset = 0) # less conservative
thres.knockoff.plus = knockoff.threshold(W, fdr = q, offset = 1) # more conservative
knockoff.selected <- which(W >= thres.knockoff)
knockoff.plus.selected <- which(W >= thres.knockoff.plus)

result[[i]] <- c(
  fdp.BH = fdp(BH.selected),
  fdp.knockoff = fdp(knockoff.selected),
  fdp.knockoff.plus = fdp(knockoff.plus.selected),
  power.BH = power(BH.selected, k),
  power.knockoff = power(knockoff.selected, k),
  power.knockoff.plus = power(knockoff.plus.selected, k)
)
}
result.summary <- matrix(unlist(result), m, 6, byrow = TRUE)
result.SigmaX[j, ] <- colMeans(result.summary)
}
```

```{r, echo = FALSE}
plot(log(d.vec), d.vec, type = "n", ylim = range(0, result.SigmaX[, 1 : 3]), xlab = expression(d), ylab = "FDR", main = expression(paste("FDR: Factor Model for ", X)), xaxt = "n")
axis(1, at = log(d.vec), labels = d.vec)
for (i in 1 : 3) {
  lines(log(d.vec), result.SigmaX[, i], type = "o", col = method.col[i], pch = i)
}
abline(h = q, lty = 2, lwd = 2)
legend("topright", col = method.col, lty = 1, pch = 1 : 3, legend = method.name)

plot(log(d.vec), d.vec, type = "n", ylim = range(0, 1, result.SigmaX[, 4 : 6]), xlab = expression(d), ylab = "Power", main = expression(paste("Power: Factor Model for ", X)), xaxt = "n")
axis(1, at = log(d.vec), labels = d.vec)
for (i in 1 : 3) {
  lines(log(d.vec), result.SigmaX[, (i + 3)], type = "o", col = method.col[i], pch = i)
}
legend("topright", col = method.col, lty = 1, pch = 1 : 3, legend = method.name)
```

### Scenario 3: $\hat\beta$ from a factor model

```{r factor_betahat_overall, echo = FALSE, cache = TRUE}
d.vec <- c(1, 5, 10, 50, 100, 500, 1000)
set.seed(777)
result.Sigmabetahat <- matrix(0, length(d.vec), 6)
colnames(result.Sigmabetahat) <- c("fdp.BH", "fdp.Knockoff", "fdp.Knockoff.plus", "power.BH", "power.Knockoff", "power.Knockoff.plus")
rownames(result.Sigmabetahat) <- paste("d =", d.vec)
for (j in seq(length(d.vec))) {
## Generate correlation matrix of betahat
d <- d.vec[j]
B <- matrix(rnorm(p * d, 0, 1), p, d)
Sigma.betahat <- tcrossprod(B) + diag(p)
Cor.betahat <- cov2cor(Sigma.betahat)
## Simulate X with independent columns
X <- matrix(rnorm(n * p), n, p)
## Normalize X
X <- t(t(X) / sqrt(colSums(X^2)))
## Transform independent columns to have Sigma_betahat^{-1} correlation structure
X <- X %*% chol(solve(Cor.betahat))
## Generate knockoffs
Xk <- knockoff::create.fixed(X)
Xk <- Xk$Xk
## Signal strength
A <- 3.5
## Set beta
beta <- rep(0, p)
nonzero <- sample(p, k)
beta[nonzero] <- A
m <- 100
result <- list()
for (i in 1 : m) {
y <- X %*% beta + rnorm(n)

## Least squares
lm.fit <- lm(y ~ X - 1)
pvalue <- summary(lm.fit)$coefficients[, 4]

## BH
BH.fit <- p.adjust(pvalue, method = "BH")
BH.selected <- (1 : p)[BH.fit <= q]

## Knockoff
W = stat.glmnet_lambdasmax(X, Xk, y)
thres.knockoff = knockoff.threshold(W, fdr = q, offset = 0) # less conservative
thres.knockoff.plus = knockoff.threshold(W, fdr = q, offset = 1) # more conservative
knockoff.selected <- which(W >= thres.knockoff)
knockoff.plus.selected <- which(W >= thres.knockoff.plus)

result[[i]] <- c(
  fdp.BH = fdp(BH.selected),
  fdp.knockoff = fdp(knockoff.selected),
  fdp.knockoff.plus = fdp(knockoff.plus.selected),
  power.BH = power(BH.selected, k),
  power.knockoff = power(knockoff.selected, k),
  power.knockoff.plus = power(knockoff.plus.selected, k)
)
}
result.summary <- matrix(unlist(result), m, 6, byrow = TRUE)
result.Sigmabetahat[j, ] <- colMeans(result.summary)
}
```

```{r, echo = FALSE}
plot(log(d.vec), d.vec, type = "n", ylim = range(0, result.Sigmabetahat[, 1 : 3]), xlab = expression(d), ylab = "FDR", main = expression(paste("FDR: Factor Model for ", Sigma[hat(beta)])), xaxt = "n")
axis(1, at = log(d.vec), labels = d.vec)
for (i in 1 : 3) {
  lines(log(d.vec), result.Sigmabetahat[, i], type = "o", col = method.col[i], pch = i)
}
abline(h = q, lty = 2, lwd = 2)
legend("topright", col = method.col, lty = 1, pch = 1 : 3, legend = method.name)

plot(log(d.vec), d.vec, type = "n", ylim = range(0, 1, result.Sigmabetahat[, 4 : 6]), xlab = expression(d), ylab = "Power", main = expression(paste("Power: Factor Model for ", Sigma[hat(beta)])), xaxt = "n")
axis(1, at = log(d.vec), labels = d.vec)
for (i in 1 : 3) {
  lines(log(d.vec), result.Sigmabetahat[, (i + 3)], type = "o", col = method.col[i], pch = i)
}
legend("topright", col = method.col, lty = 1, pch = 1 : 3, legend = method.name)
```

## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
