---
title: "Knockoff vs Bayesian: Mixture normal signals"
author: "Lei Sun"
date: 2018-04-03
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

## Introduction

The true $\beta$ are simulated as $\beta \sim \pi_0\delta_0 + (1 - \pi_0)N(0, \sigma_\beta^2)$.

```{r, echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE}
library(ashr)
library(varbvs)
library(knockoff)
library(Matrix)
library(reshape2)
library(ggplot2)
library(lattice)
library(doMC)
```

```{r, echo = FALSE, cache = TRUE}
n <- 2000
p <- 1000
k <- 200
m <- 100
q <- 0.1
```

## $n > p$

### Independent design

$X_{n \times p}$ has independent columns simulated from $N(0, (1/\sqrt n)^2)$ so they are roughly normalized.

```{r, echo = FALSE, cache = TRUE}
Cov.X <- diag(1 / n, p)
```

```{r, echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE}
A <- 5
result <- list()
for (i in 1 : m) {
beta <- rep(0, p)
nonzero <- sample(p, k)
beta[nonzero] <- rnorm(k, 0, A)

X <- matrix(rnorm(n * p, 0, sqrt(1 / n)), n, p)
y <- X %*% beta + rnorm(n)

## Least squares
lm.fit <- lm(y ~ X - 1)
pvalue <- summary(lm.fit)$coefficients[, 4]
betahat <- summary(lm.fit)$coefficients[, 1]
sebetahat <- summary(lm.fit)$coefficients[, 2]

## BH
BH.fit <- p.adjust(pvalue, method = "BH")
BH.selected <- (1 : p)[BH.fit <= q]

## ASH
ash.fit <- ashr::ash(betahat, sebetahat, mixcompdist = "normal", method = "fdr")
ash.selected <- (1 : p)[get_qvalue(ash.fit) <= q]

## Knockoff
Xk <- knockoff::create.gaussian(X, mu = rep(0, p), Sigma = Cov.X, method = "equi")
W <- knockoff::stat.glmnet_coefdiff(X, Xk, y, cores = 4)
thres.knockoff = knockoff::knockoff.threshold(W, fdr = q, offset = 0) # less conservative
thres.knockoff.plus = knockoff::knockoff.threshold(W, fdr = q, offset = 1) # more conservative
knockoff.selected <- which(W >= thres.knockoff)
knockoff.plus.selected <- which(W >= thres.knockoff.plus)

Xk2 <- knockoff::create.second_order(X, method = "equi")
W2 <- knockoff::stat.glmnet_coefdiff(X, Xk2, y, cores = 4)
thres.knockoff2 = knockoff::knockoff.threshold(W2, fdr = q, offset = 0) # less conservative
thres.knockoff.plus2 = knockoff::knockoff.threshold(W2, fdr = q, offset = 1) # more conservative
knockoff.selected2 <- which(W2 >= thres.knockoff2)
knockoff.plus.selected2 <- which(W2 >= thres.knockoff.plus2)

## varbvs
varbvs.fit <- varbvs(X, NULL, y, verbose = FALSE)
varbvs.lfdr <- 1 - varbvs.fit$pip
varbvs.q <- ashr::qval.from.lfdr(varbvs.lfdr)
varbvs.q.selected <- (1 : p)[varbvs.q <= q]

## varbvsmix
varbvsmix.fit <- varbvs::varbvsmix(X, NULL, y, sa = ash.fit$fitted_g$sd, verbose = FALSE)
varbvsmix.lfdr <- varbvsmix.fit$alpha[, 1]
varbvsmix.q <- ashr::qval.from.lfdr(varbvsmix.lfdr)
varbvsmix.q.selected <- (1 : p)[varbvsmix.q <= q]
varbvsmix.lfsr <- varbvsmix.fit$lfsr
varbvsmix.s <- ashr::qval.from.lfdr(varbvsmix.lfsr)
varbvsmix.s.selected <- (1 : p)[varbvsmix.s <= q]

result[[i]] <- c(
  fdp.BH = sum(beta[BH.selected] == 0) / max(1, length(BH.selected)),
  fdp.ash = sum(beta[ash.selected] == 0) / max(1, length(ash.selected)),
  fdp.knockoff = sum(beta[knockoff.selected] == 0) / max(1, length(knockoff.selected)),
  fdp.knockoff.plus = sum(beta[knockoff.plus.selected] == 0) / max(1, length(knockoff.plus.selected)),
  fdp.knockoff.est = sum(beta[knockoff.selected2] == 0) / max(1, length(knockoff.selected2)),
  fdp.knockoff.plus.est = sum(beta[knockoff.plus.selected2] == 0) / max(1, length(knockoff.plus.selected2)),
  fdp.varbvs = sum(beta[varbvs.selected] == 0) / max(1, length(varbvs.selected)),
  power.BH = sum(beta[BH.selected] != 0) / k,
  power.ash = sum(beta[ash.selected] != 0) / k,
  power.knockoff = sum(beta[knockoff.selected] != 0) / k,
  power.knockoff.plus = sum(beta[knockoff.plus.selected] != 0) / k,
  power.knockoff.est = sum(beta[knockoff.selected2] != 0) / k,
  power.knockoff.plus.est = sum(beta[knockoff.plus.selected2] != 0) / k,
  power.varbvs = sum(beta[varbvs.selected] != 0) / k
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 14, byrow = TRUE)
boxplot(result.summary[, 1 : 7], names = c("BH", "ASH", "Knockoff.G", "Knockoff+.G", "Knockoff.E", "Knockoff+.E", "varbvsmix"), ylab = "FDP", las = 2)
abline(h = q, lty = 2, col = "red")
boxplot(result.summary[, 8 : 14], names = c("BH", "ASH", "Knockoff.G", "Knockoff+.G", "Knockoff.E", "Knockoff+.E", "varbvsmix"), ylab = "TDP", las = 2)
```

### Local correlation design

$X_{n \times p}$ has correlation $\Sigma_{ij} = \rho^{|i - j|}$. Each row is independently $N(0, \frac1n\Sigma)$.

```{r, cache = TRUE, echo = FALSE}
rho <- 0.5
Sigma <- toeplitz(rho^(0 : (p - 1)))
Sigma.5 <- chol(Sigma)
Cov.X <- Sigma / n
```

```{r, echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE}
A <- 5
result <- list()
for (i in 1 : m) {
beta <- rep(0, p)
nonzero <- sample(p, k)
beta[nonzero] <- rnorm(k, 0, A)

X <- matrix(rnorm(n * p, 0, sqrt(1 / n)), n, p)
X <- X %*% Sigma.5
y <- X %*% beta + rnorm(n)

## Least squares
lm.fit <- lm(y ~ X - 1)
pvalue <- summary(lm.fit)$coefficients[, 4]
betahat <- summary(lm.fit)$coefficients[, 1]
sebetahat <- summary(lm.fit)$coefficients[, 2]

## BH
BH.fit <- p.adjust(pvalue, method = "BH")
BH.selected <- (1 : p)[BH.fit <= q]

## ASH
ash.fit <- ashr::ash(betahat, sebetahat, mixcompdist = "normal", method = "fdr")
ash.selected <- (1 : p)[get_qvalue(ash.fit) <= q]

## Knockoff
Xk <- knockoff::create.gaussian(X, mu = rep(0, p), Sigma = Cov.X, method = "equi")
W <- knockoff::stat.glmnet_coefdiff(X, Xk, y, cores = 4)
thres.knockoff = knockoff::knockoff.threshold(W, fdr = q, offset = 0) # less conservative
thres.knockoff.plus = knockoff::knockoff.threshold(W, fdr = q, offset = 1) # more conservative
knockoff.selected <- which(W >= thres.knockoff)
knockoff.plus.selected <- which(W >= thres.knockoff.plus)

Xk2 <- knockoff::create.second_order(X, method = "equi")
W2 <- knockoff::stat.glmnet_coefdiff(X, Xk2, y, cores = 4)
thres.knockoff2 = knockoff::knockoff.threshold(W2, fdr = q, offset = 0) # less conservative
thres.knockoff.plus2 = knockoff::knockoff.threshold(W2, fdr = q, offset = 1) # more conservative
knockoff.selected2 <- which(W2 >= thres.knockoff2)
knockoff.plus.selected2 <- which(W2 >= thres.knockoff.plus2)

## varbvs
varbvs.fit <- varbvs::varbvsmix(X, NULL, y, sa = ash.fit$fitted_g$sd, verbose = FALSE)
varbvs.lfdr <- varbvs.fit$alpha[, 1]
varbvs.q <- ashr::qval.from.lfdr(varbvs.lfdr)
varbvs.selected <- (1 : p)[varbvs.q <= q]

result[[i]] <- c(
  fdp.BH = sum(beta[BH.selected] == 0) / max(1, length(BH.selected)),
  fdp.ash = sum(beta[ash.selected] == 0) / max(1, length(ash.selected)),
  fdp.knockoff = sum(beta[knockoff.selected] == 0) / max(1, length(knockoff.selected)),
  fdp.knockoff.plus = sum(beta[knockoff.plus.selected] == 0) / max(1, length(knockoff.plus.selected)),
  fdp.knockoff.est = sum(beta[knockoff.selected2] == 0) / max(1, length(knockoff.selected2)),
  fdp.knockoff.plus.est = sum(beta[knockoff.plus.selected2] == 0) / max(1, length(knockoff.plus.selected2)),
  fdp.varbvs = sum(beta[varbvs.selected] == 0) / max(1, length(varbvs.selected)),
  power.BH = sum(beta[BH.selected] != 0) / k,
  power.ash = sum(beta[ash.selected] != 0) / k,
  power.knockoff = sum(beta[knockoff.selected] != 0) / k,
  power.knockoff.plus = sum(beta[knockoff.plus.selected] != 0) / k,
  power.knockoff.est = sum(beta[knockoff.selected2] != 0) / k,
  power.knockoff.plus.est = sum(beta[knockoff.plus.selected2] != 0) / k,
  power.varbvs = sum(beta[varbvs.selected] != 0) / k
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 14, byrow = TRUE)
boxplot(result.summary[, 1 : 7], names = c("BH", "ASH", "Knockoff.G", "Knockoff+.G", "Knockoff.E", "Knockoff+.E", "varbvsmix"), ylab = "FDP", las = 2)
abline(h = q, lty = 2, col = "red")
boxplot(result.summary[, 8 : 14], names = c("BH", "ASH", "Knockoff.G", "Knockoff+.G", "Knockoff.E", "Knockoff+.E", "varbvsmix"), ylab = "TDP", las = 2)
```

### Factor Model for $X$

```{r, echo = FALSE, cache = TRUE}
d <- 5
B <- matrix(rnorm(p * d), p, d)
Cor.X <- cov2cor(tcrossprod(B) + diag(p))
Cor.X.5 <- chol(Cor.X)
Cov.X <- Cor.X / n
```

```{r, echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE}
A <- 7
result <- list()
for (i in 1 : m) {
beta <- rep(0, p)
nonzero <- sample(p, k)
beta[nonzero] <- rnorm(k, 0, A)

X <- matrix(rnorm(n * p, 0, sqrt(1 / n)), n) %*% Cor.X.5
y <- X %*% beta + rnorm(n)

## Least squares
lm.fit <- lm(y ~ X - 1)
pvalue <- summary(lm.fit)$coefficients[, 4]
betahat <- summary(lm.fit)$coefficients[, 1]
sebetahat <- summary(lm.fit)$coefficients[, 2]

## BH
BH.fit <- p.adjust(pvalue, method = "BH")
BH.selected <- (1 : p)[BH.fit <= q]

## ASH
ash.fit <- ashr::ash(betahat, sebetahat, mixcompdist = "normal", method = "fdr")
ash.selected <- (1 : p)[get_qvalue(ash.fit) <= q]

## Knockoff
Xk <- knockoff::create.gaussian(X, mu = rep(0, p), Sigma = Cov.X, method = "equi")
W <- knockoff::stat.glmnet_coefdiff(X, Xk, y, cores = 4)
thres.knockoff = knockoff::knockoff.threshold(W, fdr = q, offset = 0) # less conservative
thres.knockoff.plus = knockoff::knockoff.threshold(W, fdr = q, offset = 1) # more conservative
knockoff.selected <- which(W >= thres.knockoff)
knockoff.plus.selected <- which(W >= thres.knockoff.plus)

Xk2 <- knockoff::create.second_order(X, method = "equi")
W2 <- knockoff::stat.glmnet_coefdiff(X, Xk2, y, cores = 4)
thres.knockoff2 = knockoff::knockoff.threshold(W2, fdr = q, offset = 0) # less conservative
thres.knockoff.plus2 = knockoff::knockoff.threshold(W2, fdr = q, offset = 1) # more conservative
knockoff.selected2 <- which(W2 >= thres.knockoff2)
knockoff.plus.selected2 <- which(W2 >= thres.knockoff.plus2)

## varbvs
varbvs.fit <- varbvs::varbvsmix(X, NULL, y, sa = ash.fit$fitted_g$sd, verbose = FALSE)
varbvs.lfdr <- varbvs.fit$alpha[, 1]
varbvs.q <- ashr::qval.from.lfdr(varbvs.lfdr)
varbvs.selected <- (1 : p)[varbvs.q <= q]

result[[i]] <- c(
  fdp.BH = sum(beta[BH.selected] == 0) / max(1, length(BH.selected)),
  fdp.ash = sum(beta[ash.selected] == 0) / max(1, length(ash.selected)),
  fdp.knockoff = sum(beta[knockoff.selected] == 0) / max(1, length(knockoff.selected)),
  fdp.knockoff.plus = sum(beta[knockoff.plus.selected] == 0) / max(1, length(knockoff.plus.selected)),
  fdp.knockoff.est = sum(beta[knockoff.selected2] == 0) / max(1, length(knockoff.selected2)),
  fdp.knockoff.plus.est = sum(beta[knockoff.plus.selected2] == 0) / max(1, length(knockoff.plus.selected2)),
  fdp.varbvs = sum(beta[varbvs.selected] == 0) / max(1, length(varbvs.selected)),
  power.BH = sum(beta[BH.selected] != 0) / k,
  power.ash = sum(beta[ash.selected] != 0) / k,
  power.knockoff = sum(beta[knockoff.selected] != 0) / k,
  power.knockoff.plus = sum(beta[knockoff.plus.selected] != 0) / k,
  power.knockoff.est = sum(beta[knockoff.selected2] != 0) / k,
  power.knockoff.plus.est = sum(beta[knockoff.plus.selected2] != 0) / k,
  power.varbvs = sum(beta[varbvs.selected] != 0) / k
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 14, byrow = TRUE)
boxplot(result.summary[, 1 : 7], names = c("BH", "ASH", "Knockoff.G", "Knockoff+.G", "Knockoff.E", "Knockoff+.E", "varbvsmix"), ylab = "FDP", las = 2)
abline(h = q, lty = 2, col = "red")
boxplot(result.summary[, 8 : 14], names = c("BH", "ASH", "Knockoff.G", "Knockoff+.G", "Knockoff.E", "Knockoff+.E", "varbvsmix"), ylab = "TDP", las = 2)
```

### Factor Model for $\hat\beta$

```{r, echo = FALSE, cache = TRUE}
d <- 5
B <- matrix(rnorm(p * d), p, d)
Cor.X <- signif(cov2cor(solve(tcrossprod(B) + diag(p))), digits = 6)
Cor.X.5 <- chol(Cor.X)
Cov.X <- Cor.X / n
```

```{r, echo = FALSE, cache = TRUE, message = FALSE, warning = FALSE}
A <- 7
result <- list()
for (i in 1 : m) {
beta <- rep(0, p)
nonzero <- sample(p, k)
beta[nonzero] <- rnorm(k, 0, A)

X <- matrix(rnorm(n * p, 0, sqrt(1 / n)), n) %*% Cor.X.5
y <- X %*% beta + rnorm(n)

## Least squares
lm.fit <- lm(y ~ X - 1)
pvalue <- summary(lm.fit)$coefficients[, 4]
betahat <- summary(lm.fit)$coefficients[, 1]
sebetahat <- summary(lm.fit)$coefficients[, 2]

## BH
BH.fit <- p.adjust(pvalue, method = "BH")
BH.selected <- (1 : p)[BH.fit <= q]

## ASH
ash.fit <- ashr::ash(betahat, sebetahat, mixcompdist = "normal", method = "fdr")
ash.selected <- (1 : p)[get_qvalue(ash.fit) <= q]

## Knockoff
Xk <- knockoff::create.gaussian(X, mu = rep(0, p), Sigma = Cov.X, method = "equi")
W <- knockoff::stat.glmnet_coefdiff(X, Xk, y, cores = 4)
thres.knockoff = knockoff::knockoff.threshold(W, fdr = q, offset = 0) # less conservative
thres.knockoff.plus = knockoff::knockoff.threshold(W, fdr = q, offset = 1) # more conservative
knockoff.selected <- which(W >= thres.knockoff)
knockoff.plus.selected <- which(W >= thres.knockoff.plus)

Xk2 <- knockoff::create.second_order(X, method = "equi")
W2 <- knockoff::stat.glmnet_coefdiff(X, Xk2, y, cores = 4)
thres.knockoff2 = knockoff::knockoff.threshold(W2, fdr = q, offset = 0) # less conservative
thres.knockoff.plus2 = knockoff::knockoff.threshold(W2, fdr = q, offset = 1) # more conservative
knockoff.selected2 <- which(W2 >= thres.knockoff2)
knockoff.plus.selected2 <- which(W2 >= thres.knockoff.plus2)

## varbvs
varbvs.fit <- varbvs::varbvsmix(X, NULL, y, sa = ash.fit$fitted_g$sd, verbose = FALSE)
varbvs.lfdr <- varbvs.fit$alpha[, 1]
varbvs.q <- ashr::qval.from.lfdr(varbvs.lfdr)
varbvs.selected <- (1 : p)[varbvs.q <= q]

result[[i]] <- c(
  fdp.BH = sum(beta[BH.selected] == 0) / max(1, length(BH.selected)),
  fdp.ash = sum(beta[ash.selected] == 0) / max(1, length(ash.selected)),
  fdp.knockoff = sum(beta[knockoff.selected] == 0) / max(1, length(knockoff.selected)),
  fdp.knockoff.plus = sum(beta[knockoff.plus.selected] == 0) / max(1, length(knockoff.plus.selected)),
  fdp.knockoff.est = sum(beta[knockoff.selected2] == 0) / max(1, length(knockoff.selected2)),
  fdp.knockoff.plus.est = sum(beta[knockoff.plus.selected2] == 0) / max(1, length(knockoff.plus.selected2)),
  fdp.varbvs = sum(beta[varbvs.selected] == 0) / max(1, length(varbvs.selected)),
  power.BH = sum(beta[BH.selected] != 0) / k,
  power.ash = sum(beta[ash.selected] != 0) / k,
  power.knockoff = sum(beta[knockoff.selected] != 0) / k,
  power.knockoff.plus = sum(beta[knockoff.plus.selected] != 0) / k,
  power.knockoff.est = sum(beta[knockoff.selected2] != 0) / k,
  power.knockoff.plus.est = sum(beta[knockoff.plus.selected2] != 0) / k,
  power.varbvs = sum(beta[varbvs.selected] != 0) / k
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 14, byrow = TRUE)
boxplot(result.summary[, 1 : 7], names = c("BH", "ASH", "Knockoff.G", "Knockoff+.G", "Knockoff.E", "Knockoff+.E", "varbvsmix"), ylab = "FDP", las = 2)
abline(h = q, lty = 2, col = "red")
boxplot(result.summary[, 8 : 14], names = c("BH", "ASH", "Knockoff.G", "Knockoff+.G", "Knockoff.E", "Knockoff+.E", "varbvsmix"), ylab = "TDP", las = 2)
```

## Observation

1. Model-$X$ knockoff is very powerful.
2. Using estimated distribution of $X$ rather than the true distribution hurts the power of Model-$X$ knockoff.
3. The power of Model-$X$ knockoff using estimated distributio of $X$ is on par with that of `ASH` and `BH`, probably because [the presence of small signals makes knockoff less powerful](knockoff_6.html#model-(x)_knockoffs).
4. Sometimes `equi` is better than `SDP` when generating knockoffs, as shown in [previous simulations using factor model for $X$](knockoff_8.html#model-(x)_design15).

## $n < p$

```{r}
n <- 300
p <- 1000
k <- 200
m <- 100
q <- 0.1
```

### Independent design

```{r, echo = FALSE, cache = TRUE, message = FALSE}
A <- 5

Cov.X <- diag(1 / n, p)
result <- list()

for (i in 1 : m) {
  X <- matrix(rnorm(n * p, 0, sqrt(1 / n)), n, p)

  beta <- rep(0, p)
  nonzero <- sample(p, k)
  beta[nonzero] <- rnorm(k, 0, A)
  
  y <- X %*% beta + rnorm(n)

  ## Knockoff
  Xk_g <- knockoff::create.gaussian(X, mu = rep(0, p), Sigma = Cov.X, method = "equi")
  Xk_2 <- knockoff::create.second_order(X, method = "equi")
  gauss_equi <- knockoff::stat.glmnet_coefdiff(X, Xk_g, y, cores = 4)
  est_equi <- knockoff::stat.glmnet_coefdiff(X, Xk_2, y, cores = 4)
  Knockoff.threshold.g <- knockoff::knockoff.threshold(gauss_equi, fdr = q, offset = 0)
  Knockoff.threshold.2 <- knockoff::knockoff.threshold(est_equi, fdr = q, offset = 0)
  Knockoff.threshold.plus.g <- knockoff::knockoff.threshold(gauss_equi, fdr = q, offset = 1)
  Knockoff.threshold.plus.2 <- knockoff::knockoff.threshold(est_equi, fdr = q, offset = 1)
  Knockoff.g.selected <- (1 : p)[gauss_equi >= Knockoff.threshold.g]
  Knockoff.plus.g.selected <- (1 : p)[gauss_equi >= Knockoff.threshold.plus.g]
  Knockoff.2.selected <- (1 : p)[est_equi >= Knockoff.threshold.2]
  Knockoff.plus.2.selected <- (1 : p)[est_equi >= Knockoff.threshold.plus.2]

  ## ASH
  betahat <- c()
  sebetahat <- c()
  for (j in 1 : p) {
    fit <- lm(y ~ X[, j] - 1)
    betahat[j] <- summary(fit)$coefficients[1]
    sebetahat[j] <- summary(fit)$coefficients[2]
  }
  ash.fit <- ashr::ash(betahat, sebetahat, mixcompdist = "normal", method = "fdr")
  ash.selected <- (1 : p)[get_qvalue(ash.fit) <= q]

  ## varbvs
  varbvs.fit <- varbvs::varbvsmix(X, NULL, y, sa = ash.fit$fitted_g$sd, verbose = FALSE)
  varbvs.lfdr <- varbvs.fit$alpha[, 1]
  varbvs.q <- ashr::qval.from.lfdr(varbvs.lfdr)
  varbvs.selected <- (1 : p)[varbvs.q <= q]

result[[i]] <- c(
  fdp.knockoff.g = sum(beta[Knockoff.g.selected] == 0) / max(1, length(Knockoff.g.selected)),
  fdp.knockoff.plus.g = sum(beta[Knockoff.plus.g.selected] == 0) / max(1, length(Knockoff.plus.g.selected)),
  fdp.Knockoff.2 = sum(beta[Knockoff.2.selected] == 0) / max(1, length(Knockoff.2.selected)),
  fdp.knockoff.plus.2 = sum(beta[Knockoff.plus.2.selected] == 0) / max(1, length(Knockoff.plus.2.selected)),
  fdp.ash = sum(beta[ash.selected] == 0) / max(1, length(ash.selected)),
  fdp.varbvs = sum(beta[varbvs.selected] == 0) / max(1, length(varbvs.selected)),
  power.knockoff.g = sum(beta[Knockoff.g.selected] != 0) / k,
  power.knockoff.plus.g = sum(beta[Knockoff.plus.g.selected] != 0) / k,
  power.knockoff.2 = sum(beta[Knockoff.2.selected] != 0) / k,
  power.knockoff.plus.2 = sum(beta[Knockoff.plus.2.selected] != 0) / k,
  power.ash = sum(beta[ash.selected] != 0) / k,
  power.varbvs = sum(beta[varbvs.selected] != 0) / k
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 12, byrow = TRUE)
boxplot(result.summary[, 1 : 6], names = c("Knockoff.G", "Knockoff+.G", "Knockoff.E", "Knockoff+.E", "ASH", "varbvsmix"), ylab = "FDP", las = 2)
abline(h = q, lty = 2, col = "red")
boxplot(result.summary[, 7 : 12], names = c("Knockoff.G", "Knockoff+.G", "Knockoff.E", "Knockoff+.E", "ASH", "varbvsmix"), ylab = "TDP", las = 2)
```

### Local correlation design

```{r, echo = FALSE, cache = TRUE}
rho <- 0.5
Cor.X <- toeplitz(rho^{0 : (p - 1)})
Cor.X.5 <- chol(Cor.X)
Cov.X <- Cor.X / n
```

```{r, echo = FALSE, cache = TRUE, message = FALSE}
A <- 5

result <- list()

for (i in 1 : m) {
beta <- rep(0, p)
nonzero <- sample(p, k)
beta[nonzero] <- rnorm(k, 0, A)

X <- matrix(rnorm(n * p, 0, sqrt(1 / n)), n) %*% Cor.X.5
y <- X %*% beta + rnorm(n)

  ## Knockoff
  Xk_g <- knockoff::create.gaussian(X, mu = rep(0, p), Sigma = Cov.X, method = "equi")
  Xk_2 <- knockoff::create.second_order(X, method = "equi")
  gauss_equi <- knockoff::stat.glmnet_coefdiff(X, Xk_g, y, cores = 4)
  est_equi <- knockoff::stat.glmnet_coefdiff(X, Xk_2, y, cores = 4)
  Knockoff.threshold.g <- knockoff::knockoff.threshold(gauss_equi, fdr = q, offset = 0)
  Knockoff.threshold.2 <- knockoff::knockoff.threshold(est_equi, fdr = q, offset = 0)
  Knockoff.threshold.plus.g <- knockoff::knockoff.threshold(gauss_equi, fdr = q, offset = 1)
  Knockoff.threshold.plus.2 <- knockoff::knockoff.threshold(est_equi, fdr = q, offset = 1)
  Knockoff.g.selected <- (1 : p)[gauss_equi >= Knockoff.threshold.g]
  Knockoff.plus.g.selected <- (1 : p)[gauss_equi >= Knockoff.threshold.plus.g]
  Knockoff.2.selected <- (1 : p)[est_equi >= Knockoff.threshold.2]
  Knockoff.plus.2.selected <- (1 : p)[est_equi >= Knockoff.threshold.plus.2]

  ## ASH
  betahat <- c()
  sebetahat <- c()
  for (j in 1 : p) {
    fit <- lm(y ~ X[, j] - 1)
    betahat[j] <- summary(fit)$coefficients[1]
    sebetahat[j] <- summary(fit)$coefficients[2]
  }
  ash.fit <- ashr::ash(betahat, sebetahat, mixcompdist = "normal", method = "fdr")
  ash.selected <- (1 : p)[get_qvalue(ash.fit) <= q]

  ## varbvs
  varbvs.fit <- varbvs::varbvsmix(X, NULL, y, sa = ash.fit$fitted_g$sd, verbose = FALSE)
  varbvs.lfdr <- varbvs.fit$alpha[, 1]
  varbvs.q <- ashr::qval.from.lfdr(varbvs.lfdr)
  varbvs.selected <- (1 : p)[varbvs.q <= q]

result[[i]] <- c(
  fdp.knockoff.g = sum(beta[Knockoff.g.selected] == 0) / max(1, length(Knockoff.g.selected)),
  fdp.knockoff.plus.g = sum(beta[Knockoff.plus.g.selected] == 0) / max(1, length(Knockoff.plus.g.selected)),
  fdp.Knockoff.2 = sum(beta[Knockoff.2.selected] == 0) / max(1, length(Knockoff.2.selected)),
  fdp.knockoff.plus.2 = sum(beta[Knockoff.plus.2.selected] == 0) / max(1, length(Knockoff.plus.2.selected)),
  fdp.ash = sum(beta[ash.selected] == 0) / max(1, length(ash.selected)),
  fdp.varbvs = sum(beta[varbvs.selected] == 0) / max(1, length(varbvs.selected)),
  power.knockoff.g = sum(beta[Knockoff.g.selected] != 0) / k,
  power.knockoff.plus.g = sum(beta[Knockoff.plus.g.selected] != 0) / k,
  power.knockoff.2 = sum(beta[Knockoff.2.selected] != 0) / k,
  power.knockoff.plus.2 = sum(beta[Knockoff.plus.2.selected] != 0) / k,
  power.ash = sum(beta[ash.selected] != 0) / k,
  power.varbvs = sum(beta[varbvs.selected] != 0) / k
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 12, byrow = TRUE)
boxplot(result.summary[, 1 : 6], names = c("Knockoff.G", "Knockoff+.G", "Knockoff.E", "Knockoff+.E", "ASH", "varbvsmix"), ylab = "FDP", las = 2)
abline(h = q, lty = 2, col = "red")
boxplot(result.summary[, 7 : 12], names = c("Knockoff.G", "Knockoff+.G", "Knockoff.E", "Knockoff+.E", "ASH", "varbvsmix"), ylab = "TDP", las = 2)
```

### Factor Model for $X$

```{r, echo = FALSE, cache = TRUE}
d <- 5
B <- matrix(rnorm(p * d), p, d)
Cor.X <- cov2cor(tcrossprod(B) + diag(p))
Cor.X.5 <- chol(Cor.X)
Cov.X <- Cor.X / n
```

```{r, echo = FALSE, cache = TRUE, message = FALSE}
A <- 7

result <- list()

for (i in 1 : m) {
beta <- rep(0, p)
nonzero <- sample(p, k)
beta[nonzero] <- rnorm(k, 0, A)

X <- matrix(rnorm(n * p, 0, sqrt(1 / n)), n) %*% Cor.X.5
y <- X %*% beta + rnorm(n)

  ## Knockoff
  Xk_g <- knockoff::create.gaussian(X, mu = rep(0, p), Sigma = Cov.X, method = "equi")
  Xk_2 <- knockoff::create.second_order(X, method = "equi")
  gauss_equi <- knockoff::stat.glmnet_coefdiff(X, Xk_g, y, cores = 4)
  est_equi <- knockoff::stat.glmnet_coefdiff(X, Xk_2, y, cores = 4)
  Knockoff.threshold.g <- knockoff::knockoff.threshold(gauss_equi, fdr = q, offset = 0)
  Knockoff.threshold.2 <- knockoff::knockoff.threshold(est_equi, fdr = q, offset = 0)
  Knockoff.threshold.plus.g <- knockoff::knockoff.threshold(gauss_equi, fdr = q, offset = 1)
  Knockoff.threshold.plus.2 <- knockoff::knockoff.threshold(est_equi, fdr = q, offset = 1)
  Knockoff.g.selected <- (1 : p)[gauss_equi >= Knockoff.threshold.g]
  Knockoff.plus.g.selected <- (1 : p)[gauss_equi >= Knockoff.threshold.plus.g]
  Knockoff.2.selected <- (1 : p)[est_equi >= Knockoff.threshold.2]
  Knockoff.plus.2.selected <- (1 : p)[est_equi >= Knockoff.threshold.plus.2]

  ## ASH
  betahat <- c()
  sebetahat <- c()
  for (j in 1 : p) {
    fit <- lm(y ~ X[, j] - 1)
    betahat[j] <- summary(fit)$coefficients[1]
    sebetahat[j] <- summary(fit)$coefficients[2]
  }
  ash.fit <- ashr::ash(betahat, sebetahat, mixcompdist = "normal", method = "fdr")
  ash.selected <- (1 : p)[get_qvalue(ash.fit) <= q]

  ## varbvs
  varbvs.fit <- varbvs::varbvsmix(X, NULL, y, sa = ash.fit$fitted_g$sd, verbose = FALSE)
  varbvs.lfdr <- varbvs.fit$alpha[, 1]
  varbvs.q <- ashr::qval.from.lfdr(varbvs.lfdr)
  varbvs.selected <- (1 : p)[varbvs.q <= q]

result[[i]] <- c(
  fdp.knockoff.g = sum(beta[Knockoff.g.selected] == 0) / max(1, length(Knockoff.g.selected)),
  fdp.knockoff.plus.g = sum(beta[Knockoff.plus.g.selected] == 0) / max(1, length(Knockoff.plus.g.selected)),
  fdp.Knockoff.2 = sum(beta[Knockoff.2.selected] == 0) / max(1, length(Knockoff.2.selected)),
  fdp.knockoff.plus.2 = sum(beta[Knockoff.plus.2.selected] == 0) / max(1, length(Knockoff.plus.2.selected)),
  fdp.ash = sum(beta[ash.selected] == 0) / max(1, length(ash.selected)),
  fdp.varbvs = sum(beta[varbvs.selected] == 0) / max(1, length(varbvs.selected)),
  power.knockoff.g = sum(beta[Knockoff.g.selected] != 0) / k,
  power.knockoff.plus.g = sum(beta[Knockoff.plus.g.selected] != 0) / k,
  power.knockoff.2 = sum(beta[Knockoff.2.selected] != 0) / k,
  power.knockoff.plus.2 = sum(beta[Knockoff.plus.2.selected] != 0) / k,
  power.ash = sum(beta[ash.selected] != 0) / k,
  power.varbvs = sum(beta[varbvs.selected] != 0) / k
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 12, byrow = TRUE)
boxplot(result.summary[, 1 : 6], names = c("Knockoff.G", "Knockoff+.G", "Knockoff.E", "Knockoff+.E", "ASH", "varbvsmix"), ylab = "FDP", las = 2)
abline(h = q, lty = 2, col = "red")
boxplot(result.summary[, 7 : 12], names = c("Knockoff.G", "Knockoff+.G", "Knockoff.E", "Knockoff+.E", "ASH", "varbvsmix"), ylab = "TDP", las = 2)
```

### Factor Model for $\hat\beta$

```{r, echo = FALSE, cache = TRUE}
d <- 5
B <- matrix(rnorm(p * d), p, d)
Cor.X <- signif(cov2cor(solve(tcrossprod(B) + diag(p))), digits = 6)
Cor.X.5 <- chol(Cor.X)
Cov.X <- Cor.X / n
```

```{r, echo = FALSE, cache = TRUE, message = FALSE}
A <- 7

result <- list()

for (i in 1 : m) {
beta <- rep(0, p)
nonzero <- sample(p, k)
beta[nonzero] <- A

X <- matrix(rnorm(n * p, 0, sqrt(1 / n)), n) %*% Cor.X.5
y <- X %*% beta + rnorm(n)

  ## Knockoff
  Xk_g <- knockoff::create.gaussian(X, mu = rep(0, p), Sigma = Cov.X, method = "equi")
  Xk_2 <- knockoff::create.second_order(X, method = "equi")
  gauss_equi <- knockoff::stat.glmnet_coefdiff(X, Xk_g, y, cores = 4)
  est_equi <- knockoff::stat.glmnet_coefdiff(X, Xk_2, y, cores = 4)
  Knockoff.threshold.g <- knockoff::knockoff.threshold(gauss_equi, fdr = q, offset = 0)
  Knockoff.threshold.2 <- knockoff::knockoff.threshold(est_equi, fdr = q, offset = 0)
  Knockoff.threshold.plus.g <- knockoff::knockoff.threshold(gauss_equi, fdr = q, offset = 1)
  Knockoff.threshold.plus.2 <- knockoff::knockoff.threshold(est_equi, fdr = q, offset = 1)
  Knockoff.g.selected <- (1 : p)[gauss_equi >= Knockoff.threshold.g]
  Knockoff.plus.g.selected <- (1 : p)[gauss_equi >= Knockoff.threshold.plus.g]
  Knockoff.2.selected <- (1 : p)[est_equi >= Knockoff.threshold.2]
  Knockoff.plus.2.selected <- (1 : p)[est_equi >= Knockoff.threshold.plus.2]

  ## ASH
  betahat <- c()
  sebetahat <- c()
  for (j in 1 : p) {
    fit <- lm(y ~ X[, j] - 1)
    betahat[j] <- summary(fit)$coefficients[1]
    sebetahat[j] <- summary(fit)$coefficients[2]
  }
  ash.fit <- ashr::ash(betahat, sebetahat, mixcompdist = "normal", method = "fdr")
  ash.selected <- (1 : p)[get_qvalue(ash.fit) <= q]

  ## varbvs
  varbvs.fit <- varbvs::varbvsmix(X, NULL, y, sa = ash.fit$fitted_g$sd, verbose = FALSE)
  varbvs.lfdr <- varbvs.fit$alpha[, 1]
  varbvs.q <- ashr::qval.from.lfdr(varbvs.lfdr)
  varbvs.selected <- (1 : p)[varbvs.q <= q]

result[[i]] <- c(
  fdp.knockoff.g = sum(beta[Knockoff.g.selected] == 0) / max(1, length(Knockoff.g.selected)),
  fdp.knockoff.plus.g = sum(beta[Knockoff.plus.g.selected] == 0) / max(1, length(Knockoff.plus.g.selected)),
  fdp.Knockoff.2 = sum(beta[Knockoff.2.selected] == 0) / max(1, length(Knockoff.2.selected)),
  fdp.knockoff.plus.2 = sum(beta[Knockoff.plus.2.selected] == 0) / max(1, length(Knockoff.plus.2.selected)),
  fdp.ash = sum(beta[ash.selected] == 0) / max(1, length(ash.selected)),
  fdp.varbvs = sum(beta[varbvs.selected] == 0) / max(1, length(varbvs.selected)),
  power.knockoff.g = sum(beta[Knockoff.g.selected] != 0) / k,
  power.knockoff.plus.g = sum(beta[Knockoff.plus.g.selected] != 0) / k,
  power.knockoff.2 = sum(beta[Knockoff.2.selected] != 0) / k,
  power.knockoff.plus.2 = sum(beta[Knockoff.plus.2.selected] != 0) / k,
  power.ash = sum(beta[ash.selected] != 0) / k,
  power.varbvs = sum(beta[varbvs.selected] != 0) / k
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 12, byrow = TRUE)
boxplot(result.summary[, 1 : 6], names = c("Knockoff.G", "Knockoff+.G", "Knockoff.E", "Knockoff+.E", "ASH", "varbvsmix"), ylab = "FDP", las = 2)
abline(h = q, lty = 2, col = "red")
boxplot(result.summary[, 7 : 12], names = c("Knockoff.G", "Knockoff+.G", "Knockoff.E", "Knockoff+.E", "ASH", "varbvsmix"), ylab = "TDP", las = 2)
```

## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
