---
title: "Variability of `Knockoff`'s FDR Control"
author: "Lei Sun"
date: 2018-04-03
output: workflowr::wflow_html
---





## Introduction

We hypothesize that `Knockoff` might have a potential problem: the variability of the actual FDP could be large, although the mean of FDP is theoretically and empirically controlled at FDR.

The reason is that `Knockoff` relies on the **flip sign property** of the test statistics $W_j$ for all null variables. Actually the events $\{W_j \geq t_j\}$ or $\{W_j \leq -t_j\}$ are independent for all null variables. However, they are **not identically distributed**.

Therefore, if every null variable is "unique," in the sense that its test statistic has a distinct distribution, for example, if it tends to be larger or in a different region than anyone else, then this test statistic could randomly be positive or negative, and affect the estimate of FDP for different random samples.

In common high-dimensional settings it's usually not a big problem since in those simulations no null variables are unique, meaning that we would expect to see $W_i$ and $W_j$ showing up in regions symmetric at zero.

```{r, echo = FALSE, message = FALSE, warning = FALSE}
library(knockoff)
library(Matrix)
library(tidyverse)
library(ggplot2)
```

## A simple illustration

$X$ is $30 \times 4$, $X_1$ and $X_3$ are "true" variables, and $X_2$ and $X_4$ are nulls. $X_2$ is highly correlated with $X_1$, $\rho = 0.99$, whereas $X_4$ is almost uncorrelated with $X_3$, $\rho = 0.01$.

```{r, echo = FALSE, cache = TRUE}
n <- 30
p <- 4
Sigma <- matrix(c(1, 0.99, 0, 0, 0.99, 1, 0, 0, 0, 0, 1, 0.01, 0, 0, 0.01, 1), byrow = TRUE, 4, 4)
beta <- c(5, 0, 5, 0) / sqrt(n)

W <- list()

for (i in 1 : 1000) {
  X1 <- rnorm(n)
  X2 <- 0.99 * X1 + sqrt(1 - 0.99^2) * rnorm(n)
  X3 <- rnorm(n)
  X4 <- 0.01 * X3 + sqrt(1 - 0.01^2) * rnorm(n)
  X <- cbind(X1, X2, X3, X4)
  Xk <- knockoff::create.gaussian(X, mu = rep(0, 4), Sigma = Sigma, method = "sdp")
  y <- X %*% beta + rnorm(n)
  W[[i]] <- knockoff::stat.glmnet_coefdiff(X, Xk, y)
}
```

Below is a plot of $W_2$ vs $W_4$. As we can see, $|W_2|$ is usually much greater than $|W_4|$, and in many samples, only $W_2$ will show up in the rejection region $W \geq t$ or its symmetric null estimation region $W \le -t$, which brings variability of $\hat{FDP}$ as the null statistic $W_2$ shows up in one region or the other.

```{r, simple_var, echo = FALSE, cache = TRUE}
W <- matrix(unlist(W), byrow = TRUE, 1000)
Wlim <- max(abs(W[, c(2, 4)]))
plot(W[, 2], W[, 4], xlim = c(-Wlim, Wlim), ylim = c(-Wlim, Wlim),
     xlab = expression(W[2]),
     ylab = expression(W[4]))
abline(0, 1, lty = 2, col = "blue")
abline(0, -1, lty = 2, col = "blue")
```

## Example

$X$ is $n \times 20$. There are $10$ "true" variables: $X_1, X_3, X_5, \ldots, X_{17}, X_{19}$ and $10$ null variables: $X_2, X_4, X_6, \ldots, X_{18}, X_{20}$. The correlation between the true and null variables are decreasing such that $\rho(X_1, X_2) = 0.9, \rho(X_3, X_4) = 0.8, \rho(X_5, X_6) = 0.7, \ldots, \rho(X_{17}, X_{18}) = 0.2, \rho(X_{19}, X_{20}) = 0.1$, and all other pairwise correlations are zero.

```{r, echo = FALSE, cache = TRUE}
Sigma <- bdiag(
  matrix(c(1, 0.9, 0.9, 1), 2, 2),
  matrix(c(1, 0.8, 0.8, 1), 2, 2),
  matrix(c(1, 0.7, 0.7, 1), 2, 2),
  matrix(c(1, 0.6, 0.6, 1), 2, 2),
  matrix(c(1, 0.5, 0.5, 1), 2, 2),
  matrix(c(1, 0.4, 0.4, 1), 2, 2),
  matrix(c(1, 0.3, 0.3, 1), 2, 2),
  matrix(c(1, 0.2, 0.2, 1), 2, 2),
  matrix(c(1, 0.1, 0.1, 1), 2, 2),
  matrix(c(1, 0.0, 0.0, 1), 2, 2)
)
Sigma <- as.matrix(Sigma)
Cov.X <- Sigma / n
rho.X <- 9 : 0 / 10
k <- 10
q <- 0.2
beta <- rep(c(5, 0), 10)
```

### $n = 30$

The variability in FDP given by `Knockoff` is obvious.

```{r var30, echo = FALSE, cache = TRUE}
n <- 30
m <- 1000
result <- selected <- W.list <- list()
for (i in 1 : m) {
X <- matrix(0, n, 20)
X[, seq(1, 20, by = 2)] <- matrix(rnorm(n * 10, 0, sqrt(1 / n)), n, 10)
for (j in seq(2, 20, by = 2)) {
  X[, j] <- rho.X[j / 2] * X[, j - 1] + sqrt(1 - rho.X[j / 2]^2) * rnorm(n, 0, sqrt(1 / n))
}

y <- X %*% beta + rnorm(n)

## Least squares
lm.fit <- lm(y ~ X - 1)
pvalue <- summary(lm.fit)$coefficients[, 4]
betahat <- summary(lm.fit)$coefficients[, 1]
sebetahat <- summary(lm.fit)$coefficients[, 2]

## BH
BH.fit <- p.adjust(pvalue, method = "BH")
BH.selected <- (1 : 20)[BH.fit <= q]

## Knockoff
Xk <- knockoff::create.gaussian(X, mu = rep(0, p), Sigma = Cov.X, method = "sdp")
W <- knockoff::stat.glmnet_coefdiff(X, Xk, y, cores = 4)
thres.knockoff = knockoff::knockoff.threshold(W, fdr = q, offset = 0) # less conservative
thres.knockoff.plus = knockoff::knockoff.threshold(W, fdr = q, offset = 1) # more conservative
knockoff.selected <- which(W >= thres.knockoff)
knockoff.plus.selected <- which(W >= thres.knockoff.plus)

W.list[[i]] <- W

result[[i]] <- c(
  fdp.BH = sum(beta[BH.selected] == 0) / max(1, length(BH.selected)),
  fdp.knockoff = sum(beta[knockoff.selected] == 0) / max(1, length(knockoff.selected)),
  fdp.knockoff.plus = sum(beta[knockoff.plus.selected] == 0) / max(1, length(knockoff.plus.selected)),
  power.BH = sum(beta[BH.selected] != 0) / max(sum(beta != 0), 1),
  power.knockoff = sum(beta[knockoff.selected] != 0) / max(sum(beta != 0), 1),
  power.knockoff.plus = sum(beta[knockoff.plus.selected] != 0) / max(sum(beta != 0), 1)
)

selected[[i]] <- list(
  BH.selected <- BH.selected,
  knockoff.selected <- knockoff.selected,
  knockoff.plus.selected <- knockoff.plus.selected
)
}
```

```{r, echo = FALSE}
mean_sdp <- function(x) {
   m <- mean(x)
   ymax <- m + sd(x)
   return(c(y = m, ymax = ymax, ymin = m))
}

result.summary <- matrix(unlist(result), m, 6, byrow = TRUE)

boxplot(result.summary[, 1 : 3], names = c("BH", "Knockoff", "Knockoff+"), ylab = "FDP")
stripchart(as.vector(result.summary[, 1 : 3]) ~ factor(rep(1 : 3, each = m)), vertical = TRUE, method = "jitter", add = TRUE, pch = 20, col = 'blue')
abline(h = q, lty = 2, col = "red")

FDP <- as.vector((result.summary[, 1 : 3]))
Method <- rep(c("BH", "Knockoff", "Knockoff+"), each = m)
FDP <- cbind.data.frame(FDP, Method)
ggplot(data = FDP,
        aes(x = Method, y = FDP, col = Method)) +
  geom_violin(trim = TRUE) +
  geom_hline(yintercept = q, linetype = "dashed") +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  labs(y = "FDP", x = "") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10), axis.title.y = element_text(size = 15), axis.text.x = element_text(size = 15), axis.text.y = element_text(size = 10))

boxplot(result.summary[, 4 : 6], names = c("BH", "Knockoff", "Knockoff+"), ylab = "TDP")
stripchart(as.vector(result.summary[, 4 : 6]) ~ factor(rep(4 : 6, each = m)), vertical = TRUE, method = "jitter", add = TRUE, pch = 20, col = 'blue')

TDP <- as.vector((result.summary[, 4 : 6]))
TDP <- cbind.data.frame(TDP, Method)
ggplot(data = TDP,
        aes(x = Method, y = TDP, col = Method)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  labs(y = "TDP", x = "") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10), axis.title.y = element_text(size = 15), axis.text.x = element_text(size = 15), axis.text.y = element_text(size = 10))
```

### $n = 10K$

The variability in FDP given by `Knockoff` is less than when $n = 30$, but still bigger than that given by `BH`.

```{r var10000, echo = FALSE, cache = TRUE}
n <- 1e4
m <- 1000
result <- selected <- W.list <- list()
for (i in 1 : m) {
X <- matrix(0, n, 20)
X[, seq(1, 20, by = 2)] <- matrix(rnorm(n * 10, 0, sqrt(1 / n)), n, 10)
for (j in seq(2, 20, by = 2)) {
  X[, j] <- rho.X[j / 2] * X[, j - 1] + sqrt(1 - rho.X[j / 2]^2) * rnorm(n, 0, sqrt(1 / n))
}

y <- X %*% beta + rnorm(n)

## Least squares
lm.fit <- lm(y ~ X - 1)
pvalue <- summary(lm.fit)$coefficients[, 4]
betahat <- summary(lm.fit)$coefficients[, 1]
sebetahat <- summary(lm.fit)$coefficients[, 2]

## BH
BH.fit <- p.adjust(pvalue, method = "BH")
BH.selected <- (1 : 20)[BH.fit <= q]

## Knockoff
Xk <- knockoff::create.gaussian(X, mu = rep(0, p), Sigma = Cov.X, method = "sdp")
W <- knockoff::stat.glmnet_coefdiff(X, Xk, y, cores = 4)
thres.knockoff = knockoff::knockoff.threshold(W, fdr = q, offset = 0) # less conservative
thres.knockoff.plus = knockoff::knockoff.threshold(W, fdr = q, offset = 1) # more conservative
knockoff.selected <- which(W >= thres.knockoff)
knockoff.plus.selected <- which(W >= thres.knockoff.plus)

W.list[[i]] <- W

result[[i]] <- c(
  fdp.BH = sum(beta[BH.selected] == 0) / max(1, length(BH.selected)),
  fdp.knockoff = sum(beta[knockoff.selected] == 0) / max(1, length(knockoff.selected)),
  fdp.knockoff.plus = sum(beta[knockoff.plus.selected] == 0) / max(1, length(knockoff.plus.selected)),
  power.BH = sum(beta[BH.selected] != 0) / max(sum(beta != 0), 1),
  power.knockoff = sum(beta[knockoff.selected] != 0) / max(sum(beta != 0), 1),
  power.knockoff.plus = sum(beta[knockoff.plus.selected] != 0) / max(sum(beta != 0), 1)
)

selected[[i]] <- list(
  BH.selected <- BH.selected,
  knockoff.selected <- knockoff.selected,
  knockoff.plus.selected <- knockoff.plus.selected
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 6, byrow = TRUE)

boxplot(result.summary[, 1 : 3], names = c("BH", "Knockoff", "Knockoff+"), ylab = "FDP")
stripchart(as.vector(result.summary[, 1 : 3]) ~ factor(rep(1 : 3, each = m)), vertical = TRUE, method = "jitter", add = TRUE, pch = 20, col = 'blue')
abline(h = q, lty = 2, col = "red")

FDP <- as.vector((result.summary[, 1 : 3]))
Method <- rep(c("BH", "Knockoff", "Knockoff+"), each = m)
FDP <- cbind.data.frame(FDP, Method)
ggplot(data = FDP,
        aes(x = Method, y = FDP, col = Method)) +
  geom_violin(trim = TRUE) +
  geom_hline(yintercept = q, linetype = "dashed") +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  labs(y = "FDP", x = "") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10), axis.title.y = element_text(size = 15), axis.text.x = element_text(size = 15), axis.text.y = element_text(size = 10))

boxplot(result.summary[, 4 : 6], names = c("BH", "Knockoff", "Knockoff+"), ylab = "TDP")
stripchart(as.vector(result.summary[, 4 : 6]) ~ factor(rep(4 : 6, each = m)), vertical = TRUE, method = "jitter", add = TRUE, pch = 20, col = 'blue')

TDP <- as.vector((result.summary[, 4 : 6]))
TDP <- cbind.data.frame(TDP, Method)
ggplot(data = TDP,
        aes(x = Method, y = TDP, col = Method)) +
  geom_violin(trim = TRUE) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  labs(y = "TDP", x = "") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10), axis.title.y = element_text(size = 15), axis.text.x = element_text(size = 15), axis.text.y = element_text(size = 10))
```


