---
title: "`Knockoff` on Small Signals"
author: "Lei Sun"
date: 2018-02-05
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

## Introduction

In the `Knockoff` paper simulations, $\beta$'s are either $0$ or $A$. Here we are replicating the results, and investigating how well `Knockoff` deal with small signals.

In the following simulations, we always have $n = 3000$, $p = 1000$, For a certain $\beta$, $Y_n \sim N(X_{n\times p}\beta_p, I_n)$. Out of $p = 1000$ $\beta_j$'s, here are three scenarios.

- Scenario 1: $950$ are 0, and the rest $50$ are $A = 3.5$. (replicating a data point on Fig 3 of the `Knockoff` paper)
- Scenario 2: $850$ are 0, $50$ are $A = 3.5$ as large signals, and the rest $100$ are small signals uniformly from $0$ to $3.5$.
- Scenario 3: $750$ are 0, $50$ are $A = 3.5$ as large signals, and the rest $200$ are small signals uniformly from $0$ to $3.5$.

```{r, echo = FALSE, cache = TRUE}
library(knockoff)
library(ggplot2)
fdp <- function(selected) sum(beta[selected] == 0) / max(length(selected), 1)
power <- function(selected, k = k) sum(beta[selected] != 0) / max(k, 1)
mean_sdp <- function(x) {
   m <- mean(x)
   ymax <- m + sd(x)
   return(c(y = m, ymax = ymax, ymin = m))
}
method.name <- c("BH", "Knockoff", "Knockoff+")
method.col <- c("blue", "red", "maroon")
set.seed(777)
```

```{r}
n <- 3000
p <- 1000
k <- 50
q <- 0.1
A <- 3.5
```

### Scenario 1: 50 large signals, no small signals, 950 zeroes.

```{r, cache = TRUE}
X <- matrix(rnorm(n * p), n , p)
X <- svd(X)$u
Xk <- knockoff::create.fixed(X)
Xk <- Xk$Xk
```

```{r, echo = FALSE, cache = TRUE}
beta <- rep(0, p)
large <- sample(p, k)
beta[large] <- A
```

```{r, echo = FALSE, fig.asp = 0.4, fig.height = 5}
par(mfrow = c(1, 2))
hist(beta, xlab = expression(beta), main = expression(paste("Histogram of ", beta)))
hist(beta[beta != 0], xlab = expression(beta), main = expression(paste("Histogram of non-zero ", beta)), breaks = seq(0, 3.5, by = 0.5))
```

```{r, echo = FALSE, cache = TRUE}
m <- 1000
result <- list()
for (i in 1 : m) {
y <- X %*% beta + rnorm(n)

## Least squares
lm.fit <- lm(y ~ X - 1)
pvalue <- summary(lm.fit)$coefficients[, 4]

## BH
BH.fit <- p.adjust(pvalue, method = "BH")
BH.selected <- (1 : p)[BH.fit <= q]

## Knockoff
W = stat.glmnet_lambdasmax(X, Xk, y)
thres.knockoff = knockoff.threshold(W, fdr = q, offset = 0) # less conservative
thres.knockoff.plus = knockoff.threshold(W, fdr = q, offset = 1) # more conservative
knockoff.selected <- which(W >= thres.knockoff)
knockoff.plus.selected <- which(W >= thres.knockoff.plus)

result[[i]] <- c(
  fdp.BH = fdp(BH.selected),
  fdp.knockoff = fdp(knockoff.selected),
  fdp.knockoff.plus = fdp(knockoff.plus.selected),
  power.BH = power(BH.selected, sum(beta != 0)),
  power.knockoff = power(knockoff.selected, sum(beta != 0)),
  power.knockoff.plus = power(knockoff.plus.selected, sum(beta != 0))
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 6, byrow = TRUE)
colnames(result.summary) <- c("fdp.BH", "fdp.Knockoff", "fdp.Knockoff.plus", "power.BH", "power.Knockoff", "power.Knockoff.plus")
result.nosmall <- result.summary
```

### Scenario 2: 50 large signals, 100 small signals, 850 zeroes.

```{r, cache = TRUE}
X <- matrix(rnorm(n * p), n , p)
X <- svd(X)$u
Xk <- knockoff::create.fixed(X)
Xk <- Xk$Xk
```

```{r, echo = FALSE}
k.small <- 100
beta <- rep(0, p)
large <- sample(p, k)
small <- sample(setdiff(seq(p), large), k.small)
beta[large] <- A
beta[small] <- seq(0, 3, length = k.small + 1)[-1]
```

```{r, echo = FALSE, fig.asp = 0.4, fig.height = 5}
par(mfrow = c(1, 2))
hist(beta, xlab = expression(beta), main = expression(paste("Histogram of ", beta)))
hist(beta[beta != 0], xlab = expression(beta), main = expression(paste("Histogram of non-zero ", beta)), breaks = seq(0, 3.5, by = 0.5))
```

```{r, echo = FALSE, cache = TRUE}
m <- 1000
result <- list()
for (i in 1 : m) {
y <- X %*% beta + rnorm(n)

## Least squares
lm.fit <- lm(y ~ X - 1)
pvalue <- summary(lm.fit)$coefficients[, 4]

## BH
BH.fit <- p.adjust(pvalue, method = "BH")
BH.selected <- (1 : p)[BH.fit <= q]

## Knockoff
W = stat.glmnet_lambdasmax(X, Xk, y)
thres.knockoff = knockoff.threshold(W, fdr = q, offset = 0) # less conservative
thres.knockoff.plus = knockoff.threshold(W, fdr = q, offset = 1) # more conservative
knockoff.selected <- which(W >= thres.knockoff)
knockoff.plus.selected <- which(W >= thres.knockoff.plus)

result[[i]] <- c(
  fdp.BH = fdp(BH.selected),
  fdp.knockoff = fdp(knockoff.selected),
  fdp.knockoff.plus = fdp(knockoff.plus.selected),
  power.BH = power(BH.selected, sum(beta != 0)),
  power.knockoff = power(knockoff.selected, sum(beta != 0)),
  power.knockoff.plus = power(knockoff.plus.selected, sum(beta != 0)),
  power.large.BH <- length(intersect(BH.selected, large)) / length(large),
  power.large.knockoff <- length(intersect(knockoff.selected, large)) / length(large),
  power.large.knockoff.plus <- length(intersect(knockoff.plus.selected, large)) / length(large),
  power.small.BH <- length(intersect(BH.selected, small)) / length(small),
  power.small.knockoff <- length(intersect(knockoff.selected, small)) / length(small),
  power.small.knockoff.plus <- length(intersect(knockoff.plus.selected, small)) / length(small)
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 12, byrow = TRUE)
colnames(result.summary) <- c("fdp.BH", "fdp.Knockoff", "fdp.Knockoff.plus", "power.BH", "power.Knockoff", "power.Knockoff.plus", "power.large.BH", "power.large.Knockoff", "power.large.Knockoff.plus", "power.small.BH", "power.small.Knockoff", "power.small.Knockoff.plus")
result.fewsmall <- result.summary
```

### Scenario 3: 50 large signals, 200 small signals, 750 zeroes.

```{r, cache = TRUE}
X <- matrix(rnorm(n * p), n , p)
X <- svd(X)$u
Xk <- knockoff::create.fixed(X)
Xk <- Xk$Xk
```

```{r, echo = FALSE}
k.small <- 200
beta <- rep(0, p)
large <- sample(p, k)
small <- sample(setdiff(seq(p), large), k.small)
beta[large] <- A
beta[small] <- seq(0, 3, length = k.small + 1)[-1]
```

```{r, echo = FALSE, fig.asp = 0.4, fig.height = 5}
par(mfrow = c(1, 2))
hist(beta, xlab = expression(beta), main = expression(paste("Histogram of ", beta)))
hist(beta[beta != 0], xlab = expression(beta), main = expression(paste("Histogram of non-zero ", beta)), breaks = seq(0, 3.5, by = 0.5))
```

```{r, echo = FALSE, cache = TRUE}
m <- 1000
result <- list()
for (i in 1 : m) {
y <- X %*% beta + rnorm(n)

## Least squares
lm.fit <- lm(y ~ X - 1)
pvalue <- summary(lm.fit)$coefficients[, 4]

## BH
BH.fit <- p.adjust(pvalue, method = "BH")
BH.selected <- (1 : p)[BH.fit <= q]

## Knockoff
W = stat.glmnet_lambdasmax(X, Xk, y)
thres.knockoff = knockoff.threshold(W, fdr = q, offset = 0) # less conservative
thres.knockoff.plus = knockoff.threshold(W, fdr = q, offset = 1) # more conservative
knockoff.selected <- which(W >= thres.knockoff)
knockoff.plus.selected <- which(W >= thres.knockoff.plus)

result[[i]] <- c(
  fdp.BH = fdp(BH.selected),
  fdp.knockoff = fdp(knockoff.selected),
  fdp.knockoff.plus = fdp(knockoff.plus.selected),
  power.BH = power(BH.selected, sum(beta != 0)),
  power.knockoff = power(knockoff.selected, sum(beta != 0)),
  power.knockoff.plus = power(knockoff.plus.selected, sum(beta != 0)),
  power.large.BH <- length(intersect(BH.selected, large)) / length(large),
  power.large.knockoff <- length(intersect(knockoff.selected, large)) / length(large),
  power.large.knockoff.plus <- length(intersect(knockoff.plus.selected, large)) / length(large),
  power.small.BH <- length(intersect(BH.selected, small)) / length(small),
  power.small.knockoff <- length(intersect(knockoff.selected, small)) / length(small),
  power.small.knockoff.plus <- length(intersect(knockoff.plus.selected, small)) / length(small)
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 12, byrow = TRUE)
colnames(result.summary) <- c("fdp.BH", "fdp.Knockoff", "fdp.Knockoff.plus", "power.BH", "power.Knockoff", "power.Knockoff.plus", "power.large.BH", "power.large.Knockoff", "power.large.Knockoff.plus", "power.small.BH", "power.small.Knockoff", "power.small.Knockoff.plus")
result.manysmall <- result.summary
```

## Orthogonal design

$X$ has random orthonormal columns

```{r, echo = FALSE}
summary <- rbind.data.frame(colMeans(result.nosmall), colMeans(result.fewsmall), colMeans(result.manysmall))
colnames(summary) <- c("FDP.BH", "FDP.Knockoff", "FDP.Knockoff.Plus", "Power.BH", "Power.Knockoff", "Power.Knockoff.Plus", "Power.Large.BH", "Power.Large.Knockoff", "Power.Large.Knockoff.Plus", "Power.Small.BH", "Power.Small.Knockoff", "Power.Small.Knockoff.Plus")
summary[1, 7 : 9] <- summary[1, 4 : 6]
summary[1, 10 : 12] <- NA
library(knitr)
kable(summary, digits = 4)
```

```{r, echo = FALSE}
FDP.summary <- rbind.data.frame(
   cbind.data.frame(FDP = result.nosmall[, 1], Method = rep("BH", length(result.nosmall[, 1])), Scenario = rep("No Small Signals", length(result.nosmall[, 1]))),
   cbind.data.frame(FDP = result.nosmall[, 2], Method = rep("Knockoff", length(result.nosmall[, 2])), Scenario = rep("No Small Signals", length(result.nosmall[, 2]))),
   cbind.data.frame(FDP = result.nosmall[, 3], Method = rep("Knockoff+", length(result.nosmall[, 3])), Scenario = rep("No Small Signals", length(result.nosmall[, 3]))),
   cbind.data.frame(FDP = result.fewsmall[, 1], Method = rep("BH", length(result.fewsmall[, 1])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 1]))),
   cbind.data.frame(FDP = result.fewsmall[, 2], Method = rep("Knockoff", length(result.fewsmall[, 2])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 2]))),
   cbind.data.frame(FDP = result.fewsmall[, 3], Method = rep("Knockoff+", length(result.fewsmall[, 3])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 3]))),
   cbind.data.frame(FDP = result.manysmall[, 1], Method = rep("BH", length(result.manysmall[, 1])), Scenario = rep("More Small Signals", length(result.manysmall[, 1]))),
   cbind.data.frame(FDP = result.manysmall[, 2], Method = rep("Knockoff", length(result.manysmall[, 2])), Scenario = rep("More Small Signals", length(result.manysmall[, 2]))),
   cbind.data.frame(FDP = result.manysmall[, 3], Method = rep("Knockoff+", length(result.manysmall[, 3])), Scenario = rep("More Small Signals", length(result.manysmall[, 3])))
 )

ggplot(data = FDP.summary,
        aes(x = Method, y = FDP, col = Method)) +
  geom_violin(trim = TRUE) +
  facet_wrap(~Scenario) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  geom_hline(yintercept = q, col = "maroon", linetype = "dashed", size = 1) +
  labs(title = bquote(paste("False Discovery Proportions at ", FDR == .(q), " Cutoff")), x = "", y = "FDP") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10), axis.title.y = element_text(size = 10), axis.text.x = element_text(size = 10), axis.text.y = element_text(size = 10))
```

```{r, echo = FALSE}
Power.summary <- rbind.data.frame(
   cbind.data.frame(Power = result.nosmall[, 4], Method = rep("BH", length(result.nosmall[, 4])), Scenario = rep("No Small Signals", length(result.nosmall[, 4]))),
   cbind.data.frame(Power = result.nosmall[, 5], Method = rep("Knockoff", length(result.nosmall[, 5])), Scenario = rep("No Small Signals", length(result.nosmall[, 5]))),
   cbind.data.frame(Power = result.nosmall[, 6], Method = rep("Knockoff+", length(result.nosmall[, 6])), Scenario = rep("No Small Signals", length(result.nosmall[, 6]))),
   cbind.data.frame(Power = result.fewsmall[, 4], Method = rep("BH", length(result.fewsmall[, 4])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 4]))),
   cbind.data.frame(Power = result.fewsmall[, 5], Method = rep("Knockoff", length(result.fewsmall[, 5])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 5]))),
   cbind.data.frame(Power = result.fewsmall[, 6], Method = rep("Knockoff+", length(result.fewsmall[, 6])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 6]))),
   cbind.data.frame(Power = result.manysmall[, 4], Method = rep("BH", length(result.manysmall[, 4])), Scenario = rep("More Small Signals", length(result.manysmall[, 4]))),
   cbind.data.frame(Power = result.manysmall[, 5], Method = rep("Knockoff", length(result.manysmall[, 5])), Scenario = rep("More Small Signals", length(result.manysmall[, 5]))),
   cbind.data.frame(Power = result.manysmall[, 6], Method = rep("Knockoff+", length(result.manysmall[, 6])), Scenario = rep("More Small Signals", length(result.manysmall[, 6])))
 )

ggplot(data = Power.summary,
        aes(x = Method, y = Power, col = Method)) +
  geom_violin(trim = TRUE) +
  facet_wrap(~Scenario) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Overall Power at ", FDR == .(q), " Cutoff")), x = "", y = "Power") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10), axis.title.y = element_text(size = 10), axis.text.x = element_text(size = 10), axis.text.y = element_text(size = 10))
```

```{r, echo = FALSE}
Power.large.summary <- rbind.data.frame(
   cbind.data.frame(Power = result.nosmall[, 4], Method = rep("BH", length(result.nosmall[, 4])), Scenario = rep("No Small Signals", length(result.nosmall[, 4]))),
   cbind.data.frame(Power = result.nosmall[, 5], Method = rep("Knockoff", length(result.nosmall[, 5])), Scenario = rep("No Small Signals", length(result.nosmall[, 5]))),
   cbind.data.frame(Power = result.nosmall[, 6], Method = rep("Knockoff+", length(result.nosmall[, 6])), Scenario = rep("No Small Signals", length(result.nosmall[, 6]))),
   cbind.data.frame(Power = result.fewsmall[, 7], Method = rep("BH", length(result.fewsmall[, 7])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 7]))),
   cbind.data.frame(Power = result.fewsmall[, 8], Method = rep("Knockoff", length(result.fewsmall[, 8])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 8]))),
   cbind.data.frame(Power = result.fewsmall[, 9], Method = rep("Knockoff+", length(result.fewsmall[, 9])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 9]))),
   cbind.data.frame(Power = result.manysmall[, 7], Method = rep("BH", length(result.manysmall[, 7])), Scenario = rep("More Small Signals", length(result.manysmall[, 7]))),
   cbind.data.frame(Power = result.manysmall[, 8], Method = rep("Knockoff", length(result.manysmall[, 8])), Scenario = rep("More Small Signals", length(result.manysmall[, 8]))),
   cbind.data.frame(Power = result.manysmall[, 9], Method = rep("Knockoff+", length(result.manysmall[, 9])), Scenario = rep("More Small Signals", length(result.manysmall[, 9])))
 )

ggplot(data = Power.large.summary,
        aes(x = Method, y = Power, col = Method)) +
  geom_violin(trim = TRUE) +
  facet_wrap(~Scenario) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Power for Large Signals at ", FDR == .(q), " Cutoff")), x = "", y = "Power") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10), axis.title.y = element_text(size = 10), axis.text.x = element_text(size = 10), axis.text.y = element_text(size = 10))
```

```{r, echo = FALSE}
Power.small.summary <- rbind.data.frame(
   cbind.data.frame(Power = result.fewsmall[, 10], Method = rep("BH", length(result.fewsmall[, 10])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 10]))),
   cbind.data.frame(Power = result.fewsmall[, 11], Method = rep("Knockoff", length(result.fewsmall[, 11])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 11]))),
   cbind.data.frame(Power = result.fewsmall[, 12], Method = rep("Knockoff+", length(result.fewsmall[, 12])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 12]))),
   cbind.data.frame(Power = result.manysmall[, 10], Method = rep("BH", length(result.manysmall[, 10])), Scenario = rep("More Small Signals", length(result.manysmall[, 10]))),
   cbind.data.frame(Power = result.manysmall[, 11], Method = rep("Knockoff", length(result.manysmall[, 11])), Scenario = rep("More Small Signals", length(result.manysmall[, 11]))),
   cbind.data.frame(Power = result.manysmall[, 12], Method = rep("Knockoff+", length(result.manysmall[, 12])), Scenario = rep("More Small Signals", length(result.manysmall[, 12])))
 )

ggplot(data = Power.small.summary,
        aes(x = Method, y = Power, col = Method)) +
  geom_violin(trim = TRUE) +
  facet_wrap(~Scenario) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Power for Small Signals at ", FDR == .(q), " Cutoff")), x = "", y = "Power") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10), axis.title.y = element_text(size = 10), axis.text.x = element_text(size = 10), axis.text.y = element_text(size = 10))
```

## Independent design

$X_{n \times p}$ has independent columns simulated from $N(0, 1)$ and then normalized to have $\|X_j\|_2^2 \equiv 1$. 

```{r}
n <- 3000
p <- 1000
k <- 50
q <- 0.1
A <- 3.5
```

```{r, cache = TRUE}
X <- matrix(rnorm(n * p), n , p)
X <- t(t(X) / sqrt(colSums(X^2)))
Xk <- knockoff::create.fixed(X)
Xk <- Xk$Xk
```

```{r, echo = FALSE, cache = TRUE}
beta <- rep(0, p)
large <- sample(p, k)
beta[large] <- A
```

```{r, echo = FALSE, cache = TRUE}
m <- 1000
result <- list()
for (i in 1 : m) {
y <- X %*% beta + rnorm(n)

## Least squares
lm.fit <- lm(y ~ X - 1)
pvalue <- summary(lm.fit)$coefficients[, 4]

## BH
BH.fit <- p.adjust(pvalue, method = "BH")
BH.selected <- (1 : p)[BH.fit <= q]

## Knockoff
W = stat.glmnet_lambdasmax(X, Xk, y)
thres.knockoff = knockoff.threshold(W, fdr = q, offset = 0) # less conservative
thres.knockoff.plus = knockoff.threshold(W, fdr = q, offset = 1) # more conservative
knockoff.selected <- which(W >= thres.knockoff)
knockoff.plus.selected <- which(W >= thres.knockoff.plus)

result[[i]] <- c(
  fdp.BH = fdp(BH.selected),
  fdp.knockoff = fdp(knockoff.selected),
  fdp.knockoff.plus = fdp(knockoff.plus.selected),
  power.BH = power(BH.selected, sum(beta != 0)),
  power.knockoff = power(knockoff.selected, sum(beta != 0)),
  power.knockoff.plus = power(knockoff.plus.selected, sum(beta != 0))
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 6, byrow = TRUE)
colnames(result.summary) <- c("fdp.BH", "fdp.Knockoff", "fdp.Knockoff.plus", "power.BH", "power.Knockoff", "power.Knockoff.plus")
result.nosmall <- result.summary
```

```{r, cache = TRUE}
X <- matrix(rnorm(n * p), n , p)
X <- t(t(X) / sqrt(colSums(X^2)))
Xk <- knockoff::create.fixed(X)
Xk <- Xk$Xk
```

```{r, echo = FALSE}
k.small <- 100
beta <- rep(0, p)
large <- sample(p, k)
small <- sample(setdiff(seq(p), large), k.small)
beta[large] <- A
beta[small] <- seq(0, 3, length = k.small + 1)[-1]
```

```{r, echo = FALSE, cache = TRUE}
m <- 1000
result <- list()
for (i in 1 : m) {
y <- X %*% beta + rnorm(n)

## Least squares
lm.fit <- lm(y ~ X - 1)
pvalue <- summary(lm.fit)$coefficients[, 4]

## BH
BH.fit <- p.adjust(pvalue, method = "BH")
BH.selected <- (1 : p)[BH.fit <= q]

## Knockoff
W = stat.glmnet_lambdasmax(X, Xk, y)
thres.knockoff = knockoff.threshold(W, fdr = q, offset = 0) # less conservative
thres.knockoff.plus = knockoff.threshold(W, fdr = q, offset = 1) # more conservative
knockoff.selected <- which(W >= thres.knockoff)
knockoff.plus.selected <- which(W >= thres.knockoff.plus)

result[[i]] <- c(
  fdp.BH = fdp(BH.selected),
  fdp.knockoff = fdp(knockoff.selected),
  fdp.knockoff.plus = fdp(knockoff.plus.selected),
  power.BH = power(BH.selected, sum(beta != 0)),
  power.knockoff = power(knockoff.selected, sum(beta != 0)),
  power.knockoff.plus = power(knockoff.plus.selected, sum(beta != 0)),
  power.large.BH <- length(intersect(BH.selected, large)) / length(large),
  power.large.knockoff <- length(intersect(knockoff.selected, large)) / length(large),
  power.large.knockoff.plus <- length(intersect(knockoff.plus.selected, large)) / length(large),
  power.small.BH <- length(intersect(BH.selected, small)) / length(small),
  power.small.knockoff <- length(intersect(knockoff.selected, small)) / length(small),
  power.small.knockoff.plus <- length(intersect(knockoff.plus.selected, small)) / length(small)
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 12, byrow = TRUE)
colnames(result.summary) <- c("fdp.BH", "fdp.Knockoff", "fdp.Knockoff.plus", "power.BH", "power.Knockoff", "power.Knockoff.plus", "power.large.BH", "power.large.Knockoff", "power.large.Knockoff.plus", "power.small.BH", "power.small.Knockoff", "power.small.Knockoff.plus")
result.fewsmall <- result.summary
```

```{r, cache = TRUE}
X <- matrix(rnorm(n * p), n , p)
X <- t(t(X) / sqrt(colSums(X^2)))
Xk <- knockoff::create.fixed(X)
Xk <- Xk$Xk
```

```{r, echo = FALSE}
k.small <- 200
beta <- rep(0, p)
large <- sample(p, k)
small <- sample(setdiff(seq(p), large), k.small)
beta[large] <- A
beta[small] <- seq(0, 3, length = k.small + 1)[-1]
```

```{r, echo = FALSE, cache = TRUE}
m <- 1000
result <- list()
for (i in 1 : m) {
y <- X %*% beta + rnorm(n)

## Least squares
lm.fit <- lm(y ~ X - 1)
pvalue <- summary(lm.fit)$coefficients[, 4]

## BH
BH.fit <- p.adjust(pvalue, method = "BH")
BH.selected <- (1 : p)[BH.fit <= q]

## Knockoff
W = stat.glmnet_lambdasmax(X, Xk, y)
thres.knockoff = knockoff.threshold(W, fdr = q, offset = 0) # less conservative
thres.knockoff.plus = knockoff.threshold(W, fdr = q, offset = 1) # more conservative
knockoff.selected <- which(W >= thres.knockoff)
knockoff.plus.selected <- which(W >= thres.knockoff.plus)

result[[i]] <- c(
  fdp.BH = fdp(BH.selected),
  fdp.knockoff = fdp(knockoff.selected),
  fdp.knockoff.plus = fdp(knockoff.plus.selected),
  power.BH = power(BH.selected, sum(beta != 0)),
  power.knockoff = power(knockoff.selected, sum(beta != 0)),
  power.knockoff.plus = power(knockoff.plus.selected, sum(beta != 0)),
  power.large.BH <- length(intersect(BH.selected, large)) / length(large),
  power.large.knockoff <- length(intersect(knockoff.selected, large)) / length(large),
  power.large.knockoff.plus <- length(intersect(knockoff.plus.selected, large)) / length(large),
  power.small.BH <- length(intersect(BH.selected, small)) / length(small),
  power.small.knockoff <- length(intersect(knockoff.selected, small)) / length(small),
  power.small.knockoff.plus <- length(intersect(knockoff.plus.selected, small)) / length(small)
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 12, byrow = TRUE)
colnames(result.summary) <- c("fdp.BH", "fdp.Knockoff", "fdp.Knockoff.plus", "power.BH", "power.Knockoff", "power.Knockoff.plus", "power.large.BH", "power.large.Knockoff", "power.large.Knockoff.plus", "power.small.BH", "power.small.Knockoff", "power.small.Knockoff.plus")
result.manysmall <- result.summary
```

```{r, echo = FALSE}
summary <- rbind.data.frame(colMeans(result.nosmall), colMeans(result.fewsmall), colMeans(result.manysmall))
colnames(summary) <- c("FDP.BH", "FDP.Knockoff", "FDP.Knockoff.Plus", "Power.BH", "Power.Knockoff", "Power.Knockoff.Plus", "Power.Large.BH", "Power.Large.Knockoff", "Power.Large.Knockoff.Plus", "Power.Small.BH", "Power.Small.Knockoff", "Power.Small.Knockoff.Plus")
summary[1, 7 : 9] <- summary[1, 4 : 6]
summary[1, 10 : 12] <- NA
library(knitr)
kable(summary, digits = 4)
```

```{r, echo = FALSE}
FDP.summary <- rbind.data.frame(
   cbind.data.frame(FDP = result.nosmall[, 1], Method = rep("BH", length(result.nosmall[, 1])), Scenario = rep("No Small Signals", length(result.nosmall[, 1]))),
   cbind.data.frame(FDP = result.nosmall[, 2], Method = rep("Knockoff", length(result.nosmall[, 2])), Scenario = rep("No Small Signals", length(result.nosmall[, 2]))),
   cbind.data.frame(FDP = result.nosmall[, 3], Method = rep("Knockoff+", length(result.nosmall[, 3])), Scenario = rep("No Small Signals", length(result.nosmall[, 3]))),
   cbind.data.frame(FDP = result.fewsmall[, 1], Method = rep("BH", length(result.fewsmall[, 1])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 1]))),
   cbind.data.frame(FDP = result.fewsmall[, 2], Method = rep("Knockoff", length(result.fewsmall[, 2])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 2]))),
   cbind.data.frame(FDP = result.fewsmall[, 3], Method = rep("Knockoff+", length(result.fewsmall[, 3])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 3]))),
   cbind.data.frame(FDP = result.manysmall[, 1], Method = rep("BH", length(result.manysmall[, 1])), Scenario = rep("More Small Signals", length(result.manysmall[, 1]))),
   cbind.data.frame(FDP = result.manysmall[, 2], Method = rep("Knockoff", length(result.manysmall[, 2])), Scenario = rep("More Small Signals", length(result.manysmall[, 2]))),
   cbind.data.frame(FDP = result.manysmall[, 3], Method = rep("Knockoff+", length(result.manysmall[, 3])), Scenario = rep("More Small Signals", length(result.manysmall[, 3])))
 )

ggplot(data = FDP.summary,
        aes(x = Method, y = FDP, col = Method)) +
  geom_violin(trim = TRUE) +
  facet_wrap(~Scenario) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  geom_hline(yintercept = q, col = "maroon", linetype = "dashed", size = 1) +
  labs(title = bquote(paste("False Discovery Proportions at ", FDR == .(q), " Cutoff")), x = "", y = "FDP") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10), axis.title.y = element_text(size = 10), axis.text.x = element_text(size = 10), axis.text.y = element_text(size = 10))
```

```{r, echo = FALSE}
Power.summary <- rbind.data.frame(
   cbind.data.frame(Power = result.nosmall[, 4], Method = rep("BH", length(result.nosmall[, 4])), Scenario = rep("No Small Signals", length(result.nosmall[, 4]))),
   cbind.data.frame(Power = result.nosmall[, 5], Method = rep("Knockoff", length(result.nosmall[, 5])), Scenario = rep("No Small Signals", length(result.nosmall[, 5]))),
   cbind.data.frame(Power = result.nosmall[, 6], Method = rep("Knockoff+", length(result.nosmall[, 6])), Scenario = rep("No Small Signals", length(result.nosmall[, 6]))),
   cbind.data.frame(Power = result.fewsmall[, 4], Method = rep("BH", length(result.fewsmall[, 4])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 4]))),
   cbind.data.frame(Power = result.fewsmall[, 5], Method = rep("Knockoff", length(result.fewsmall[, 5])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 5]))),
   cbind.data.frame(Power = result.fewsmall[, 6], Method = rep("Knockoff+", length(result.fewsmall[, 6])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 6]))),
   cbind.data.frame(Power = result.manysmall[, 4], Method = rep("BH", length(result.manysmall[, 4])), Scenario = rep("More Small Signals", length(result.manysmall[, 4]))),
   cbind.data.frame(Power = result.manysmall[, 5], Method = rep("Knockoff", length(result.manysmall[, 5])), Scenario = rep("More Small Signals", length(result.manysmall[, 5]))),
   cbind.data.frame(Power = result.manysmall[, 6], Method = rep("Knockoff+", length(result.manysmall[, 6])), Scenario = rep("More Small Signals", length(result.manysmall[, 6])))
 )

ggplot(data = Power.summary,
        aes(x = Method, y = Power, col = Method)) +
  geom_violin(trim = TRUE) +
  facet_wrap(~Scenario) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Overall Power at ", FDR == .(q), " Cutoff")), x = "", y = "Power") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10), axis.title.y = element_text(size = 10), axis.text.x = element_text(size = 10), axis.text.y = element_text(size = 10))
```

```{r, echo = FALSE}
Power.large.summary <- rbind.data.frame(
   cbind.data.frame(Power = result.nosmall[, 4], Method = rep("BH", length(result.nosmall[, 4])), Scenario = rep("No Small Signals", length(result.nosmall[, 4]))),
   cbind.data.frame(Power = result.nosmall[, 5], Method = rep("Knockoff", length(result.nosmall[, 5])), Scenario = rep("No Small Signals", length(result.nosmall[, 5]))),
   cbind.data.frame(Power = result.nosmall[, 6], Method = rep("Knockoff+", length(result.nosmall[, 6])), Scenario = rep("No Small Signals", length(result.nosmall[, 6]))),
   cbind.data.frame(Power = result.fewsmall[, 7], Method = rep("BH", length(result.fewsmall[, 7])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 7]))),
   cbind.data.frame(Power = result.fewsmall[, 8], Method = rep("Knockoff", length(result.fewsmall[, 8])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 8]))),
   cbind.data.frame(Power = result.fewsmall[, 9], Method = rep("Knockoff+", length(result.fewsmall[, 9])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 9]))),
   cbind.data.frame(Power = result.manysmall[, 7], Method = rep("BH", length(result.manysmall[, 7])), Scenario = rep("More Small Signals", length(result.manysmall[, 7]))),
   cbind.data.frame(Power = result.manysmall[, 8], Method = rep("Knockoff", length(result.manysmall[, 8])), Scenario = rep("More Small Signals", length(result.manysmall[, 8]))),
   cbind.data.frame(Power = result.manysmall[, 9], Method = rep("Knockoff+", length(result.manysmall[, 9])), Scenario = rep("More Small Signals", length(result.manysmall[, 9])))
 )

ggplot(data = Power.large.summary,
        aes(x = Method, y = Power, col = Method)) +
  geom_violin(trim = TRUE) +
  facet_wrap(~Scenario) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Power for Large Signals at ", FDR == .(q), " Cutoff")), x = "", y = "Power") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10), axis.title.y = element_text(size = 10), axis.text.x = element_text(size = 10), axis.text.y = element_text(size = 10))
```

```{r, echo = FALSE}
Power.small.summary <- rbind.data.frame(
   cbind.data.frame(Power = result.fewsmall[, 10], Method = rep("BH", length(result.fewsmall[, 10])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 10]))),
   cbind.data.frame(Power = result.fewsmall[, 11], Method = rep("Knockoff", length(result.fewsmall[, 11])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 11]))),
   cbind.data.frame(Power = result.fewsmall[, 12], Method = rep("Knockoff+", length(result.fewsmall[, 12])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 12]))),
   cbind.data.frame(Power = result.manysmall[, 10], Method = rep("BH", length(result.manysmall[, 10])), Scenario = rep("More Small Signals", length(result.manysmall[, 10]))),
   cbind.data.frame(Power = result.manysmall[, 11], Method = rep("Knockoff", length(result.manysmall[, 11])), Scenario = rep("More Small Signals", length(result.manysmall[, 11]))),
   cbind.data.frame(Power = result.manysmall[, 12], Method = rep("Knockoff+", length(result.manysmall[, 12])), Scenario = rep("More Small Signals", length(result.manysmall[, 12])))
 )

ggplot(data = Power.small.summary,
        aes(x = Method, y = Power, col = Method)) +
  geom_violin(trim = TRUE) +
  facet_wrap(~Scenario) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Power for Small Signals at ", FDR == .(q), " Cutoff")), x = "", y = "Power") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10), axis.title.y = element_text(size = 10), axis.text.x = element_text(size = 10), axis.text.y = element_text(size = 10))
```

## Local correlation design

$X_{n \times p}$ has correlation $\Sigma_{ij} = \rho^{|i - j|}$. Each row is independently $N(0, \Sigma)$ and then normalized to have $\|X_j\|_2^2 \equiv 1$.

```{r}
n <- 3000
p <- 1000
k <- 50
q <- 0.1
A <- 3.5
```

```{r, cache = TRUE}
X <- matrix(rnorm(n * p), n , p)
X <- t(t(X) / sqrt(colSums(X^2)))
rho <- 0.25
Sigma <- toeplitz(rho^(0 : (p - 1)))
X <- X %*% chol(Sigma)
Xk <- knockoff::create.fixed(X)
Xk <- Xk$Xk
```

```{r, echo = FALSE, cache = TRUE}
beta <- rep(0, p)
large <- sample(p, k)
beta[large] <- A
```

```{r, echo = FALSE, cache = TRUE}
m <- 1000
result <- list()
for (i in 1 : m) {
y <- X %*% beta + rnorm(n)

## Least squares
lm.fit <- lm(y ~ X - 1)
pvalue <- summary(lm.fit)$coefficients[, 4]

## BH
BH.fit <- p.adjust(pvalue, method = "BH")
BH.selected <- (1 : p)[BH.fit <= q]

## Knockoff
W = stat.glmnet_lambdasmax(X, Xk, y)
thres.knockoff = knockoff.threshold(W, fdr = q, offset = 0) # less conservative
thres.knockoff.plus = knockoff.threshold(W, fdr = q, offset = 1) # more conservative
knockoff.selected <- which(W >= thres.knockoff)
knockoff.plus.selected <- which(W >= thres.knockoff.plus)

result[[i]] <- c(
  fdp.BH = fdp(BH.selected),
  fdp.knockoff = fdp(knockoff.selected),
  fdp.knockoff.plus = fdp(knockoff.plus.selected),
  power.BH = power(BH.selected, sum(beta != 0)),
  power.knockoff = power(knockoff.selected, sum(beta != 0)),
  power.knockoff.plus = power(knockoff.plus.selected, sum(beta != 0))
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 6, byrow = TRUE)
colnames(result.summary) <- c("fdp.BH", "fdp.Knockoff", "fdp.Knockoff.plus", "power.BH", "power.Knockoff", "power.Knockoff.plus")
result.nosmall <- result.summary
```

```{r, cache = TRUE}
X <- matrix(rnorm(n * p), n , p)
X <- t(t(X) / sqrt(colSums(X^2)))
rho <- 0.25
Sigma <- toeplitz(rho^(0 : (p - 1)))
X <- X %*% chol(Sigma)
Xk <- knockoff::create.fixed(X)
Xk <- Xk$Xk
```

```{r, echo = FALSE}
k.small <- 100
beta <- rep(0, p)
large <- sample(p, k)
small <- sample(setdiff(seq(p), large), k.small)
beta[large] <- A
beta[small] <- seq(0, 3, length = k.small + 1)[-1]
```

```{r, echo = FALSE, cache = TRUE}
m <- 1000
result <- list()
for (i in 1 : m) {
y <- X %*% beta + rnorm(n)

## Least squares
lm.fit <- lm(y ~ X - 1)
pvalue <- summary(lm.fit)$coefficients[, 4]

## BH
BH.fit <- p.adjust(pvalue, method = "BH")
BH.selected <- (1 : p)[BH.fit <= q]

## Knockoff
W = stat.glmnet_lambdasmax(X, Xk, y)
thres.knockoff = knockoff.threshold(W, fdr = q, offset = 0) # less conservative
thres.knockoff.plus = knockoff.threshold(W, fdr = q, offset = 1) # more conservative
knockoff.selected <- which(W >= thres.knockoff)
knockoff.plus.selected <- which(W >= thres.knockoff.plus)

result[[i]] <- c(
  fdp.BH = fdp(BH.selected),
  fdp.knockoff = fdp(knockoff.selected),
  fdp.knockoff.plus = fdp(knockoff.plus.selected),
  power.BH = power(BH.selected, sum(beta != 0)),
  power.knockoff = power(knockoff.selected, sum(beta != 0)),
  power.knockoff.plus = power(knockoff.plus.selected, sum(beta != 0)),
  power.large.BH <- length(intersect(BH.selected, large)) / length(large),
  power.large.knockoff <- length(intersect(knockoff.selected, large)) / length(large),
  power.large.knockoff.plus <- length(intersect(knockoff.plus.selected, large)) / length(large),
  power.small.BH <- length(intersect(BH.selected, small)) / length(small),
  power.small.knockoff <- length(intersect(knockoff.selected, small)) / length(small),
  power.small.knockoff.plus <- length(intersect(knockoff.plus.selected, small)) / length(small)
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 12, byrow = TRUE)
colnames(result.summary) <- c("fdp.BH", "fdp.Knockoff", "fdp.Knockoff.plus", "power.BH", "power.Knockoff", "power.Knockoff.plus", "power.large.BH", "power.large.Knockoff", "power.large.Knockoff.plus", "power.small.BH", "power.small.Knockoff", "power.small.Knockoff.plus")
result.fewsmall <- result.summary
```

```{r, cache = TRUE}
X <- matrix(rnorm(n * p), n , p)
X <- t(t(X) / sqrt(colSums(X^2)))
rho <- 0.25
Sigma <- toeplitz(rho^(0 : (p - 1)))
X <- X %*% chol(Sigma)
Xk <- knockoff::create.fixed(X)
Xk <- Xk$Xk
```

```{r, echo = FALSE}
k.small <- 200
beta <- rep(0, p)
large <- sample(p, k)
small <- sample(setdiff(seq(p), large), k.small)
beta[large] <- A
beta[small] <- seq(0, 3, length = k.small + 1)[-1]
```

```{r, echo = FALSE, cache = TRUE}
m <- 1000
result <- list()
for (i in 1 : m) {
y <- X %*% beta + rnorm(n)

## Least squares
lm.fit <- lm(y ~ X - 1)
pvalue <- summary(lm.fit)$coefficients[, 4]

## BH
BH.fit <- p.adjust(pvalue, method = "BH")
BH.selected <- (1 : p)[BH.fit <= q]

## Knockoff
W = stat.glmnet_lambdasmax(X, Xk, y)
thres.knockoff = knockoff.threshold(W, fdr = q, offset = 0) # less conservative
thres.knockoff.plus = knockoff.threshold(W, fdr = q, offset = 1) # more conservative
knockoff.selected <- which(W >= thres.knockoff)
knockoff.plus.selected <- which(W >= thres.knockoff.plus)

result[[i]] <- c(
  fdp.BH = fdp(BH.selected),
  fdp.knockoff = fdp(knockoff.selected),
  fdp.knockoff.plus = fdp(knockoff.plus.selected),
  power.BH = power(BH.selected, sum(beta != 0)),
  power.knockoff = power(knockoff.selected, sum(beta != 0)),
  power.knockoff.plus = power(knockoff.plus.selected, sum(beta != 0)),
  power.large.BH <- length(intersect(BH.selected, large)) / length(large),
  power.large.knockoff <- length(intersect(knockoff.selected, large)) / length(large),
  power.large.knockoff.plus <- length(intersect(knockoff.plus.selected, large)) / length(large),
  power.small.BH <- length(intersect(BH.selected, small)) / length(small),
  power.small.knockoff <- length(intersect(knockoff.selected, small)) / length(small),
  power.small.knockoff.plus <- length(intersect(knockoff.plus.selected, small)) / length(small)
)
}
```

```{r, echo = FALSE}
result.summary <- matrix(unlist(result), m, 12, byrow = TRUE)
colnames(result.summary) <- c("fdp.BH", "fdp.Knockoff", "fdp.Knockoff.plus", "power.BH", "power.Knockoff", "power.Knockoff.plus", "power.large.BH", "power.large.Knockoff", "power.large.Knockoff.plus", "power.small.BH", "power.small.Knockoff", "power.small.Knockoff.plus")
result.manysmall <- result.summary
```

```{r, echo = FALSE}
summary <- rbind.data.frame(colMeans(result.nosmall), colMeans(result.fewsmall), colMeans(result.manysmall))
colnames(summary) <- c("FDP.BH", "FDP.Knockoff", "FDP.Knockoff.Plus", "Power.BH", "Power.Knockoff", "Power.Knockoff.Plus", "Power.Large.BH", "Power.Large.Knockoff", "Power.Large.Knockoff.Plus", "Power.Small.BH", "Power.Small.Knockoff", "Power.Small.Knockoff.Plus")
summary[1, 7 : 9] <- summary[1, 4 : 6]
summary[1, 10 : 12] <- NA
library(knitr)
kable(summary, digits = 4)
```

```{r, echo = FALSE}
FDP.summary <- rbind.data.frame(
   cbind.data.frame(FDP = result.nosmall[, 1], Method = rep("BH", length(result.nosmall[, 1])), Scenario = rep("No Small Signals", length(result.nosmall[, 1]))),
   cbind.data.frame(FDP = result.nosmall[, 2], Method = rep("Knockoff", length(result.nosmall[, 2])), Scenario = rep("No Small Signals", length(result.nosmall[, 2]))),
   cbind.data.frame(FDP = result.nosmall[, 3], Method = rep("Knockoff+", length(result.nosmall[, 3])), Scenario = rep("No Small Signals", length(result.nosmall[, 3]))),
   cbind.data.frame(FDP = result.fewsmall[, 1], Method = rep("BH", length(result.fewsmall[, 1])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 1]))),
   cbind.data.frame(FDP = result.fewsmall[, 2], Method = rep("Knockoff", length(result.fewsmall[, 2])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 2]))),
   cbind.data.frame(FDP = result.fewsmall[, 3], Method = rep("Knockoff+", length(result.fewsmall[, 3])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 3]))),
   cbind.data.frame(FDP = result.manysmall[, 1], Method = rep("BH", length(result.manysmall[, 1])), Scenario = rep("More Small Signals", length(result.manysmall[, 1]))),
   cbind.data.frame(FDP = result.manysmall[, 2], Method = rep("Knockoff", length(result.manysmall[, 2])), Scenario = rep("More Small Signals", length(result.manysmall[, 2]))),
   cbind.data.frame(FDP = result.manysmall[, 3], Method = rep("Knockoff+", length(result.manysmall[, 3])), Scenario = rep("More Small Signals", length(result.manysmall[, 3])))
 )

ggplot(data = FDP.summary,
        aes(x = Method, y = FDP, col = Method)) +
  geom_violin(trim = TRUE) +
  facet_wrap(~Scenario) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  geom_hline(yintercept = q, col = "maroon", linetype = "dashed", size = 1) +
  labs(title = bquote(paste("False Discovery Proportions at ", FDR == .(q), " Cutoff")), x = "", y = "FDP") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10), axis.title.y = element_text(size = 10), axis.text.x = element_text(size = 10), axis.text.y = element_text(size = 10))
```

```{r, echo = FALSE}
Power.summary <- rbind.data.frame(
   cbind.data.frame(Power = result.nosmall[, 4], Method = rep("BH", length(result.nosmall[, 4])), Scenario = rep("No Small Signals", length(result.nosmall[, 4]))),
   cbind.data.frame(Power = result.nosmall[, 5], Method = rep("Knockoff", length(result.nosmall[, 5])), Scenario = rep("No Small Signals", length(result.nosmall[, 5]))),
   cbind.data.frame(Power = result.nosmall[, 6], Method = rep("Knockoff+", length(result.nosmall[, 6])), Scenario = rep("No Small Signals", length(result.nosmall[, 6]))),
   cbind.data.frame(Power = result.fewsmall[, 4], Method = rep("BH", length(result.fewsmall[, 4])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 4]))),
   cbind.data.frame(Power = result.fewsmall[, 5], Method = rep("Knockoff", length(result.fewsmall[, 5])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 5]))),
   cbind.data.frame(Power = result.fewsmall[, 6], Method = rep("Knockoff+", length(result.fewsmall[, 6])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 6]))),
   cbind.data.frame(Power = result.manysmall[, 4], Method = rep("BH", length(result.manysmall[, 4])), Scenario = rep("More Small Signals", length(result.manysmall[, 4]))),
   cbind.data.frame(Power = result.manysmall[, 5], Method = rep("Knockoff", length(result.manysmall[, 5])), Scenario = rep("More Small Signals", length(result.manysmall[, 5]))),
   cbind.data.frame(Power = result.manysmall[, 6], Method = rep("Knockoff+", length(result.manysmall[, 6])), Scenario = rep("More Small Signals", length(result.manysmall[, 6])))
 )

ggplot(data = Power.summary,
        aes(x = Method, y = Power, col = Method)) +
  geom_violin(trim = TRUE) +
  facet_wrap(~Scenario) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Overall Power at ", FDR == .(q), " Cutoff")), x = "", y = "Power") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10), axis.title.y = element_text(size = 10), axis.text.x = element_text(size = 10), axis.text.y = element_text(size = 10))
```

```{r, echo = FALSE}
Power.large.summary <- rbind.data.frame(
   cbind.data.frame(Power = result.nosmall[, 4], Method = rep("BH", length(result.nosmall[, 4])), Scenario = rep("No Small Signals", length(result.nosmall[, 4]))),
   cbind.data.frame(Power = result.nosmall[, 5], Method = rep("Knockoff", length(result.nosmall[, 5])), Scenario = rep("No Small Signals", length(result.nosmall[, 5]))),
   cbind.data.frame(Power = result.nosmall[, 6], Method = rep("Knockoff+", length(result.nosmall[, 6])), Scenario = rep("No Small Signals", length(result.nosmall[, 6]))),
   cbind.data.frame(Power = result.fewsmall[, 7], Method = rep("BH", length(result.fewsmall[, 7])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 7]))),
   cbind.data.frame(Power = result.fewsmall[, 8], Method = rep("Knockoff", length(result.fewsmall[, 8])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 8]))),
   cbind.data.frame(Power = result.fewsmall[, 9], Method = rep("Knockoff+", length(result.fewsmall[, 9])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 9]))),
   cbind.data.frame(Power = result.manysmall[, 7], Method = rep("BH", length(result.manysmall[, 7])), Scenario = rep("More Small Signals", length(result.manysmall[, 7]))),
   cbind.data.frame(Power = result.manysmall[, 8], Method = rep("Knockoff", length(result.manysmall[, 8])), Scenario = rep("More Small Signals", length(result.manysmall[, 8]))),
   cbind.data.frame(Power = result.manysmall[, 9], Method = rep("Knockoff+", length(result.manysmall[, 9])), Scenario = rep("More Small Signals", length(result.manysmall[, 9])))
 )

ggplot(data = Power.large.summary,
        aes(x = Method, y = Power, col = Method)) +
  geom_violin(trim = TRUE) +
  facet_wrap(~Scenario) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Power for Large Signals at ", FDR == .(q), " Cutoff")), x = "", y = "Power") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10), axis.title.y = element_text(size = 10), axis.text.x = element_text(size = 10), axis.text.y = element_text(size = 10))
```

```{r, echo = FALSE}
Power.small.summary <- rbind.data.frame(
   cbind.data.frame(Power = result.fewsmall[, 10], Method = rep("BH", length(result.fewsmall[, 10])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 10]))),
   cbind.data.frame(Power = result.fewsmall[, 11], Method = rep("Knockoff", length(result.fewsmall[, 11])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 11]))),
   cbind.data.frame(Power = result.fewsmall[, 12], Method = rep("Knockoff+", length(result.fewsmall[, 12])), Scenario = rep("Less Small Signals", length(result.fewsmall[, 12]))),
   cbind.data.frame(Power = result.manysmall[, 10], Method = rep("BH", length(result.manysmall[, 10])), Scenario = rep("More Small Signals", length(result.manysmall[, 10]))),
   cbind.data.frame(Power = result.manysmall[, 11], Method = rep("Knockoff", length(result.manysmall[, 11])), Scenario = rep("More Small Signals", length(result.manysmall[, 11]))),
   cbind.data.frame(Power = result.manysmall[, 12], Method = rep("Knockoff+", length(result.manysmall[, 12])), Scenario = rep("More Small Signals", length(result.manysmall[, 12])))
 )

ggplot(data = Power.small.summary,
        aes(x = Method, y = Power, col = Method)) +
  geom_violin(trim = TRUE) +
  facet_wrap(~Scenario) +
  stat_summary(fun.data = "mean_sdp", geom = "pointrange") +
  scale_color_manual(values = method.col) +
  labs(title = bquote(paste("Power for Small Signals at ", FDR == .(q), " Cutoff")), x = "", y = "Power") +
  theme(legend.position = "none", plot.title = element_text(hjust = 0.5, size = 10), axis.title.y = element_text(size = 10), axis.text.x = element_text(size = 10), axis.text.y = element_text(size = 10))
```


## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
