---
title: "Regularized Gaussian Derivatives & `ASH`: Simulated True Effects with Heteroskedastic Correlated Noises"
author: "Lei Sun"
date: 2017-05-14
output: workflowr::wflow_html
---





## Introduction

Similar to [previous simulations](mosek_reg_4.html), where correlated null $z$ scores are fitted by $10$ Gaussian derivatives with regularization, we are now [fitting data sets simulated with correlated noise and true signals](ash_gd.html) by both `ASH` and Gaussian derivatives using the same regularization and see what happens.

The study is almost exactly the same as [the previous one](mosek_reg_5.html), **the single only change being that this time, the correlated noise is heteroskedastic**.  That is, $\hat s_j$ are not constant; in this simulation, they are simulated such that $\log\hat s_j \sim \text{Uniform}\left[\log0.1, \log10\right]$.

```{r, message = FALSE}
library(ashr)
source("../code/gdash.R")
```

```{r, echo = FALSE}
sample.g = function (g, n) {
  UseMethod("sample.g")
}

sample.g.normalmix = function (g, n) {
  K = length(g$pi)
  beta = list()
  for (i in 1 : K) {
    beta[[i]] = rnorm(ceiling(n * g$pi[i]), g$mean[i], g$sd[i])
  }
  return(list(beta = sample(unlist(beta)), mixcompdist = "normal"))
}

sample.g.unimix = function(g, n) {
  K = length(g$pi)
  beta = list()
  for (i in 1 : K) {
    beta[[i]] = runif(ceiling(n * g$pi[i]), g$a[i], g$b[i])
  }
  return(list(beta = sample(unlist(beta)), mixcompdist = "uniform"))
}

se.fun = function (n, method) {
  if (method == "constant") {
    sebetahat = rep(1, n)
  } else {
    sebetahat = exp(runif(n, log(0.1), log(10)))
  }
}

AltPlot = function (z.list, z.index, label, g, se, L, lambda, rho, maxiter) {
  x.range = max(c(2 * g$sd, 4))
  x.plot = seq(-x.range, x.range, 0.01)
  y.true = ashr::mixcdf(g, x.plot)
  data.set.num = length(z.list[[label]])
  for (i in 1 : data.set.num) {
    z = z.list[[label]][[i]]
    effect = sample.g(g, length(z))
    beta = effect$beta[1 : length(z)]
    sebetahat = se.fun(length(z), se)
    betahat = beta + sebetahat * z
    fit.ash = ashr::ash(betahat, sebetahat, mixcompdist = effect$mixcompdist, method = "fdr")
    if (missing(maxiter)) {
      control = list(maxiter = 50)
    } else {
      control = list(maxiter = maxiter)
    }
    gdash.time <- system.time(fit.gdash <- gdash(betahat, sebetahat,
                      mixcompdist = effect$mixcompdist,
                      gd.ord = L, w.lambda = lambda, w.rho = rho,
                      gd.normalized = TRUE, primal = FALSE,
                      method = "fdr", control = control))
    y.ash = ashr::mixcdf(fit.ash$fitted_g, x.plot)
    y.gdash = ashr::mixcdf(fit.gdash$fitted_g, x.plot)
    cat("Data Set", z.index[[label]]$set[i], ";\n")
    cat("For the Correlated Null Z Scores Only:\n")
    cat("Number of False Discoveries by BH at FDR = 0.05:", z.index[[label]]$fd.FDR0.05.bh[i], ";\n")
    cat("Number of False Discoveries by ASH at lfsr <= 0.05:", z.index[[label]]$fd.lfsr0.05.ash[i], ";\n")
    cat("pihat0 by ASH:", z.index[[label]]$pihat0.ash[i], ";\n")
    z.hist = hist(z, breaks = 100, plot = FALSE)
    hist(z, breaks = 100, prob = TRUE, ylim = c(0, max(c(dnorm(0), max(z.hist$density)))), xlab = "Correlated N(0, 1) Noise", main = "Histogram of the Correlated N(0, 1) Noise")
    lines(x.plot, dnorm(x.plot), col = "red")
    cat("Number of iterations:", fit.gdash$niter, ";\n")
    cat("Converged:", fit.gdash$converged, ";\n")
    cat("Time:", gdash.time[3], "Seconds;\n")
    cat("Normalized w:", rbind(paste(0 : L, "-"), paste(round(fit.gdash$w, 5), ";")), "\n")
    plot(x.plot, y.true, type = "l", lty = 2, ylim = c(0, 1), xlab = expression(beta), ylab = expression(hat(G)(beta)), main = expression(paste(hat(G), ": CDF of ", hat(g))))
    lines(x.plot, y.ash, lty = 2, col = "red")
    lines(x.plot, y.gdash, col = "blue")
    legend("topleft", lty = c(2, 2, 1), col = c("black", "red", "blue"), legend = c("True", "ASH", "GD-ASH"))
  }
}
```

```{r}
L = 10
lambda = 10
rho = 0.5
```

```{r}
g.null = normalmix(pi = 1, mean = 0, sd = 0)
g.s.n = normalmix(pi = c(0.6, 0.3, 0.1), mean = 0, sd = c(0, 1, 2))
g.m.n = normalmix(pi = c(0.6, 0.3, 0.1), mean = 0, sd = c(0, 2, 4))
g.l.n = normalmix(pi = c(0.6, 0.3, 0.1), mean = 0, sd = c(0, 3, 6))
```

```{r}
se = "heteroskedasticity"
```

```{r}
z.list = readRDS("../output/z_null_liver_777_select.RDS")
z.index = readRDS("../output/z_null_liver_777_select_index.RDS")
```

## Category I: Typical

```{r}
label = "typical"
```

### Global null $g_n$

```{r}
g = g.null
```

```{r, cache = TRUE, echo = FALSE}
set.seed(10)
AltPlot(z.list, z.index, label, g, se, L, lambda, rho)
```

### Small effects $g_s$

```{r}
g = g.s.n
```

```{r, cache = TRUE, echo = FALSE}
set.seed(11)
AltPlot(z.list, z.index, label, g, se, L, lambda, rho)
```

### Medium effects $g_m$

```{r}
g = g.m.n
```

```{r, cache = TRUE, echo = FALSE}
set.seed(12)
AltPlot(z.list, z.index, label, g, se, L, lambda, rho)
```

### Large effects $g_l$

```{r}
g = g.l.n
```

```{r, cache = TRUE, echo = FALSE}
set.seed(13)
AltPlot(z.list, z.index, label, g, se, L, lambda, rho)
```

## Category II: Hostile

```{r}
label = "hostile"
```

### Global null $g_n$

```{r}
g = g.null
```

```{r, cache = TRUE, echo = FALSE}
set.seed(20)
AltPlot(z.list, z.index, label, g, se, L, lambda, rho)
```

### Small effects $g_s$

```{r}
g = g.s.n
```

```{r, cache = TRUE, echo = FALSE}
set.seed(21)
AltPlot(z.list, z.index, label, g, se, L, lambda, rho)
```

### Medium effects $g_m$

```{r}
g = g.m.n
```

```{r, cache = TRUE, echo = FALSE}
set.seed(22)
AltPlot(z.list, z.index, label, g, se, L, lambda, rho)
```

### Large effects $g_l$

```{r}
g = g.l.n
```

```{r, cache = TRUE, echo = FALSE}
set.seed(23)
AltPlot(z.list, z.index, label, g, se, L, lambda, rho)
```


## Category III: Friendly

```{r}
label = "friendly"
```

### Global null $g_n$

```{r}
g = g.null
```

```{r, cache = TRUE, echo = FALSE}
set.seed(30)
AltPlot(z.list, z.index, label, g, se, L, lambda, rho)
```

### Small effects $g_s$

```{r}
g = g.s.n
```

```{r, cache = TRUE, echo = FALSE}
set.seed(31)
AltPlot(z.list, z.index, label, g, se, L, lambda, rho)
```

### Medium effects $g_m$

```{r}
g = g.m.n
```

```{r, cache = TRUE, echo = FALSE}
set.seed(32)
AltPlot(z.list, z.index, label, g, se, L, lambda, rho)
```

### Large effects $g_l$

```{r}
g = g.l.n
```

```{r, cache = TRUE, echo = FALSE}
set.seed(33)
AltPlot(z.list, z.index, label, g, se, L, lambda, rho)
```

## Category III: iid

```{r}
label = "iid"
```

### Global null $g_n$

```{r}
g = g.null
```

```{r, echo = FALSE, cache = TRUE}
set.seed(40)
AltPlot(z.list, z.index, label, g, se, L, lambda, rho)
```

### Small effects $g_s$

```{r}
g = g.s.n
```

```{r, cache = TRUE, echo = FALSE}
set.seed(41)
AltPlot(z.list, z.index, label, g, se, L, lambda, rho)
```

### Medium effects $g_m$

```{r}
g = g.m.n
```

```{r, cache = TRUE, echo = FALSE}
set.seed(42)
AltPlot(z.list, z.index, label, g, se, L, lambda, rho)
```

### Large effects $g_l$

```{r}
g = g.l.n
```

```{r, cache = TRUE, echo = FALSE}
set.seed(43)
AltPlot(z.list, z.index, label, g, se, L, lambda, rho)
```



