---
title: "Improvement on Implementation with `Rmosek`: Primal and Dual"
author: "Lei Sun"
date: 2017-05-07
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

## Introduction

We are experimenting different ways to improve the performance of `Rmosek`, using typical data sets of correlated $z$ scores.

```{r read in correlated z, cache = TRUE}
z <- read.table("../output/z_null_liver_777.txt")
```

```{r select data sets, cache = TRUE}
sel <- c(32, 327, 355, 483, 778)
ord <- c(4, 9, 9, 4, 4)
```

```{r select z score matrix, cache = TRUE, echo = FALSE}
sel.num = length(sel)
zscore = list()
for (i in 1 : sel.num) {
  zscore[[i]] = as.numeric(z[sel[i], ])
}
```

```{r gdash script, message = FALSE}
source("../code/gdash.R")
```

```{r Hermite polynomials, cache = TRUE, echo = FALSE}
library(PolynomF)
x <- polynom()
H <- polylist(x, - 1 + x^2)
for(n in 2 : 19)
  H[[n+1]] <- x * H[[n]] - n * H[[n-1]]
```

## Algorithm and variations

Recall that our [biconvex optimization problem](ash_gd.html#optimization_problem) is as follows.

$$
\begin{array}{rl}
\min\limits_{\pi,w} & -\sum\limits_{j = 1}^n\log\left(\sum\limits_{k = 1}^K\sum\limits_{l=1}^L\pi_k w_l f_{jkl} + \sum\limits_{k = 1}^K\pi_kf_{jk0}\right) - \sum\limits_{k = 1}^K\left(\lambda_k^\pi - 1\right)\log\pi_k + \sum\limits_{l = 1}^L\lambda_l^w\phi\left(\left|w_l\right|\right)
\\
\text{subject to} & \sum\limits_{k = 1}^K\pi_k = 1\\
& \sum\limits_{l=1}^L w_l \varphi^{(l)}\left(z\right) + \varphi\left(z\right) \geq 0, \forall z\in \mathbb{R}\\
& w_l \text{ decay reasonably fast,}
\end{array}
$$
where $- \sum\limits_{k = 1}^K\left(\lambda_k^\pi - 1\right)\log\pi_k$ and $+ \sum\limits_{l = 1}^L\lambda_l^w\phi\left(\left|w_l\right|\right)$ are to regularize $\pi_k$ and $w_l$, respectively.

This problem can be solved iteratively.  Starting with an initial value, each step two convex optimization problems are solved.

With a given $\hat w$, $\hat\pi$ is solved by

$$
\begin{array}{rl}
\min\limits_{\pi} & -\sum\limits_{j = 1}^n\log\left(\sum\limits_{k = 1}^K\pi_k \left(\sum\limits_{l=1}^L \hat w_l f_{jkl} + f_{jk0}\right)\right) - \sum\limits_{k = 1}^K\left(\lambda_k^\pi - 1\right)\log\pi_k\\
\text{subject to} & \sum\limits_{k = 1}^K\pi_k = 1 \ ,\\
\end{array}
$$

which is readily available with functions in `cvxr`.

Meanwhile, with a given $\hat\pi$, the optimization problem to obtain $\hat w$ becomes

$$
\begin{array}{rl}
\min\limits_{w} & -\sum\limits_{j = 1}^n\log\left(\sum\limits_{l=1}^Lw_l\left(\sum\limits_{k = 1}^K\hat\pi_k  f_{jkl}\right) + \sum\limits_{k = 1}^K\hat\pi_kf_{jk0}\right) + 
\sum\limits_{l = 1}^L\lambda_l^w
\phi
\left(\left|w_l\right|\right)
\\
\text{subject to} & \sum\limits_{l=1}^L w_l \varphi^{(l)}\left(z\right) + \varphi\left(z\right) \geq 0, \forall z\in \mathbb{R}\\
& w_l \text{ decay reasonably fast.}
\end{array}
$$
The two constraints are important to prevent [numerical instability](gaussian_derivatives_3.html).  Yet they are not readily manifested as convex.  Ideally, the regularization $\sum\limits_{l = 1}^L\lambda_l^w\phi\left(\left|w_l\right|\right)$ would be able to capture the essence of these two constaints, and at the same time maintain the convexity.  Different ideas will be explored.

In this part, we'll mainly work on the "basic form" of the $w$ optimization problem; that is, the optimization problem without regularization $\sum\limits_{l = 1}^L\lambda_l^w\phi\left(\left|w_l\right|\right)$.

In the following, we'll take a look at the basic form in its primal and dual formulations, optimized by `w.mosek()` and `w.mosek.primal` functions.  First, they are applied to the correlated null, and their performance can be compared with [the previous implementation](gaussian_derivatives_2.html) by `cvxr`.  Then, they are applied to the simulated non-null data sets, and the results are compared with those obtained by `ASH`, as well as the truth.

## Basic form: primal

In its most basic form, the $w$ estimation problem is as follows.

$$
\begin{array}{rl}
\min\limits_{w} & 
-\sum\limits_{j = 1}^n
\log\left(\sum\limits_{l=1}^Lw_l a_{jl} + a_{j0}\right) 
\\
\text{subject to} & \sum\limits_{l=1}^Lw_l a_{jl} + a_{j0} \geq 0, \forall j \ .\\
\end{array}
$$
Let the matrix $A = \left[a_{jl}\right]$, the vector $a = \left[a_{j0}\right]$, and we have its equivalent form,

$$
\begin{array}{rl}
\min\limits_{w, g} & 
-\sum\limits_{j = 1}^n
\log\left(g_j\right) 
\\
\text{subject to}
& Aw + a = g \\
& g \geq 0\ .
\end{array}
$$

This problem can be coded by `Rmosek` as a "separable convex optimization" (SCOPT) problem.

### Correlated null

```{r Rmosek primal fitting, cache = TRUE, echo = FALSE}
n = ncol(z)
gd.primal = list()
time.primal = list()
for (i in 1 : sel.num) {
  K = ord[i]
  gd.mat = matrix(0, nrow = n, ncol = K)
  for (k in 1 : K)
    gd.mat[, k] = dnorm(zscore[[i]]) * H[[k]](zscore[[i]])
  gd.mat = cbind(dnorm(zscore[[i]]), gd.mat)
  time.primal[[i]] <- system.time(gd.primal[[i]] <- w.mosek.primal(gd.mat, w_prior = rep(0, K)))
}
```

```{r Rmosek primal fitting plotting, cache = TRUE, echo = FALSE}
n = ncol(z)
x.seq = seq(-6, 6, 0.01)
for (i in 1 : sel.num) {
  K = ord[i]
  gd.seq.mat = matrix(0, nrow = length(x.seq), ncol = K)
  for (k in 1 : K)
    gd.seq.mat[, k] = dnorm(x.seq) * H[[k]](x.seq)
  y.seq = gd.seq.mat %*% gd.primal[[i]]$w + dnorm(x.seq)
  z.hist = hist(zscore[[i]], breaks = 100, plot = FALSE)
  z.hist.ymax = max(c(z.hist$density, dnorm(0)))
  cat("Fitted w:", gd.primal[[i]]$w, "\n")
  cat("Time Cost in Seconds:", time.primal[[i]][1:3], "\n")
  hist(zscore[[i]], breaks = 100, probability = TRUE, ylim = c(0, z.hist.ymax), main = "Histogram of Correlated Z Scores", xlab = "Correlated Z Scores")
  lines(x.seq, dnorm(x.seq), col = "red")
  lines(x.seq, y.seq, col = "blue")
}
```

### Signal $+$ correlated error

```{r signal simulation, cache = TRUE, echo = FALSE}
true.g = ashr::normalmix(pi = c(0.6, 0.3, 0.1), mean = 0, sd = c(0, 2, 4))
x = seq(-10, 10, 0.01)
y.true = ashr::mixcdf(true.g, x, lower.tail = TRUE)
beta <- c(
  rep(0, 6000),
  rnorm(3000, 0, 2),
  rnorm(1000, 0, 4)
)
beta <- sample(beta)
sebetahat <- rep(1, 1e4)
betahat <- list()
for (i in 1 : sel.num) {
  betahat[[i]] = beta + sebetahat * zscore[[i]]
}
```

```{r ash signal fitting, cache = TRUE, echo = FALSE}
ash.signal = list()
for (i in 1 : sel.num) {
  ash.signal[[i]] <- ashr::ash(betahat[[i]], 1, mixcompdist = "normal", method = "fdr")
}
```

```{r gdash primal signal fitting, cache = TRUE, echo = FALSE}
time.primal.signal = list()
gd.primal.signal = list()
for (i in 1 : sel.num) {
  time.primal.signal[[i]] <- system.time(gd.primal.signal[[i]] <- gdash(betahat[[i]], sebetahat, gd.ord = ord[i], primal = TRUE, gd.normalized = FALSE, w.lambda = NULL, mixcompdist = "normal", method = "fdr", control = list(maxiter = 100)))
}
```

```{r gdash primal signal plotting, cache = TRUE, echo = FALSE}
for (i in 1 : sel.num) {
  cat("Converged:", gd.primal.signal[[i]]$converged, "\n")
  cat("Number of Iteration:", gd.primal.signal[[i]]$niter, "\n")
  cat("Time Cost in Seconds:", time.primal.signal[[i]][1:3], "\n")
  plot(x, y.true, type = "l", ylab = expression(F[hat(g)](x)),
       main = "CDF of Fitted g")
  y.gdash = ashr::mixcdf(gd.primal.signal[[i]]$fitted_g, x, lower.tail = TRUE)
  y.ash = ashr::mixcdf(ash.signal[[i]]$fitted_g, x, lower.tail = TRUE)
  lines(x, y.ash, col = "red", lty = 2)
  lines(x, y.gdash, col = "blue")
  legend("topleft", lty = c(1, 2, 1), col = c("black", "red", "blue"), legend = c("True", "ASH", "GD-ASH"))
}
```

## Basic form: dual

The primal $w$ optimization problem has $n + L$ variables and $n$ constraints.  When $n$ is large, such as $n = 10K$ in our simulations, the time cost is usually substantial.  As the authors of `REBayes` pointed out, it's better to work on the dual form, which is

$$
\begin{array}{rl}
\min\limits_{v} & 
-\sum\limits_{j = 1}^n
\log\left(v_j\right) + a^Tv
\\
\text{subject to}
& A^Tv = 0 \\
& v \geq 0\ .
\end{array}
$$
The dual form has $n$ variables and more importantly, only $L$ constraints.  As $L \ll n$, the dual form is far more computationally efficient.

`Rmosek` provides optimal solutions to both primal and dual variables, so $\hat w$ is readily available when working on $v$ optimization.  But we need to be careful on which dual variables to use, such as `$sol$itr$suc`, `$sol$itr$slc`, or others.

### Correlated null

```{r Rmosek dual fitting, cache = TRUE, echo = FALSE}
n = ncol(z)
gd.dual = list()
time.dual = list()
for (i in 1 : sel.num) {
  K = ord[i]
  gd.mat = matrix(0, nrow = n, ncol = K)
  for (k in 1 : K)
    gd.mat[, k] = dnorm(zscore[[i]]) * H[[k]](zscore[[i]])
  gd.mat = cbind(dnorm(zscore[[i]]), gd.mat)
  time.dual[[i]] <- system.time(gd.dual[[i]] <- w.mosek(gd.mat, w_prior = rep(0, K)))
}
```

```{r Rmosek dual fitting plotting, cache = TRUE, echo = FALSE}
n = ncol(z)
x.seq = seq(-6, 6, 0.01)
for (i in 1 : sel.num) {
  K = ord[i]
  gd.seq.mat = matrix(0, nrow = length(x.seq), ncol = K)
  for (k in 1 : K)
    gd.seq.mat[, k] = dnorm(x.seq) * H[[k]](x.seq)
  y.seq = gd.seq.mat %*% gd.dual[[i]]$w + dnorm(x.seq)
  z.hist = hist(zscore[[i]], breaks = 100, plot = FALSE)
  z.hist.ymax = max(c(z.hist$density, dnorm(0)))
  cat("Fitted w:", gd.dual[[i]]$w, "\n")
  cat("Time Cost in Seconds:", time.dual[[i]][1:3], "\n")
  hist(zscore[[i]], breaks = 100, probability = TRUE, ylim = c(0, z.hist.ymax), main = "Histogram of Correlated Z Scores", xlab = "Correlated Z Scores")
  lines(x.seq, dnorm(x.seq), col = "red")
  lines(x.seq, y.seq, col = "blue")
}
```

### Signal $+$ correlated error

```{r gdash dual signal fitting, cache = TRUE, echo = FALSE}
time.dual.signal = list()
gd.dual.signal = list()
for (i in 1 : sel.num) {
  time.dual.signal[[i]] <- system.time(gd.dual.signal[[i]] <- gdash(betahat[[i]], sebetahat, gd.ord = ord[i], primal = FALSE, gd.normalized = FALSE, w.lambda = NULL, mixcompdist = "normal", method = "fdr", control = list(maxiter = 1000)))
}
```

```{r gdash dual signal plotting, cache = TRUE, echo = FALSE}
for (i in 1 : sel.num) {
  cat("Converged:", gd.dual.signal[[i]]$converged, "\n")
  cat("Number of Iteration:", gd.dual.signal[[i]]$niter, "\n")
  cat("Time Cost in Seconds:", time.dual.signal[[i]][1:3], "\n")
  plot(x, y.true, type = "l", ylab = expression(F[hat(g)](x)),
       main = "CDF of Fitted g")
  y.gdash = ashr::mixcdf(gd.dual.signal[[i]]$fitted_g, x, lower.tail = TRUE)
  y.ash = ashr::mixcdf(ash.signal[[i]]$fitted_g, x, lower.tail = TRUE)
  lines(x, y.ash, col = "red", lty = 2)
  lines(x, y.gdash, col = "blue")
  legend("topleft", lty = c(1, 2, 1), col = c("black", "red", "blue"), legend = c("True", "ASH", "GD-ASH"))
}
```

## Conclusion

Implementation by `Rmosek` can fully reproduce the results obtained by `cvxr`.  Moreover, the dual form gives the same results as the primal dorm does, with only a fraction of time.

It seems hopeful that we'll find a key to successfully tackle correlation in simultaneous inference, which has eluded Prof. Brad Efron for more than a decade.

## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
