---
title: "$\\hat\\pi_0$ on correlated global null estimated by `ashr` and `truncash`"
author: "Lei Sun"
date: 2017-02-21
output: workflowr::wflow_html
---


**Last updated:** `r Sys.Date()`

**Code version:** `r workflowr::extract_commit(".", 1)$sha1`

## Introduction

Using correlated global null data simulated from GTEx/Liver, $\hat\pi_0$ is estimated by `truncash` and `ashr`.  Ideally the estimates should be close to $1$.

## Simulation

In `truncash`, the threshold is $T = 1.96$.

```{r}
library(ashr)
source("../code/truncash.R")
```

```{r, cache = TRUE}
p = read.table("../output/p_null_liver_777.txt")
z = read.table("../output/z_null_liver_777.txt")
betahat = read.table("../output/betahat_null_liver_777.txt")

m = dim(p)[1]
n = dim(p)[2]
pihat0.ash = pihat0.truncash = c()

for (i in 1:m) {
  betahat_trial = as.numeric(betahat[i, ])
  sebetahat_trial = - betahat_trial / as.numeric(z[i, ])
  fit.ash = ashr::ash(betahat_trial, sebetahat_trial, method = "fdr", mixcompdist = "normal")
  pihat0.ash[i] = get_pi0(fit.ash)
  fit.truncash = truncash(betahat_trial, sebetahat_trial, t = qnorm(0.975))
  pihat0.truncash[i] = get_pi0(fit.truncash)
}
```

## Result

False positive rate by `ash`
```{r}
mean(pihat0.ash < 1)
```

False positive rate by `truncash`
```{r}
mean(pihat0.truncash < 1)
```

Compare $\hat\pi_0$ estimated by `ash` and `truncash`
```{r}
xlim = c(min(c(pihat0.ash, pihat0.truncash)), 1)
plot(pihat0.ash, pihat0.truncash, xlim = xlim, ylim = xlim, xlab = "ash", ylab = "truncash", main = expression(hat(pi)[0]))
abline(0, 1, lty = 2, col = "blue")
abline(v = 1, lty = 3, col = "red")
abline(h = 1, lty = 3, col = "red")
boxplot(pihat0.ash, pihat0.truncash, main = expression(hat(pi)[0]), names = c("ash", "truncash"))
abline(h = 1, lty = 2, col = "red")
```

## Session Information

