---
title: "`Rmosek`: Primal vs Dual with $l_1$ regularization"
author: "Lei Sun"
date: 2017-06-23
output: workflowr::wflow_html
---





## Introduction

Following [previous simulation](rmosek_primal_dual.html), we are adding $l_1$ regularization to the primal form such that

$$
\begin{array}{rl}
\min\limits_{f \in \mathbb{R}^m, \ \ g \in \mathbb{R}^n} & -\sum\limits_{i = 1}^n\log\left(g_i\right) + \sum\limits_{j = 1}^m\lambda_j\left|f_j\right| \\
\text{s.t.} & Af + a = g\\
& g \geq 0 \ .
\end{array}
$$

Its dual form is

$$
\begin{array}{rl}
\min\limits_{\nu \in \mathbb{R}^n} & a^T\nu-\sum\limits_{i = 1}^n\log\left(\nu_i\right) \\
\text{s.t.} & \left|A^T\nu\right| \leq \lambda\\
& \nu\geq0 \ .
\end{array}
$$

**Right now we haven't figured out how to program the $l_1$ regularized primal form in `Rmosek`, so here we are only comparing the dual form with or without regularization.**

## Simulation

Let $\lambda$ be

$$
\lambda_i = \begin{cases}
0 & i \text{ odd ;}\\
a / \rho^{i/2} & i \text{ even .}\\
\end{cases}
$$
with $a = 10$, $\rho = 0.5$.  $n = 10^4$, $m = 10$, $A$ and $a$ are generated in the [same](rmosek_primal_dual.html) way.

```{r, echo = FALSE, message = FALSE}
Hermite = function (gd.ord) {
  x <- PolynomF::polynom()
  H <- PolynomF::polylist(x, - 1 + x^2)
  if (gd.ord >= 3) {
    for(n in 2 : (gd.ord - 1))
      H[[n+1]] <- x * H[[n]] - n * H[[n-1]]
  }
  return(H)
}
```

```{r, echo = FALSE, message = FALSE, cache = TRUE}
set.seed(777)
N <- 1e3

n <- 1e4
m <- 10
rho <- 0.5
a <- 10
lambda <- a / sqrt(rho^(1 : m))
lambda[seq(1, m, by = 2)] = 0

time.dual = time.dual.reg = time.sys.dual = time.sys.dual.reg = niter.dual = niter.dual.reg = status.dual = status.dual.reg = c()

for (i in seq_len(N)) {
  ## Generate test data sets
  z <- rnorm(n, 0, sqrt(1.5))
  hermite <- Hermite(m)
  gd0.std <- dnorm(z)
  A <- cbind(gd0.std)
  for (j in 1 : m) {
    gd.std <- (-1)^j * hermite[[j]](z) * gd0.std / sqrt(factorial(j))
    A <- cbind(A, gd.std)
  }
  a <- A[, 1]
  A <- A[, -1]
  
  ## Dual optim w/o l_0 reg
  P <- list()
  P$sense <- "min"
  P <- list(sense = "min")
  P$c <- a
  P$A <- Matrix::Matrix(t(A), sparse = TRUE)
  P$bc <- rbind(rep(0, m), rep(0, m))
  P$bx <- rbind(rep(0, n), rep(Inf, n))
  opro <- matrix(list(), nrow = 5, ncol = n)
  rownames(opro) <- c("type", "j", "f", "g", "h")
  opro[1, ] <- as.list(rep("log", n))
  opro[2, ] <- as.list(1:n)
  opro[3, ] <- as.list(rep(-1, n))
  opro[4, ] <- as.list(rep(1, n))
  opro[5, ] <- as.list(rep(0, n))
  P$scopt <- list(opro = opro)
  time.dual[i] <- system.time(res <- Rmosek::mosek(P, opts = list(verbose = 0, getinfo = TRUE)))[3]
  time.sys.dual[i] <- res$dinfo$INTPNT_TIME
  niter.dual[i] <- res$iinfo$INTPNT_ITER
  status.dual[i] <- res$sol$itr$solsta
  
  ## Dual optim w l_0 reg
  P <- list()
  P$sense <- "min"
  P <- list(sense = "min")
  P$c <- a
  P$A <- Matrix::Matrix(t(A), sparse = TRUE)
  P$bc <- rbind(-lambda, lambda)
  P$bx <- rbind(rep(0, n), rep(Inf, n))
  opro <- matrix(list(), nrow = 5, ncol = n)
  rownames(opro) <- c("type", "j", "f", "g", "h")
  opro[1, ] <- as.list(rep("log", n))
  opro[2, ] <- as.list(1:n)
  opro[3, ] <- as.list(rep(-1, n))
  opro[4, ] <- as.list(rep(1, n))
  opro[5, ] <- as.list(rep(0, n))
  P$scopt <- list(opro = opro)
  time.dual.reg[i] <- system.time(res <- Rmosek::mosek(P, opts = list(verbose = 0, getinfo = TRUE)))[3]
  time.sys.dual.reg[i] <- res$dinfo$INTPNT_TIME
  niter.dual.reg[i] <- res$iinfo$INTPNT_ITER
  status.dual.reg[i] <- res$sol$itr$solsta
}
```

The dual optimization in all $1000$ simulation trials reaches the optimal solution both with and without regularization.

## Total time cost

```{r echo = FALSE}
boxplot(log(time.dual), log(time.dual.reg), names = c("Dual", "Dual + Reg"), main = "Total Run Time in Logarithm")
plot(log(time.dual), log(time.dual.reg), xlab = "Dual in Logarithm", ylab = "Dual + Reg in Logarithm", main = "Comparison on Total Run Time in Logarithm")
abline(0, 1, lty = 1, col = "red")
legend("bottomright", lty = 1, col = "red", "y = x", bty = "n")
```

## Number of iterations

```{r echo = FALSE}
boxplot(log(niter.dual), log(niter.dual.reg), names = c("Dual", "Dual + Reg"), main = "Number of Iterations in Logarithm")
plot(log(niter.dual), log(niter.dual.reg), xlab = "Dual in Logarithm", ylab = "Dual + Reg in Logarithm", main = "Comparison on Number of Iterations in Logarithm")
abline(0, 1, lty = 1, col = "red")
legend("bottomright", lty = 1, col = "red", "y = x", bty = "n")
```

## Time per iteration

```{r echo = FALSE}
boxplot(log(time.dual) - log(niter.dual), log(time.dual.reg) - log(niter.dual.reg), names = c("Dual", "Dual + Reg"), main = "Run Time per Iteration in Logarithm")
plot(log(time.dual) - log(niter.dual), log(time.dual.reg) - log(niter.dual.reg), xlab = "Dual in Logarithm", ylab = "Dual + Reg in Logarithm", main = "Comparison on Run Time per Iteration in Logarithm")
abline(0, 1, lty = 1, col = "red")
legend("bottomright", lty = 1, col = "red", "y = x", bty = "n")
```


