---
title: "Semicircular correlated $z$ scores"
author: "Lei Sun"
date: 2017-06-07
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

## Data generation

Let $L_{n \times k} = \left[L_{ij}\right]_{n \times k}$ be a matrix, each entry of which is generated as follows.

1. Let $L_{ij} \sim N(0, 1)$ independently.
2. Let $L_{ij} = \displaystyle\frac {L_{ij}}{\sqrt{L_{i1}^2 + \cdots + L_{ik}^2}}$.  That is, normalizing each row so that each row has a unit $l_2$ norm.

Then taking $L$ as known, let $x \sim N\left(0, I_k\right)$ be a $k$-dimensional vector comprised of $k$ independent $N\left(0, 1\right)$ random variables.  Then
$$
z = Lx \sim N\left(0, LL^T\right)
$$
should be $n$ marginally $N\left(0, 1\right)$ but correlated $z$ scores.  Indeed,
$$
\begin{array}{c}
\text{var}\left(z_i\right) = l_i^Tl_i = 1 \ ;
\\
\text{cov}\left(z_i, z_j\right) = l_i^Tl_j \neq 0 \text{, in general} \ ;
\end{array}
$$
where $l_i^T$ and $l_j^T$ are $i^\text{th}$ and $j^\text{th}$ rows of $L$ respectively.

Then we plot the histogram of $n$ $z$ scores.  One interesting thing is we can prove what these histograms would look like when $n$ is sufficiently large.

## $k = 4$

For example, when $k = 4$, $n$ is sufficiently large, say, $10^6$, the histogram of $z$ looks like a **semicircle** almost perfectly, as illustrated in the following simulation.  The semicircle is centered at the origin, and has a radius of $\left\|x\right\|_2$.

```{r}
set.seed(1)
n = 1e6
k = 4
L = matrix(rnorm(n * k), nrow = n)
s = sqrt(rowSums(L^2))
L = L / s
x = rnorm(k)
z = L %*% x
hist(z, breaks = 100, prob = TRUE)
R = sqrt(sum(x^2))
x.plot = seq(-max(abs(z)) - 1, max(abs(z)) + 1, length = 1000)
y.plot = 2 * sqrt(pmax(R^2 - x.plot^2, 0)) / (pi * R^2)
lines(x.plot, y.plot, col = "red")
```

Actually, when $k \neq 4$, for example, $k = 3$ or $k = 5$, the histograms of these correlated $z$ scores, simulated the same way, look different, and their shapes when $n \to \infty$ can be mathematically determined.

## $k = 3$

```{r}
set.seed(1)
n = 1e6
k = 3
L = matrix(rnorm(n * k), nrow = n)
s = sqrt(rowSums(L^2))
L = L / s
x = rnorm(k)
z = L %*% x
hist(z, breaks = 100, prob = TRUE)
```

## $k = 5$

```{r}
set.seed(1)
n = 1e6
k = 5
L = matrix(rnorm(n * k), nrow = n)
s = sqrt(rowSums(L^2))
L = L / s
x = rnorm(k)
z = L %*% x
hist(z, breaks = 100, prob = TRUE)
```

## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
