---
title: "Simulating Correlated $N(0, 1)$ $Z$ Scores"
author: "Lei Sun"
date: 2017-05-18
output: workflowr::wflow_html
---





## Introduction

Following [Gao](http://home.uchicago.edu/gaow/)'s suggestion, we investigate whether Gaussian derivatives can fit the empirical distributions of purely synthetic correlated $z$ scores simulated as follows.

$$
\begin{array}{rcl}
z & = & L_{n \times k} x_k / \sqrt{\text{diag}\left(LL^T\right)} \ ;\\
k &\leq& n \ ; \\
l_{ij} & \sim & N\left(0, 1\right)  \ ;\\
x_j & \sim & N\left(0, 1\right)  \ ;\\
L & = & \begin{bmatrix}
l_1^T \\
\vdots \\
l_n^T \\
\end{bmatrix}_{n \times k} \ ;
\\
z_i & = & l_{i}^Tx / \sqrt{l_i^Tl_i} \ . \\
\end{array}
$$

## Fitting

The coefficients are not fitted by [convex optimization](mosek_reg_4.html), but by the method of moments.  Namely, if a density $f$ can be decomposed by Gaussian derivatives,
$$
f\left(z\right) = \sum\limits_{l = 0}^L w_l \frac{1}{\sqrt{l!}}\varphi^{\left(l\right)}\left(z\right) \ ,
$$
then due to the [orthonormality of normalized Hermite polynomials](gaussian_derivatives.html#gaussian_derivatives_and_hermite_polynomials), $w_l$ can be expressed as
$$
w_l = \left(-1\right)^l\frac{1}{\sqrt{l!}}\int h_l\left(z\right)f\left(z\right)dz \ .
$$
Since $h_l$'s are polynomials, $w_l$ is a linear combination of moments under $f$, and can thus be estimated by sample moments, also called [Hermite moments](fitting_normal.html#hermite_moments).

## Examples

```{r, message = FALSE, echo = FALSE, cache = TRUE}
source("../code/gdash.R")
```

```{r, message = FALSE, echo = FALSE, cache = TRUE}
gd.std.mat = function(x, order) {
  hermite = Hermite(order)
  gd.mat = matrix(0, nrow = length(x), ncol = order)
  for (j in 1 : order) {
    gd.mat[, j] = hermite[[j]](x) * dnorm(x) * (-1)^j / sqrt(factorial(j))
  }
  gd.mat = cbind(dnorm(x), gd.mat)
}

WL = 100
hermite.list = orthopolynom::hermite.he.polynomials(WL)
hermite.coef = orthopolynom::polynomial.coefficients(hermite.list)
```

```{r, echo = FALSE, cache = TRUE}
order = 50
set.seed(777)
for (j in 1 : 10) {
L = matrix(rnorm(1e4 * 5), ncol = 5)
sd = sqrt(rowSums(L^2))
z = L %*% rnorm(5) / sd
## fit w by method of moments
moments = c()
for (i in 0 : WL) {
  moments[i + 1] = mean(z^i)
}
w.std = c()
for (i in 0 : WL) {
  w.std[i + 1] = sum(moments[1 : (i + 1)] / sqrt(factorial(i)) * hermite.coef[[i + 1]]) * (-1)^i
}
x.seq = seq(-max(abs(z), 3.5), max(abs(z), 3.5), 0.01)
y.gd = gd.std.mat(x.seq, order) %*% w.std[1 : (order + 1)]
z.hist = hist(z, breaks = 100, plot = FALSE)
hist(z, breaks = 100, prob = TRUE, main = "Histogram of Simulated Correlated N(0, 1) z Scores", ylim = c(0, max(c(z.hist$density, dnorm(0)))), xlim = range(x.seq))
lines(x.seq, dnorm(x.seq), col = "red")
lines(x.seq, y.gd, col = "blue")
legend("topleft", lty = 1, col = "red", "N (0, 1)", bty = "n")
legend("topright", lty = 1, col = "blue", "50 Gaussian\nDerivatives", yjust = 1, bty = "n")
}
```

## Remarks

The coefficients $\hat w_l$ estimated by the method of moments are not very satisfying even with $50$ Gaussian derivatives.  The reason might be that **completely synthetic correlated data are less likely to have samples on the extreme tails**, as observed in the histograms, yet these extreme samples are supposed to have disproportional influence on the method of moments estimates.  We also tried to estimate $\hat w_l$ by the convex optimization approach, but the results were even worse, probably due to the same reason.  The results might indicate **an interesting but often neglected difference between real data and synthetic ones**.


