---
title: "Gaussian derivatives applied to Smemo's data"
author: "Lei Sun"
date: 2017-06-17
output:
  workflowr::wflow_html:
    code_folding: hide
---





## Introduction

Re-analyze [Smemo et al 2014](http://www.nature.com/nature/journal/v507/n7492/abs/nature13138.html)'s mouse heart RNA-seq data after discussion with Matthew.

```{r read data}
counts.mat = read.table("../data/smemo.txt", header = T, row.name = 1)
counts.mat = counts.mat[, -5]
```

## Gene selection

Only use genes with total counts of $4$ samples $\geq 5$.

```{r remove zero genes}
counts = counts.mat[rowSums(counts.mat) >= 5, ]
design = model.matrix(~c(0, 0, 1, 1))
```

```{r number of selected genes, echo = FALSE}
cat("Number of selected genes:", nrow(counts))
```

## Summary statistics

```{r counts to summary statistics}
source("../code/count_to_summary.R")
summary <- count_to_summary(counts, design)
betahat <- summary$betahat
sebetahat <- summary$sebetahat
z <- summary$z
```

## Fitting $z$ with Gaussian derivatives

With stretch GD can fit $z$ scores, but it seems there should be signals.

```{r fitting gaussian derivatives, message = FALSE, warning = FALSE, echo = FALSE}
source("../code/gdash_lik.R")
source("../code/gdfit.R")
w.fit = gdfit(z, L = 10)
cat("GD Coefficients:\n")
cat(rbind(paste(1 : length(w.fit$w) - 1, ":"),
          paste(w.fit$w, ";")
          ))
plot.gdfit(z, w.fit$w, w.fit$L, breaks = 100)
plot.gdfit(z, w.fit$w, w.fit$L, std.norm = FALSE, breaks = 100)
```

## Discovered by `BH` and `ASH`

Feeding summary statistics to `BH` and `ASH`, both give thousands of discoveries.

```{r BH + ASH}
fit.BH = p.adjust((1 - pnorm(abs(z))) * 2, method = "BH")
## Number of discoveries by BH
sum(fit.BH <= 0.05)
fit.ash = ashr::ash(betahat, sebetahat, method = "fdr")
## Number of discoveries by ASH
sum(get_svalue(fit.ash) <= 0.05)
```

## Fitting `ASH` first or Gaussian derivatives first

Using default setting $L = 10$, $\lambda = 10$, $\rho = 0.5$, compare the `GD-ASH` results by fitting `ASH` first vs fitting `GD` first.  They indeed arrive at different local minima.

```{r GD-ASH fitting, message = FALSE, cache = TRUE}
fit.gdash.ASH <- gdash(betahat, sebetahat,
                       gd.priority = FALSE)
## Regularized log-likelihood by fitting ASH first
fit.gdash.ASH$loglik

fit.gdash.GD <- gdash(betahat, sebetahat)
## Regularized log-likelihood by fitting GD first
fit.gdash.GD$loglik
```

## `GD-ASH` with larger penalties on $w$

Using $\lambda = 50$, $\rho = 0.1$, fitting `ASH` first and `GD` first give the same result, and produce 1400+ discoveries with $q$ values $\leq 0.05$, all of which are discovered by `BH`.

```{r GD-ASH-Lik fitting, message = FALSE, cache = TRUE}
L = 10
lambda = 50
rho = 0.1
fit.gdash.ASH <- gdash(betahat, sebetahat,
                       gd.ord = L, w.lambda = lambda, w.rho = rho,
                       gd.priority = FALSE)
## Regularized log-likelihood by fitting ASH first
fit.gdash.ASH$loglik
## Number of discoveries
sum(fit.gdash.ASH$qvalue <= 0.05)
fit.gdash.GD <- gdash(betahat, sebetahat,
                      gd.ord = L, w.lambda = lambda, w.rho = rho,
                      gd.priority = TRUE)
## Regularized log-likelihood by fitting GD first
fit.gdash.GD$loglik
## Number of discoveries
sum(fit.gdash.GD$qvalue <= 0.05)
```

```{r GD-ASH discoveries histogram, echo = FALSE}
cat("GD Coefficients:\n")
cat(rbind(paste(1 : length(fit.gdash.ASH$w) - 1, ":"),
          paste(fit.gdash.ASH$w, ";")
          ))
hist(z[fit.gdash.ASH$qvalue <= 0.05], breaks = 100, prob = TRUE,
     xlab = "z scores discovered by GD-ASH",
     main = "Historgram of discovered z scores"
     )
```

## Fitting CASH

```{r packages}
source("../code/gdash_lik.R")
source("../code/gdfit.R")
library(edgeR)
library(limma)
library(locfdr)
```

```{r summary statistics}
counts.mat = read.table("../data/smemo.txt", header = T, row.name = 1)
counts.mat = counts.mat[, -5]
counts = counts.mat[rowSums(counts.mat) >= 5, ]
design = model.matrix(~c(0, 0, 1, 1))
dgecounts = edgeR::calcNormFactors(edgeR::DGEList(counts = counts, group = design[, 2]))
v = limma::voom(dgecounts, design, plot = FALSE)
lim = limma::lmFit(v)
r.ebayes = limma::eBayes(lim)
p = r.ebayes$p.value[, 2]
t = r.ebayes$t[, 2]
z = -sign(t) * qnorm(p/2)
```

```{r analysis}
fit.locfdr <- locfdr(z)
fit.qvalue <- qvalue::qvalue(p)
```

```{r cash}
betahat = lim$coefficients[, 2]
sebetahat = betahat / z
fit.cash <- gdash(betahat, sebetahat, gd.ord = 10)
fit.ash <- ashr::ash(betahat, sebetahat, mixcompdist = "normal", method = "fdr")
```

```{r plotting}
x.plot <- seq(-10, 10, length = 1000)
gd.ord <- 10
hermite = Hermite(gd.ord)
gd0.std = dnorm(x.plot)
matrix_lik_plot = cbind(gd0.std)
for (i in 1 : gd.ord) {
  gd.std = (-1)^i * hermite[[i]](x.plot) * gd0.std / sqrt(factorial(i))
  matrix_lik_plot = cbind(matrix_lik_plot, gd.std)
}
y.plot = matrix_lik_plot %*% fit.cash$w * fit.cash$fitted_g$pi[1]

method.col <- scales::hue_pal()(5)
# method.col <- c("#377eb8", "#984ea3", "#4daf4a", "#ff7f00", "#e41a1c")

setEPS()
postscript("../output/fig/mouseheart.eps", height = 5, width = 12)

par(mfrow = c(1, 2))
hist(z, prob = TRUE, main = "", xlab = expression(paste(z, "-scores")), cex.lab = 1.25)
lines(x.plot, y.plot, col = method.col[5], lwd = 2)
lines(x.plot, dnorm(x.plot), col = 
       "orange"
      #  method.col[2]
      , lty = 2, lwd = 2)
lines(x.plot, dnorm(x.plot, fit.locfdr$fp0[3, 1], fit.locfdr$fp0[3, 2]) * fit.locfdr$fp0[3, 3], col = method.col[3], lty = 2, lwd = 2)
legend("topleft", col = c("orange", method.col[3], method.col[5]), lty = c(2, 2, 1), legend = c("N(0, 1)", "Empirical null", expression(pi[0]~hat(f))), bty = "n", cex = 1.25)

par(mar = par("mar") + c(0, 1, 0, 0))
g1 <- fit.cash$fitted_g
g1.plot.x <- seq(-0.5, 0.5, length = 1000)
g1.plot.y <- rowSums(sapply(2 : length(g1$pi), function (i) {g1$pi[i] * dnorm(g1.plot.x, g1$mean[i], g1$sd[i])}))
plot(g1.plot.x, g1.plot.y, xlim = c(-0.35, 0.35), type = "l", xlab = expression(paste(theta, " (", log[2], " fold change)")), ylab = expression(hat(g)[1](theta)), cex.lab = 1.25)

dev.off()
```
