---
title: "Gaussian derivatives applied to Smemo's data"
author: "Lei Sun"
date: 2017-06-14
output: workflowr::wflow_html
---





## Introduction

[Smemo et al 2014](http://www.nature.com/nature/journal/v507/n7492/abs/nature13138.html) provides a mouse heart RNA-seq data set.  The data set contains 2 conditions, and each condition has only 2 samples.  We'll see if Gaussian derivatives can handle this difficult situation.

```{r read data}
counts = read.table("../data/smemo.txt", header = T, row.name = 1)
counts = counts[, -5]
```

```{r data size}
## Number of genes
nrow(counts)
## Number of samples
ncol(counts)
## Sneak peek
head(counts, 10)
```

## Preprocessing

In the first exploratory investigation, we only choose genes whose expression levels are not all zero for all 4 samples.  This is to prevent the complications brought by "non-expressed" genes.

```{r remove zero genes}
counts.nonzero = counts[rowSums(counts) >= 1, ]
## Equivalently
## counts.nonzero = counts[apply(counts, 1, max) >= 1, ]
design = model.matrix(~c(0, 0, 1, 1))
## Number of genes expressed
nrow(counts.nonzero)
```

Then we feed the count matrix to [the pipeline to get the summary statistics](nullpipeline.html): $\hat\beta$, $\hat s$, $z$.

```{r, counts to summary function}
counts_to_summary = function (counts, design) {
  dgecounts = edgeR::calcNormFactors(edgeR::DGEList(counts = counts, group = design[, 2]))
  v = limma::voom(dgecounts, design, plot = FALSE)
  lim = limma::lmFit(v)
  r.ebayes = limma::eBayes(lim)
  p = r.ebayes$p.value[, 2]
  t = r.ebayes$t[, 2]
  z = sign(t) * qnorm(1 - p/2)
  betahat = lim$coefficients[,2]
  sebetahat = betahat / z
  return (list(betahat = betahat, sebetahat = sebetahat, z = z))
}
```

```{r nonzero summary, echo = FALSE}
summary <- counts_to_summary(counts.nonzero, design)
betahat <- summary$betahat
sebetahat <- summary$sebetahat
z <- summary$z
```

## Fitting $z$ with Gaussian derivatives

Suppose $z$ are correlated null, will they be well fitted by 10 Gaussian derivatives?

```{r nonzero fitting and plotting, message = FALSE}
source("../code/gdash_lik.R")
source("../code/gdfit.R")
w.fit = gdfit(z, L = 10)
plot.gdfit(z, w.fit$w, w.fit$L, breaks = 100)
plot.gdfit(z, w.fit$w, w.fit$L, std.norm = FALSE, breaks = 100)
plot(ecdf(z))
plot.gdfit(z, w.fit$w, w.fit$L, breaks = "Sturges")
plot.gdfit(z, w.fit$w, w.fit$L, std.norm = FALSE, breaks = "Sturges")
```

## Remove two peaks

```{r non-singleton}
## Remove all singletons
counts.nonsingleton = counts[rowSums(counts) > 1, ]
## Number of non-singleton genes
nrow(counts.nonsingleton)
```

```{r non-singleton summary, echo = FALSE}
summary <- counts_to_summary(counts.nonsingleton, design)
betahat <- summary$betahat
sebetahat <- summary$sebetahat
z <- summary$z
```

```{r non-singleton fitting and plotting}
w.fit = gdfit(z, L = 10)
plot.gdfit(z, w.fit$w, w.fit$L, breaks = 100)
plot.gdfit(z, w.fit$w, w.fit$L, std.norm = FALSE, breaks = 100)
plot(ecdf(z))
```

## Higher expression

```{r positive}
## Remove all zeros
counts.pos = counts[apply(counts, 1, min) > 0, ]
## Number of positive genes
nrow(counts.pos)
```

```{r positive summary, echo = FALSE}
summary <- counts_to_summary(counts.pos, design)
betahat <- summary$betahat
sebetahat <- summary$sebetahat
z <- summary$z
```

```{r positive fitting and plotting}
w.fit = gdfit(z, L = 10)
cat(rbind(paste(0 : w.fit$L, ":"), paste(w.fit$w, ";")))
plot.gdfit(z, w.fit$w, w.fit$L, breaks = 100)
plot.gdfit(z, w.fit$w, w.fit$L, std.norm = FALSE, breaks = 100)
plot(ecdf(z))
```

```{r betahat vs sebetahat}
plot(betahat, sebetahat, cex = 0.7, pch = 19)
```

```{r betahat vs z}
plot(betahat, z, cex = 0.7, pch = 19)
```

```{r gd-ash}
fit.gdash = gdash(betahat, sebetahat)
fit.gdash
```

```{r BH}
fit.ash = ashr::ash(betahat, sebetahat)
lfsr.ash = ashr::get_lfsr(fit.ash)
sum(lfsr.ash <= 0.05)
fit.gdash.ash = ashr::ash(betahat, sebetahat, fixg = TRUE, g = fit.gdash$fitted_g)
lfsr.gdash.ash = ashr::get_lfsr(fit.gdash.ash)
sum(lfsr.gdash.ash <= 0.05)
pval = (1 - pnorm(abs(z))) * 2
pval.BH = p.adjust(pval, method = "BH")
sum(pval.BH <= 0.05)
```


