---
title: "Gaussian derivatives applied to Smemo's data"
author: "Lei Sun"
date: 2017-06-17
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

## Introduction

Re-analyze [Smemo et al 2014](http://www.nature.com/nature/journal/v507/n7492/abs/nature13138.html)'s mouse heart RNA-seq data after discussion with Matthew.

```{r read data}
counts.mat = read.table("../data/smemo.txt", header = T, row.name = 1)
counts.mat = counts[, -5]
```

## Gene selection

Only use genes with total counts of $4$ samples $\geq 5$.

```{r remove zero genes}
counts = counts.mat[rowSums(counts) >= 5, ]
design = model.matrix(~c(0, 0, 1, 1))
```

```{r number of selected genes, echo = FALSE}
cat("Number of selected genes:", nrow(counts))
```

## Summary statistics

```{r counts to summary statistics}
source("../code/count_to_summary.R")
summary <- count_to_summary(counts, design)
betahat <- summary$betahat
sebetahat <- summary$sebetahat
z <- summary$z
```

## Fitting $z$ with Gaussian derivatives

With stretch GD can fit $z$ scores, but it seems there should be signals.

```{r fitting gaussian derivatives, message = FALSE, warning = FALSE, echo = FALSE}
source("../code/gdash_lik.R")
source("../code/gdfit.R")
w.fit = gdfit(z, gd.ord = 10)
cat("GD Coefficients:\n")
cat(rbind(paste(1 : length(w.fit$w) - 1, ":"),
          paste(w.fit$w, ";")
          ))
plot.gdfit(z, w.fit$w, w.fit$gd.ord, breaks = 100)
plot.gdfit(z, w.fit$w, w.fit$gd.ord, std.norm = FALSE, breaks = 100)
```

## Discovered by `BH` and `ASH`

Feeding summary statistics to `BH` and `ASH`, both give thousands of discoveries.

```{r BH + ASH}
fit.BH = p.adjust((1 - pnorm(abs(z))) * 2, method = "BH")
## Number of discoveries by BH
sum(fit.BH <= 0.05)
fit.ash = ashr::ash(betahat, sebetahat, method = "fdr")
## Number of discoveries by ASH
sum(get_svalue(fit.ash) <= 0.05)
```

## Fitting `ASH` first or Gaussian derivatives first

Using default setting $L = 10$, $\lambda = 10$, $\rho = 0.5$, compare the `GD-ASH` results by fitting `ASH` first vs fitting `GD` first.  They indeed arrive at different local minima.

```{r GD-ASH fitting, message = FALSE, cache = TRUE}
fit.gdash.ASH <- gdash(betahat, sebetahat,
                       gd.priority = FALSE)
## Regularized log-likelihood by fitting ASH first
fit.gdash.ASH$loglik

fit.gdash.GD <- gdash(betahat, sebetahat)
## Regularized log-likelihood by fitting GD first
fit.gdash.GD$loglik
```

## `GD-ASH` with larger penalties on $w$

Using $\lambda = 50$, $\rho = 0.1$, fitting `ASH` first and `GD` first give the same result, and produce 1400+ discoveries with $q$ values $\leq 0.05$, all of which are discovered by `BH`.

```{r GD-ASH-Lik fitting, message = FALSE, cache = TRUE}
L = 10
lambda = 50
rho = 0.1
fit.gdash.ASH <- gdash(betahat, sebetahat,
                       gd.ord = L, w.lambda = lambda, w.rho = rho,
                       gd.priority = FALSE)
## Regularized log-likelihood by fitting ASH first
fit.gdash.ASH$loglik
## Number of discoveries
sum(fit.gdash.ASH$qvalue <= 0.05)
fit.gdash.GD <- gdash(betahat, sebetahat,
                      gd.ord = L, w.lambda = lambda, w.rho = rho,
                      gd.priority = TRUE)
## Regularized log-likelihood by fitting GD first
fit.gdash.GD$loglik
## Number of discoveries
sum(fit.gdash.GD$qvalue <= 0.05)
```

```{r GD-ASH discoveries histogram, echo = FALSE}
cat("GD Coefficients:\n")
cat(rbind(paste(1 : length(fit.gdash.ASH$w) - 1, ":"),
          paste(fit.gdash.ASH$w, ";")
          ))
hist(z[fit.gdash.ASH$qvalue <= 0.05], breaks = 100, prob = TRUE,
     xlab = "z scores discovered by GD-ASH",
     main = "Historgram of discovered z scores"
     )
```


## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
